### 2023-03-23 hw1/paper/main.tex
update the outline of paper

%\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
\documentclass[sigconf]{acmart}
\let\Bbbk\relax %% fix bug
\usepackage[utf8]{inputenc}

% =======================
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amsopn}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{textcomp}

\usepackage{boxedminipage}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{url}
\usepackage{times}
\usepackage{version}
% \usepackage[pdftex]{graphicx}
\usepackage{epsfig}
\usepackage{epsf}
%\usepackage{graphics}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\PassOptionsToPackage{bookmarks={false}}{hyperref}
%%%%%%%%%%%%
\usepackage{comment}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{dblfloatfix}
% ==========================
\input lstset.tex
\input macros.tex

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\begin{document}

\title{KNN with ANNOY and random forest}

\author{Hsieh Cheng-Han}
\email{emiliaistruelove@gmail.com}
\affiliation{%
  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
  \streetaddress{70 Lienhai Rd}
  \city{Kaohsiung}
  \country{Taiwan}
}

\begin{abstract}

\end{abstract}
\maketitle

\section{Introduction}
\label{sec:introduction}

\section{Related Works}

\section{the proposed algorithm}

    \bibliographystyle{IEEEtran}
    \bibliography{main}
\end{document}

### 2023-03-24 hw1/Data.cpp
update Data type and utility

@@ -1,0 +1,175 @@
+#include "src/Data.h"
+
+bool onplane(const point_t& x, const hyperplane_t& plane)
+{
+    return abs(plane.b - plane.n*x) <= minerr;
+}
+bool point_t::on(const hyperplane_t& plane)
+{
+    return onplane(*this, plane);
+}
+
+// add
+point_t operator+(const point_t& a, const point_t& b)
+{
+    if (a.size() != b.size()) { std::cerr << "a+b: a.size() != b.size(), return none point." << std::endl; return point_t{}; }
+    std::vector<double> mx{a.x};
+    for (size_t i = 0; i <= mx.size(); ++i) { mx[i] += b[i]; }
+    point_t m{mx};
+    return m;
+}
+// dot
+double operator*(const point_t &a, const point_t &b)
+{
+    if (a.size() != b.size()) { std::cerr << "a*b: a.size() != b.size(), return 0." << std::endl; return 0.0; }
+    double ret;
+    for (size_t i = 0; i < a.size(); ++i) 
+        ret += a[i] * b[i];
+    return ret;
+}
+// scale
+point_t operator*(const point_t &a, double scale)
+{
+    std::vector<double> v{a.x};
+    for (auto& x : v) x *= scale;
+    point_t ret{v};
+    return ret;
+}
+point_t operator*(double scale, const point_t &a)
+{
+    return a*scale;
+}
+point_t operator/(const point_t &a, double scale)
+{
+    // precision ?
+    // return a*(1/scale);
+
+    std::vector<double> v{a.x};
+    for (auto& x : v) x /= scale;
+    point_t ret{v};
+    return ret;
+}
+// minus
+point_t operator-(const point_t& a, const point_t& b)
+{
+    if (a.size() != b.size()) { std::cerr << "a-b: a.size() != b.size(), return none point." << std::endl; return point_t{}; }
+    // O(2n)
+    // return a+(-1*b);
+
+    // O(n)
+    std::vector<double> mx{a.x};
+    for (size_t i = 0; i <= mx.size(); ++i) { mx[i] -= b[i]; }
+    point_t m{mx};
+    return m;
+}
+
+// cout
+std::ostream& operator<<(std::ostream& os, const point_t& a)
+{
+    for (auto& x : a.x) os << x << ' ';
+    return os;
+}
+
+// assignment has been implemented as implict constructor
+
[…]

### 2023-03-24 hw1/src/Data.h

@@ -1,0 +1,122 @@
+#include <vector>
+#include <iostream>
+#include <initializer_list>
+#include <cmath>
+#include <utility>
+
+struct hyperplane_t;
+
+struct point_t
+{
+    std::vector<double> x;
+
+    point_t() = default;
+    point_t(const point_t& other): x{other.x} { std::cerr << "point_t: copy constructor called" << std::endl; }
+    point_t(point_t&& other): x{std::move(other.x)} { std::cerr << "point_t: move constructor called" << std::endl; }
+    point_t(const std::vector<double>& vx): x{vx} { std::cerr << "point_t: calling vector& constructor." << std::endl; }
+    point_t(std::vector<double>&& vx): x{vx} { std::cerr << "point_t: calling vector& constructor." << std::endl; }
+    point_t(std::initializer_list<double>& list): x{list} { std::cerr << "point_t: calling initalizer_list& constructor." << std::endl; }
+    point_t(std::initializer_list<double>&& list): x{std::forward<decltype(list)>(list)} { std::cerr << "point_t: calling initalizer_list&& constructor." << std::endl; }
+
+    std::size_t size() const { return this->x.size(); }
+
+    // cout
+    friend std::ostream& operator<<(std::ostream& os, const point_t& a);
+
+    // index-access
+    const double& operator[](std::size_t i) const { return this->x.at(i); }
+          double& operator[](std::size_t i)       { return this->x.at(i); }
+
+    bool on(const hyperplane_t& plane);
+};
+
+using vector_t = point_t;
+struct hyperplane_t
+{
+    // n^Tx = b
+    vector_t n;
+    double b;
+
+    hyperplane_t() = default;
+    hyperplane_t(double b, vector_t n): n{n}, b{b} {}
+    hyperplane_t(std::initializer_list<double>& n, double b): n{n}, b{b} {}
+    hyperplane_t(std::initializer_list<double>&& n, double b): n{std::forward<decltype(n)>(n)}, b{b} {}
+    
+    std::size_t size() const { return this->n.size(); }
+    // cout
+    friend std::ostream& operator<<(std::ostream& os, const hyperplane_t& a);
+};
+
+constexpr double minerr = 1e-8;
+
+// point utility
+//
+// add
+point_t operator+(const point_t& a, const point_t& b);
+// dot
+double operator*(const point_t& a, const point_t& b);
+// scale
+point_t operator*(const point_t& a, double scale);
+point_t operator*(double scale, const point_t& a);
[…]

### 2023-03-24 hw1/Dataloader.cpp
update Dataloader

@@ -1,0 +1,80 @@
+#include "src/Dataloader.h"
+
+static std::vector<std::string_view> split(std::string_view s, char delimiter = ',')
+{
+    std::vector<std::string_view> ret;
+
+    std::size_t cur;
+    while ((cur = s.find(delimiter)) != std::string_view::npos)
+    {
+        ret.emplace_back(s.substr((size_t)0, cur));
+        s = s.substr(cur+1);
+    }
+    ret.emplace_back(s);
+    return ret;
+}
+
+void Dataloader_t::load(std::string_view& path, dataset_t& dataset)
+{
+    dataset.clear();
+
+    std::fstream fs;
+    fs.open(path.data());
+    auto& tags = this->tags;
+    std::string s; fs >> s;
+    std::string_view rawlabels{s};
+    tags = split(rawlabels, ',');
+    while (fs >> s)
+    {
+        std::string_view rawdata{s};
+        std::vector<std::string_view> alldata = split(rawdata, ',');
+        std::vector<double> data;
+        for (auto& s : alldata)
+        {
+            double x = 0;
+            auto result = std::from_chars(s.data(), s.data()+s.size(), x);
+            if (result.ec == std::errc::invalid_argument)
+            {
+                std::cerr << "Dataloader_t::load: cannot convert string, \"" << s << "\" to double." << std::endl;
+                x = 0;
+            }
+            data.emplace_back(x);
+        }
+        double label = data.back();
+        data.pop_back();
+        dataset.emplace_back(data, label);
+    }
+}
+
+void Dataloader_t::load_test(std::string_view& path)
+{
+    this->load(path, this->test_data);
+}
+void Dataloader_t::load_test(std::string_view&& path)
+{
+    this->load(path, this->test_data);
+}
+
+void Dataloader_t::load_train(std::string_view& path)
+{
+    this->load(path, this->train_data);
+}
+void Dataloader_t::load_train(std::string_view&& path)
+{
+    this->load(path, this->train_data);
+}
+
+// unit test
+#ifdef DATALOADER_TEST
+int main()
+{
+    Dataloader_t dataloader;
+    std::cout << "load test data..." << std::endl;
+    dataloader.load_train("./data/testA/test_data.csv");
+    std::cout << dataloader.train_data << std::endl;
+    std::cout << "load train data..." << std::endl;
+    dataloader.load_test("./data/testA/train_data.csv");
+    std::cout << dataloader.test_data << std::endl;
+    return 0;
+}
+#endif

### 2023-03-24 hw1/src/Dataloader.h

@@ -1,0 +1,27 @@
+#include <vector>
+#include <utility>
+#include <string>
+#include <string_view>
+#include <map>
+#include <fstream>
+#include <charconv>
+#include "Data.h"
+
+class Dataloader_t
+{
+public:
+    // record the name of i-th field
+    std::vector<std::string_view> tags;
+    // data
+    dataset_t train_data, test_data;
+
+    std::fstream fs;
+
+    Dataloader_t() = default;
+
+    void load(std::string_view& path, dataset_t& dataset);
+    void load_test(std::string_view&& path);
+    void load_test(std::string_view& path);
+    void load_train(std::string_view&& path);
+    void load_train(std::string_view& path);
+};

### 2023-03-25 hw1/Brute.cpp
transmit to another computer

@@ -1,0 +1,30 @@
+#include "src/Brute.h"
+
+std::vector<int> argsort(const std::vector<double>& dist)
+{
+    std::vector<std::pair<int, double>> vec;
+    std::vector<int> result;
+    for (std::size_t i = 0; i < dist.size(); ++i)
+        vec.emplace_back(i, dist[i]);
+    std::sort(vec.begin(), vec.end(), [](const auto& lhs, const auto& rhs) { return lhs.second < rhs.second; });
+    for (std::size_t i = 0; i < dist.size(); ++i)
+        result.emplace_back(vec[i]);
+    return result;
+}
+
+std::vector<data_t> brute_force::knn(const data_t& data, std::size_t k)
+{
+    std::vector<double> dist;
+    for (std::size_t i = 0; i < data.size(); ++i)
+        dist.emplace_back(euclidean_dist(brute_force::dataset.data[i].point, data.point));
+    std::vector<int> dist_arg = argsort(dist);
+    std::vector<data_t> result;
+    for (auto& i : dist_arg) result.emplace_back(brute_force::dataset[i]);
+    return result;
+}
+
+double brute_force::predict(const data_t& data, std::size_t k=3)
+{
+    std::vector<data_t> knns = brute_force::knn(data, k);
+
+}

### 2023-03-25 hw1/KNN.cpp

@@ -1,0 +1,11 @@
+#include "src/KNN.h"
+
+KNN_t::KNN_t(dataset_t dataset)
+{
+    this->train_data = dataset;
+}
+
+dataset_t KNN_t::predict(dataset_t test_data)
+{
+    
+}

### 2023-03-25 hw1/main.cpp

@@ -1,10 +1,11 @@
 #include <iostream>
-#include "KNN.h"
-#include "Dataloader.h"
+#include "src/KNN.h"
+#include "src/Dataloader.h"
+#include "src/Data.h"
 
 int main()
 {
-    Dataloader_t dataloader{};
+    Dataloader_t dataloader;
     
     std::cout << "load train data..." << std::endl;
     dataloader.load_train("train.data");
@@ -13,7 +14,7 @@ int main()
     dataloader.load_test("test.data");
     
     KNN_t KNN{dataloader.train_data};
-    Data result = KNN.predict(dataloader.test_data);
+    dataset_t result = KNN.predict(dataloader.test_data);
 
     std::cout << result << std::endl;
 

### 2023-03-25 hw1/src/Annoy.h

@@ -1,0 +1,5 @@
+#include "Data.h"
+
+struct annoy
+{
+};

### 2023-03-25 hw1/src/Brute.h

@@ -1,0 +1,13 @@
+#include <iostream>
+#include <algorithm>
+#include <cstring>
+#include <utility>
+#include "Data.h"
+
+struct brute_force
+{
+    static dataset_t dataset;
+    static std::vector<data_t> knn(data_t data, std::size_t k);
+    static double predict(data_t data);
+};
+

### 2023-03-25 hw1/src/KNN.h

@@ -1,0 +1,12 @@
+#include <vector>
+#include <utility>
+#include "Data.h"
+
+class KNN_t
+{
+    dataset_t train_data;
+    KNN_t() = default;
+    KNN_t(dataset_t dataset);
+    dataset_t predict(dataset_t test_data);
+    data_t predict(data_t data);
+};

### 2023-04-01 hw1/SVM/main.cpp
ga and svm

@@ -1,0 +1,23 @@
+#include "svm.h"
+#include <iostream>
+using data_type = double;
+using label_type = int;
+
+int main()
+{
+    Dataloader_t<data_type, label_type> dataloader;
+    dataloader.load_train("../data/testA/train_data.csv");
+    dataloader.load_test("../data/testA/test_data.csv");
+
+    svm_t<data_type, label_type> svm(dataloader.train_data, dataloader.test_data);
+    svm.train_ga( 
+        /*level*/ 200,
+        /*mutation_rate*/ 0.05, 
+        /*elite_save_percent*/ 0.1, 
+        /*variation*/ 3, 
+        /*populations*/ 150
+    );
+    std::cout << "Correct_Rate: " << svm.correct_rate() << std::endl;
+
+    return 0;
+}

### 2023-04-01 hw1/SVM/svm.cpp

@@ -1,4 +1,7 @@
 #include "svm.h"
+
+#ifdef SVMTEST
+
 using data_type = double;
 using label_type = int;
 
@@ -17,3 +20,5 @@ int main()
     
     return 0;
 }
+
+#endif

### 2023-04-01 hw1/SVM/svm.h

@@ -5,36 +5,68 @@
 #include <vector>
 #include <cmath>
 #include <cstdlib>
+#include <queue>
+#include <algorithm>
+#include <unistd.h>
 #include "../include/Data.h"
 #include "../include/Dataloader.h"
 #include "../include/Datatransformer.h"
 
-template<typename T>
-struct hyperplane_data_t
+template<typename T, typename U>
+class hypvar_t;
+
+template<typename T, typename U>
+struct cmp_hyper {
+    bool operator()(hypvar_t<T, U> a, hypvar_t<T, U> b) 
+    {
+        return a.correct_rate < b.correct_rate;
+    }
+};
+
+template<typename T, typename U>
+class hypvar_t
 {
+    public:
+    hypvar_t(hyperplane_t<T> _hyperplane, dataset_t<T, U>& _dataset_train);
     double correct_rate;
     hyperplane_t<T> hyperplane;
 };
+template<typename T, typename U>
+hypvar_t<T, U> :: hypvar_t(hyperplane_t<T> _hyperplane, dataset_t<T, U>& _dataset_train)
+{
+    this->hyperplane = _hyperplane;
+
+    std::size_t data_nums = _dataset_train.size();
+    int correct_nums = 0;
+    for (std::size_t i = 0; i <data_nums ; ++i)
+    {
+        // maybe bug (data)
+        correct_nums += ((hyperplane.n * _dataset_train.data[i] - hyperplane.b > 0) == _dataset_train.label[i]);
+    }
+    this->correct_rate = ((double)correct_nums / (double)data_nums);
+}
 
 template<typename T, typename U>
 class svm_t
 {
     private:
     int level;
-    double cut_rate;
     double mutation_rate;
     double elite_save_percent;
     int variation;
     int populations;
-    std::vector< hyperplane_t<double> > hyperplanes;
+    std::priority_queue< hypvar_t<T, U>, std::vector< hypvar_t<T, U> >, cmp_hyper<T, U> > hyperplanes_data;
     void _init_gen();
+    void _next_gen();
+    hypvar_t<T, U> _crossover(hypvar_t<T, U>& a, hypvar_t<T, U>& b);
 
     public:
     dataset_t<T, U> dataset_train;
     dataset_t<T, U> dataset_test;
     svm_t();
     svm_t(dataset_t<T, U>& _dataset_train, dataset_t<T, U>& _dataset_test);
[…]

### 2023-04-01 hw1/include/Datatransformer.h
GA_SVM updated

@@ -74,7 +74,9 @@ dataset_t<T, U> Datatransformer_t<T, U>::random_pick(const dataset_t<T, U>& data
     std::vector<std::size_t> arg;
     for (std::size_t i = 0; i < dataset_.size(); ++i)
         arg.emplace_back(i);
-    std::random_shuffle(arg.begin(), arg.end());
+	std::random_device rd;
+	std::default_random_engine eng(rd());
+    std::shuffle(arg.begin(), arg.end(), eng);
 
     arg.erase(arg.begin() + n, arg.end());
     dataset_t<T, U> ret;
@@ -91,7 +93,9 @@ std::vector<dataset_t<T, U>> Datatransformer_t<T, U>::split(const dataset_t<T, U
     std::vector<std::size_t> arg;
     for (std::size_t i = 0; i < dataset_.size(); ++i)
         arg.emplace_back(i);
-    std::random_shuffle(arg.begin(), arg.end());
+	std::random_device rd;
+	std::default_random_engine eng(rd());
+    std::shuffle(arg.begin(), arg.end(), eng);
 
     //std::random_shuffle(dataset.begin(), dataset.end());
     std::vector<dataset_t<T, U>> ret;

### 2023-04-01 hw1/SVM/main.cpp
good variables

@@ -11,11 +11,11 @@ int main()
 
     svm_t<data_type, label_type> svm(dataloader.train_data, dataloader.test_data);
     svm.train_ga( 
-        /*level*/ 200,
+        /*level*/ 300,
         /*mutation_rate*/ 0.05, 
         /*elite_save_percent*/ 0.1, 
-        /*variation*/ 3, 
-        /*populations*/ 150
+        /*variation*/ 5, 
+        /*populations*/ 250
     );
     std::cout << "Correct_Rate: " << svm.correct_rate() << std::endl;
 

### 2023-04-01 hw1/KNN/main.cpp
update Annoy with bfs

@@ -70,10 +70,14 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 	std::cout << "===================================================================" << std::endl;
 
     std::cout << "Set knn search algorithm: ANNOY" << std::endl;
+    std::cout << "Set ANNOY search algorithm: bfs" << std::endl;
     std::size_t maxpoint = 17;
     if (argc >= 3) maxpoint = std::atoi(argv[2]);
     std::cout << "Max point count in the leaf of search tree = " << maxpoint << std::endl;
-    KNN.set_knn_method(std::make_shared<annoy<data_type, label_type>>(maxpoint));
+	auto annoy_ = std::make_shared<annoy<data_type, label_type> >(maxpoint);
+	annoy_->bfs_threhold = 5;
+	annoy_->search_method = "bfs";
+    KNN.set_knn_method(annoy_);
     std::cout << "Train the KNN..." << std::endl;
     KNN.train(dataloader.train_data);
     std::cout << "Predict the test data..." << std::endl;

### 2023-04-01 hw1/KNN/src/Annoy.h

@@ -2,6 +2,7 @@
 #define __ANNOY_H__
 #include "../../include/Data.h"
 #include <vector>
+#include <queue>
 #include <random>
 
 template<typename T, typename U>
@@ -32,12 +33,15 @@ class annoy : public KNN_Method_t<T, U>
 public:
     tree_t<T, U> tree;
 	std::size_t maxpoint = 13;
+	std::string search_method = "bfs";
+	double bfs_threhold = 20;
 	annoy() = default;
 	annoy(std::size_t maxp): maxpoint{maxp} {}
 	dataset_t<T, U> knn(const dataset_t<T, U>& dataset, const point_t<T>& data, std::size_t k);
 	void build(const dataset_t<T, U>& dataset) override;
     void dfs_build(node_t<T, U>*& now, const dataset_t<T, U>& dataset);
     dataset_t<T, U> dfs(node_t<T, U>* now, const point_t<T>& data);
+	dataset_t<T, U> bfs(node_t<T, U>* root, const point_t<T>& data, double threhold);
 };
 
 template<typename T, typename U>
@@ -54,20 +58,45 @@ dataset_t<T, U> annoy<T, U>::dfs(node_t<T, U>* now, const point_t<T>& data)
 	return dfs(now->r, data);
 }
 
-/*
 template<typename T, typename U>
-dataset_t<T, U> annoy<T, U>::bfs(node_t* now, const point_t<T>& data)
+dataset_t<T, U> annoy<T, U>::bfs(node_t<T, U>* root, const point_t<T>& data, double threhold)
 {
-    //TODO
-    exit(1);
+	std::priority_queue<std::pair<double, node_t<T, U>*>> pq;
+	pq.emplace(euclidean_dist(root->mid, data), root);
+	dataset_t<T, U> ret;
+	while (!pq.empty())
+	{
+		auto [dist, now] = pq.top(); pq.pop();
+		if (now->leaf) { ret += now->dataset; continue; }
+		if (dist < threhold)
+		{
+			//std::cout << "dist < threhold, find both subtree" << std::endl;
+			pq.emplace(euclidean_dist(now->l->mid, data), now->l);
+			pq.emplace(euclidean_dist(now->r->mid, data), now->r);
+		}
+		else if (data < now->mid)
+			pq.emplace(euclidean_dist(now->l->mid, data), now->l);
+		else
+			pq.emplace(euclidean_dist(now->r->mid, data), now->r);
+	}
+	return ret;
 }
-*/
 
 template<typename T, typename U>
[…]

### 2023-04-01 hw1/include/Data.h
add point_t to hyperplane_t distance function && point_t::operator+ and point_t::operator* now will padding zeros

@@ -7,7 +7,6 @@
 #include <functional>
 #include <limits>
 #include <utility>
-#include <ranges>
 
 constexpr double minerr = std::numeric_limits<double>::epsilon();
 
@@ -36,6 +35,8 @@ template<typename T> std::ostream& operator<<(std::ostream& os, const point_t<T>
 // distance
 template<typename T> point_t<T> midpoint(const point_t<T>& a, const point_t<T>& b);
 template<typename T> double euclidean_dist(const point_t<T>& a, const point_t<T>& b);
+template<typename T> double euclidean_dist(const point_t<T>& x0, const hyperplane_t<T>& plane);
+template<typename T> double euclidean_dist(const hyperplane_t<T>& plane, const point_t<T>& x0);
 template<typename T> double minkowski_dist(const point_t<T>& a, const point_t<T>& b, int p);
 
 // hyperplane utility
@@ -244,25 +245,47 @@ point_t<T>& point_t<T>::operator=(point_t<T>&& other)
 template<typename T>
 point_t<T>& point_t<T>::operator+=(const point_t<T>& other)
 {
-    if (this->size() != other.size()) { std::cerr << "a+=b: a.size() != b.size(), return originally left point." << std::endl; return *this; }
+    if (this->size() != other.size())
+	{
+		std::cerr << "ERROR: a+=b: a.size(" << this->size() << ") != b.size(" << other.size() << "), return originally left point." << std::endl;
+		return *this;
+	}
     for (size_t i = 0; i <= this->size(); ++i) { (*this)[i] += other[i]; }
     return *this;
 }
 template<typename T>
 point_t<T> operator+(const point_t<T>& a, const point_t<T>& b)
 {
-    if (a.size() != b.size()) { std::cerr << "a+b: a.size() != b.size(), exit..." << std::endl; exit(1); }
-    point_t<T> ret{a};
-    for (size_t i = 0; i < ret.size(); ++i) { ret[i] += b[i]; }
+    if (a.size() != b.size()) { std::cerr << "WARNING: a+b: a.size(" << a.size() << ") != b.size(" << b.size() << "). Padding zeros." << std::endl; }
+    point_t<T> ret;
+	if (a.size() > b.size())
+	{
+		const point_t<T>& ma = a;
+		const point_t<T>& mi = b;
[…]

### 2023-04-01 hw1/KNN/KNN.cpp
remove unused files

@@ -1,3 +1,0 @@
-#include "src/KNN.h"
-
-

### 2023-04-01 hw1/KNN/main.cpp
experiment

@@ -7,97 +7,80 @@
 #include "../include/Dataloader.h"
 #include "../include/Datatransformer.h"
 
-using data_type = double;
-using label_type = int;
+using data_t = double;
+using label_t = int;
 
 int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 {
-    std::string_view train_path = "../data/testA/train_data.csv";
-    std::string_view test_path  = "../data/testA/test_data.csv";
-    std::cout << "Train data path is " << train_path << std::endl;
-    std::cout << "Test data path is " << test_path << std::endl;
+// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method brute --k  9  
+// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12]
+// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method annoy --k  9    --annoy_search_method dfs  --maxpoint 17
+// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12] [13]                  [14] [15]       [16]
+// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method annoy --k  9    --annoy_search_method bfs  --maxpoint 17   --bfs_threhold 5
+// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12] [13]                  [14]  [15]       [16] [17]           [18]
+	
+    std::string_view train_path = argv[4];
+    std::string_view test_path  = argv[6];
+    std::cerr << "Train data path is " << train_path << std::endl;
+    std::cerr << "Test data path is " << test_path << std::endl;
 
     
-    std::size_t k = 9;
-    if (argc >= 2) k = (std::size_t)std::atoi(argv[1]);
-    std::cout << "k = " << k << std::endl;
+    std::size_t k = (std::size_t)std::atoi(argv[12]);
 
     // data is double, label is int
-    Dataloader_t<data_type, label_type> dataloader;
+    Dataloader_t<data_t, label_t> dataloader;
     
[…]

### 2023-04-01 hw1/include/Data.h
disable the error output

@@ -248,7 +248,7 @@ point_t<T>& point_t<T>::operator+=(const point_t<T>& other)
     if (this->size() != other.size())
 	{
 		std::cerr << "ERROR: a+=b: a.size(" << this->size() << ") != b.size(" << other.size() << "), return originally left point." << std::endl;
-		return *this;
+		exit(1);
 	}
     for (size_t i = 0; i <= this->size(); ++i) { (*this)[i] += other[i]; }
     return *this;
@@ -256,7 +256,10 @@ point_t<T>& point_t<T>::operator+=(const point_t<T>& other)
 template<typename T>
 point_t<T> operator+(const point_t<T>& a, const point_t<T>& b)
 {
-    if (a.size() != b.size()) { std::cerr << "WARNING: a+b: a.size(" << a.size() << ") != b.size(" << b.size() << "). Padding zeros." << std::endl; }
+    if (a.size() != b.size())
+	{
+		//std::cerr << "WARNING: a+b: a.size(" << a.size() << ") != b.size(" << b.size() << "). Padding zeros." << std::endl;
+	}
     point_t<T> ret;
 	if (a.size() > b.size())
 	{
@@ -283,7 +286,10 @@ point_t<T> operator+(const point_t<T>& a, const point_t<T>& b)
 template<typename T>
 T operator*(const point_t<T>& a, const point_t<T>& b)
 {
-    if (a.size() != b.size()) { std::cerr << "WARNING: a*b: a.size(" << a.size() << ") != b.size(" << b.size() << "). Padding zeros." << std::endl; }
+    if (a.size() != b.size()) 
+	{ 
+		//std::cerr << "WARNING: a*b: a.size(" << a.size() << ") != b.size(" << b.size() << "). Padding zeros." << std::endl;
+	}
     T ret = 0;
     for (size_t i = 0; i < std::min(a.size(), b.size()); ++i) ret += a[i] * b[i];
     return ret;

### 2023-04-01 hw1/KNN/main.cpp
experiment

@@ -1,6 +1,7 @@
 #include <iostream>
 #include <memory>
 #include <cmath>
+#include <chrono>
 #include "src/KNN.h"
 #include "src/Brute.h"
 #include "src/Annoy.h"
@@ -12,17 +13,10 @@ using label_t = int;
 
 int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 {
-// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method brute --k  9  
-// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12]
-// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method annoy --k  9    --annoy_search_method dfs  --maxpoint 17
-// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12] [13]                  [14] [15]       [16]
-// ./main.elf --repeat 100 --traindata ../data/testA/train_data.csv --testdata ../data/testA/test_data.csv --normalize true --search_method annoy --k  9    --annoy_search_method bfs  --maxpoint 17   --bfs_threhold 5
-// [0]        [1]      [2] [3]         [4]                          [5]        [6]                         [7]         [8]  [9]             [10]  [11] [12] [13]                  [14]  [15]       [16] [17]           [18]
-	
     std::string_view train_path = argv[4];
     std::string_view test_path  = argv[6];
-    std::cerr << "Train data path is " << train_path << std::endl;
-    std::cerr << "Test data path is " << test_path << std::endl;
+    //std::cerr << "Train data path is " << train_path << std::endl;
+    //std::cerr << "Test data path is " << test_path << std::endl;
 
     
     std::size_t k = (std::size_t)std::atoi(argv[12]);
@@ -30,57 +24,66 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     // data is double, label is int
     Dataloader_t<data_t, label_t> dataloader;
     
-    std::cerr << "Load the train data..." << std::endl;
[…]

### 2023-04-01 hw1/decision_tree/random_forest.cpp
remove unused files

@@ -1,2 +1,0 @@
-#include "src/random_forest.h"
-

### 2023-04-01 hw1/decision_tree/main.cpp
experiment

@@ -1,166 +1,99 @@
 #include <iostream>
 #include <memory>
 #include <cmath>
+#include <cstring>
+#include <chrono>
 #include "src/decision_tree.h"
 #include "src/DT_criterion.h"
 #include "src/random_forest.h"
 #include "../include/Dataloader.h"
 #include "../include/Datatransformer.h"
 
-using data_type = double;
-using label_type = int;
+using data_t = double;
+using label_t = int;
 
 int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 {
-    std::string_view train_path = "../data/testA/train_data.csv";
-    std::string_view test_path  = "../data/testA/test_data.csv";
-    std::cout << "Train data path is " << train_path << std::endl;
-    std::cout << "Test data path is " << test_path << std::endl;
-    Dataloader_t<data_type, label_type> dataloader;
+// ./main.elf --repeat $repeat --traindata $DATASET/train_data.csv --testdata $DATASET/test_data.csv --normalize $normalize --search_method decision_tree  --criterion entropy >> $LOGFILE
+// [0]        [1]      [2]     [3]         [5]                     [6]        [7]                    [8]         [9]        [10]            [11]           [12]        [13]
+// ./main.elf --repeat $repeat --traindata $DATASET/train_data.csv --testdata $DATASET/test_data.csv --normalize $normalize --search_method random_forest  --criterion entropy -n   $n   >> $LOGFILE
+// [0]        [1]      [2]     [3]         [5]                     [6]        [7]                    [8]         [9]        [10]            [11]           [12]        [13]    [14] [15]
+    std::string_view train_path = argv[5];
+    std::string_view test_path  = argv[7];
+    //std::cerr << "Train data path is " << train_path << std::endl;
+    //std::cerr << "Test data path is " << test_path << std::endl;
+    Dataloader_t<data_t, label_t> dataloader;
     
-    std::cout << "Load train data..." << std::endl;
+    //std::cerr << "Load train data..." << std::endl;
     dataloader.load_train(train_path);
-    dataloader.load_train(Datatransformer_t<data_type, label_type>::drop_attrs_are_xs(dataloader.train_data, std::vector<std::size_t>{2,3,4}, std::vector<data_type>{0,0,0}));
-    //std::cerr << "train data =\n" << dataloader.train_data << std::endl;
[…]

### 2023-04-02 hw1/decision_tree/main.cpp
experiment

@@ -46,47 +46,53 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 	std::chrono::steady_clock::time_point st = std::chrono::steady_clock::now();
 	if (strcmp(argv[11], "decision_tree") == 0)
 	{
-		//std::cerr << "Decision tree ..." << std::endl;
-		decision_tree_t<data_t, label_t> tree;
-		//std::cerr << "Set criterion(entropy)..." << std::endl;
-		if (strcmp(argv[13], "entropy"))
-			tree.set_criterion(std::make_shared<entropy_crit<label_t>>());
-		else if (strcmp(argv[13], "gini"))
-    		tree.set_criterion(std::make_shared<gini_crit<label_t>>());
-		//std::cerr << "Build tree..." << std::endl;
-		tree.build(dataloader.train_data);
+		for (std::size_t t = 0; t < repeat; ++t)
+		{
+			//std::cerr << "Decision tree ..." << std::endl;
+			decision_tree_t<data_t, label_t> tree;
+			//std::cerr << "Set criterion(entropy)..." << std::endl;
+			if (strcmp(argv[13], "entropy"))
+				tree.set_criterion(std::make_shared<entropy_crit<label_t>>());
+			else if (strcmp(argv[13], "gini"))
+				tree.set_criterion(std::make_shared<gini_crit<label_t>>());
+			//std::cerr << "Build tree..." << std::endl;
+			tree.build(dataloader.train_data);
 
-		//std::cerr << "Predict test data..." << std::endl;
-		auto result = tree.predict(dataloader.test_data);
-		auto correct = [](int out, int y) { return (double)(out == y); };
-		auto correct_n = (int)score<label_t>(result, dataloader.test_data.label, correct);
-		double acc = (double)correct_n/result.size()*100;
-		macc += acc;
-		sum += acc;
-		sum2 += acc*acc;
+			//std::cerr << "Predict test data..." << std::endl;
+			auto result = tree.predict(dataloader.test_data);
+			auto correct = [](int out, int y) { return (double)(out == y); };
+			auto correct_n = (int)score<label_t>(result, dataloader.test_data.label, correct);
+			double acc = (double)correct_n/result.size()*100;
+			macc += acc;
+			sum += acc;
+			sum2 += acc*acc;
+		}
 	}
 	else if (strcmp(argv[11], "random_forest") == 0)
 	{
-    	//std::cerr << "Random forest ..." << std::endl;
[…]

### 2023-04-02 hw1/decision_tree/main.cpp
bug fix

@@ -15,11 +15,11 @@ using label_t = int;
 int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 {
 // ./main.elf --repeat $repeat --traindata $DATASET/train_data.csv --testdata $DATASET/test_data.csv --normalize $normalize --search_method decision_tree  --criterion entropy >> $LOGFILE
-// [0]        [1]      [2]     [3]         [5]                     [6]        [7]                    [8]         [9]        [10]            [11]           [12]        [13]
+// [0]        [1]      [2]     [3]         [4]                     [5]        [6]                    [7]         [8]        [9]             [10]           [11]        [12]
 // ./main.elf --repeat $repeat --traindata $DATASET/train_data.csv --testdata $DATASET/test_data.csv --normalize $normalize --search_method random_forest  --criterion entropy -n   $n   >> $LOGFILE
-// [0]        [1]      [2]     [3]         [5]                     [6]        [7]                    [8]         [9]        [10]            [11]           [12]        [13]    [14] [15]
-    std::string_view train_path = argv[5];
-    std::string_view test_path  = argv[7];
+// [0]        [1]      [2]     [3]         [4]                     [5]        [6]                    [7]         [8]        [9]             [10]           [11]        [12]    [13] [14]
+    std::string_view train_path = argv[4];
+    std::string_view test_path  = argv[6];
     //std::cerr << "Train data path is " << train_path << std::endl;
     //std::cerr << "Test data path is " << test_path << std::endl;
     Dataloader_t<data_t, label_t> dataloader;
@@ -31,7 +31,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     //std::cerr << "Load test data..." << std::endl;
     dataloader.load_test(test_path);
     dataloader.load_test(dataloader.test_data);
-	if (strcmp(argv[9], "true") == 0)
+	if (strcmp(argv[8], "true") == 0)
 	{
 		dataloader.load_train(Datatransformer_t<data_t, label_t>::normalize(dataloader.train_data));
 		dataloader.load_test(Datatransformer_t<data_t, label_t>::normalize(dataloader.test_data));
[…]

### 2023-04-02 hw1/paper/main.tex
update paper

@@
 %\IEEEoverridecommandlockouts
-\documentclass[sigconf]{acmart}
-\let\Bbbk\relax %% fix bug
+%\documentclass[sigconf]{acmart}
+%\let\Bbbk\relax %% fix bug
+\documentclass[twocolumn,10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 % ==========================
-\input lstset.tex
-\input macros.tex
+%\usepackage[a4paper, margin = 2.5cm]{geometry}
 
@@
 
-\title{KNN with ANNOY and random forest}
+\title{The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes}
 
 \author{Hsieh Cheng-Han}
-\email{emiliaistruelove@gmail.com}
-\affiliation{%
-  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
-  \streetaddress{70 Lienhai Rd}
-  \city{Kaohsiung}
-  \country{Taiwan}
-}
-
-\begin{abstract}
-
-\end{abstract}
+\date{October 2022}
 \maketitle
 
+\section*{abstract}
+  This work compares the accuracy of some classifiers for early the prediction of diabetes. More specifically, 
+  the research compares the accuracy of k-nearest neighbors (KNN) algorithm, decision tree, random forest, 
+  support vector machine (SVM), neural network, naive Bayes classifier, and PLA on the prediction of diabetes, which 
+  the dataset is collected with eight features, times of pregnancy, concentration of glucose in blood, blood 
+  pressure, skin thickness,  concentration of insulin in blood, body mass index (BMI), the value of diabetes 
+  pedigree function and age.
+
+  The result show that XXX is the most accurate on the prediction of diabetes.
+
 \section{Introduction}
-\label{sec:introduction}
+\label{sec:Introduction}
+  Diabetes is a chronic disease which may cause many complications. There're lots of reason that can put a person 
+  at the highly risk of having diabetes, such as age, obesity, lack of exercies, and more on. So many reasons 
+  interweave together making the manual prediction on diabetes is nearly impossible. However, lots of works \cite{MUJUMDAR2019292} \cite{MAHBOOBALAM2019100204} \cite{10.3389/fgene.2018.00515}
+  show that it is possible to have high accuracy by using machine learning techniques, such as random forest, 
+  K-means clustering, neural network, and so on.
 
-\section{Related Works}
+  By collecting the essential data of human body, prediction of diabetes can be turn into classification problem. 
+  Imagine that an individual case with essential data is a point in hyperspace, if it is closer to the cluster
+  having diabetes, this case is more likely to have diabetes in the future, otherwise, this case is more likely 
+  healthy. But there are lots of machine learning techniques born to solve classification problem, it remains a 
+  problem that which technique having the hightest accuracy on the prediction of diabetes.
 
-\section{the proposed algorithm}
+  To find out which techniques is more suitable to predict diabetes, this work examines the diagnosis of diabetes 
+  using KNN algorithm, decision tree, random forest, SVM, neural network naive Bayes classifier, and PLA.
+\section{Related works}
+\label{sec:Related works}
+  \bf{k-nearest neighbors (KNN) classification algorithm}: The KNN classification algorithm is a supervised learning 
+  method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
+  "birds of a feather flock together". By pick the $k$-nearest neighbors of a data point, the class label can be determined.
+
+  The rough process of KNN is described below: suppose that there is a dataset which contain $N$ data point, denoted as 
+  $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
+  a data with unknown class label is given, denoted $(X, Y)$. By a preset distance function $d(P, Q)$, ordering the dataset 
+  as $(X_{(1)}, Y_{(1)}), (X_{(2)}, Y_{(2)}), \cdots, (X_{(N)}, Y_{(N)})$ where $d(X_{(1)}, X)\leq d(X_{(2)}, X)\leq\cdots\leq d(X_{(N)}, X)$. 
+  Pick the $k$-first class labels to determine the unknow class label, $Y$.
+
+  \bf{decision tree}: Decision tree is a supervised learning method. Unlike KNN uses distance to determine the outcome, 
+  decision tree uses a sequence of deicsion that maximize the information gain, which can distinguish the class label of 
+  data as much as possible, to determine the outcome.  Given a dataset, $D$, which contain $N$ data and class label, the 
+  construction of a decision tree can be described as below: suppose there are $M$ decisions, denoted $f_i$. A decision can 
+  separate dataset $D$ into $m$ kinds, denote $D'_j$. The decision tree will adopt $\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$, 
+  and then recursively construct the tree until the data in separated dataset have the same class label. 
+  When a data with unknown class label comes, a decision tree determines recursively by the decision node until the leaf node. 
+  The advantage of decision tree is fast, and the decision is clear. But the disadvantage is that it is very likely overfitting 
+  and the structure of tree will become more complex with the more the class labels. To solve this problem, the following 
+  techniques is developed:
+
+  \bf{random forst}: Instead of a signle decision tree, random forest use lots of decision trees, which form a "forest". 
+  The decision trees are constructed by random subset of dataset. The key differs random forest from decision tree is that 
+  while decision trees consider all the possible feature splits, random forests only select a subset of those features, which 
+  reduce the risk of overfitting, bias, and overall variance.
+
+  \bf{support vector machine (SVM)}: 
+  \bf{neural network}: 
+  \bf{naive Bayes classifier}: 
+  \bf{PLA}:
+
+\section{KNN}
+
+\section{SVM}
+
+\section{neural network}
+
+\section{Naive Bayes classifier}
+
+\section{PLA}
+
+\section{Experiment result}
+
+\section{Conclusion}
 

### 2023-04-02 hw1/paper/main.tex
update KNN, decision tree, random forest

@@
   the research compares the accuracy of k-nearest neighbors (KNN) algorithm, decision tree, random forest, 
-  support vector machine (SVM), neural network, naive Bayes classifier, and PLA on the prediction of diabetes, which 
+  support vector machine (SVM), neural network, naive Bayes classifier, and perceptron learning algorithm (PLA) on the prediction of diabetes, which 
   the dataset is collected with eight features, times of pregnancy, concentration of glucose in blood, blood 
@@
 \label{sec:Related works}
-  \bf{k-nearest neighbors (KNN) classification algorithm}: The KNN classification algorithm is a supervised learning 
+  \bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
   method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
-  "birds of a feather flock together". By pick the $k$-nearest neighbors of a data point, the class label can be determined.
+  "birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
+  can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
+  well for prediction of diabetes disease.
 
-  The rough process of KNN is described below: suppose that there is a dataset which contain $N$ data point, denoted as 
+  \bf{decision tree}: \rm{Unlike} KNN uses distance to determine the outcome, 
+  decision tree uses a sequence of deicsion that maximize the information gain, which can distinguish the class label of 
+  data as much as possible, to determine the outcome. Many works \cite{5893838} \cite{8342938} have applied deicsion tree 
+  method and gain a good accuracy. The advantage of decision tree is fast, easy to implement, and the decision is clear. 
+  But the disadvantage is that it is very likely over-fitting and the structure of tree will become more complex with the 
+  more the class labels. To solve this problem, the following techniques is developed:
+
+  \bf{random forst}: \rm{Instead} of a signle decision tree, random forest use lots of decision trees, which form a "forest". 
+  The decision trees are constructed by random subset of dataset. The key differs random forest from decision tree is that 
+  while decision trees consider all the possible feature splits, random forests only select a subset of those features, which 
+  reduce the risk of overfitting, bias, and overall variance. In \cite{7972337} \cite{10.1007/978-981-16-2164-2_19}, random 
+  forest shows that it can greatly reduce the problem of over-fitting of the single decision tree, and gain an ever higher accuracy.
+
+  \bf{support vector machine (SVM)}: 
+  \bf{neural network}: 
+  \bf{naive Bayes classifier}: 
+  \bf{perceptron learning algorithm (PLA)}:
+
+\section{KNN}
+  The rough process of KNN is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
   $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
@@
 
-  \bf{decision tree}: Decision tree is a supervised learning method. Unlike KNN uses distance to determine the outcome, 
-  decision tree uses a sequence of deicsion that maximize the information gain, which can distinguish the class label of 
-  data as much as possible, to determine the outcome.  Given a dataset, $D$, which contain $N$ data and class label, the 
-  construction of a decision tree can be described as below: suppose there are $M$ decisions, denoted $f_i$. A decision can 
-  separate dataset $D$ into $m$ kinds, denote $D'_j$. The decision tree will adopt $\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$, 
+\section{decision tree}
+  Given a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
+  below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
+  $D'_j$. The decision tree will adopt $\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
   and then recursively construct the tree until the data in separated dataset have the same class label. 
   When a data with unknown class label comes, a decision tree determines recursively by the decision node until the leaf node.
-  The advantage of decision tree is fast, and the decision is clear. But the disadvantage is that it is very likely overfitting 
-  and the structure of tree will become more complex with the more the class labels. To solve this problem, the following 
-  techniques is developed:
+  The function of calculating information, $I$, can be various from implementation. The most famous two information function is 
+  entropy, and gini impurity. The formula of information entropy is $I_H(X)=-\sum_{x}p(x)\log_2p(x)$ 
+  and gini impurity is $I_G(X)=1-\sum_{x}p(x)^2$.
 
-  \bf{random forst}: Instead of a signle decision tree, random forest use lots of decision trees, which form a "forest". 
-  The decision trees are constructed by random subset of dataset. The key differs random forest from decision tree is that 
-  while decision trees consider all the possible feature splits, random forests only select a subset of those features, which 
-  reduce the risk of overfitting, bias, and overall variance.
-
-  \bf{support vector machine (SVM)}: 
-  \bf{neural network}: 
-  \bf{naive Bayes classifier}: 
-  \bf{PLA}:
-
-\section{KNN}
+\section{random forest}
+  Given the fact that a signle decision tree can be easily over-fitting, a technique called "random forest" is developed. By 
+  constructing $m$ decision trees with randomized subsets of training dataset, the different decision trees forms a "forest". 
+  The process that random forest determine a data with unknown class label can be outlined as follow: suppose for a coming data, 
+  $c_i$ decision trees in a random forest classify it as class $i$. Then the random forest will classify the data as class $\arg\max_{i} c_i$.
 

### 2023-04-02 hw1/paper/main.tex
update KNN-ANNOY

@@
 
-\section*{abstract}
+\section*{Abstract}
   This work compares the accuracy of some classifiers for early the prediction of diabetes. More specifically, 
@@
 \section{KNN}
-  The rough process of KNN is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
+  \rm{The} rough process of KNN algorithm is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
   $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
@@
   Pick the $k$-first class labels to determine the unknow class label, $Y$.
+
+  The algorithm to find $k$ nearest neighbors is the soul of KNN algorithm. The naive way to do that is brute force. By calculating every 
+  distance between the dataset and the undetermined data, the desired class can be easily obtained. The time complexity of brute force is $O(n)$. 
+  Another way to find $k$ nearest neighbors is approximate nearest neighbors oh yeah (ANNOY). This approximate algorithm is used at Spotify 
+  for music recommendations. The process of ANNOY is described follow: In every iteration, two points are randomly chosen, denoted $\vec x_1,\vec x_2$, 
+  and the hyperplane in the middle, whose equation is $\vec n^T\vec x=(\vec x_1-\vec x_2)^T\vec x=(\vec x_1-\vec x_2)^T(\vec x_1+\vec x_2)/2=b$ 
+  separates all the points in dataset into two kind, "below" ($\vec n^T\vec x<b$) or "above" ($\vec n^T\vec x>b$). Also, in every iteration, a 
+  binary tree structure is constructed whose left child contains all the points "below" the hyperplane and right child contains all the points "above". 
+  The end condition is when a side of hyperplane contains points no more than $M$, which is a preset parameter. 
+  When query a $k$ nearest neighbors of a point, recursively determine if the point "below" or "above" the hyperplane until reaching the leaf node. 
+  The time complexity of construction is $O(n)$, and the time complexity of query is $O(\log n)$.
+  But since the region searched may have less $k$ points, the search path shall cover both nodes if the point is too close to the hyperplane. This 
+  techniques though may increase the search time, still, it can greatly increase the accuracy of searching.
 

### 2023-04-02 hw1/paper/main.tex
update KNN-ANNOY

@@
   \bf{support vector machine (SVM)}:
+
   \bf{neural network}:
+
   \bf{naive Bayes classifier}:
+
   \bf{perceptron learning algorithm (PLA)}:
@@
   below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
-  $D'_j$. The decision tree will adopt $\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
+  $D'_j$. The decision tree will adopt $\arg\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
   and then recursively construct the tree until the data in separated dataset have the same class label. 
@@
   The process that random forest determine a data with unknown class label can be outlined as follow: suppose for a coming data, 
-  $c_i$ decision trees in a random forest classify it as class $i$. Then the random forest will classify the data as class $\arg\max_{i} c_i$.
+  $c_i$ decision trees in a random forest classify it as class $i$. Then the random forest will classify the data as class $\arg\max c_i$.
 

### 2023-04-03 hw1/PLA_pocket/pla_pocket.py
cannot plot

@@ -1,0 +1,59 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+# input the data
+train_data = pd.read_csv('train_data.csv')
+test_data = pd.read_csv('test_data.csv')
+X_train = train_data.iloc[:,:-1].values
+X_test = test_data.iloc[:,:-1].values
+y_train = train_data.iloc[:,-1].values
+y_test = test_data.iloc[:,-1].values
+
+# add bias term
+X_train = np.insert(X_train, 0, 1, axis=1)
+X_test = np.insert(X_test, 0, 1, axis=1)
+
+# initialize weights
+w = np.zeros(X_train.shape[1])
+
+# Pocket Perceptron Learning Algorithm
+num_iterations = 1000
+min_error = len(y_train)
+best_w = w
+for i in range(num_iterations):
+    y_pred = np.sign(X_train.dot(w))
+    errors = (y_pred != y_train)
+    num_errors = errors.sum()
+    if num_errors < min_error:
+        min_error = num_errors
+        best_w = w
+    if num_errors == 0:
+        break
+    random_index = np.random.choice(np.where(errors)[0])
+    w = w + y_train[random_index] * X_train[random_index]
+
+# predict labels for test data
+y_pred = np.sign(X_test.dot(best_w))
+
+# calculate accuracy
+accuracy = (y_pred == y_test).mean()
+print(f"Accuracy: {accuracy:.5f}")
+
+# # plot data points and decision boundary
+# plt.scatter(X_train[:,1], X_train[:,2], c=y_train, cmap=plt.cm.Paired, edgecolors='k')
+# x1_min, x1_max = np.concatenate((X_train[:,1], X_test[:,1])).min(), np.concatenate((X_train[:,1], X_test[:,1])).max()
+# x2_min, x2_max = np.concatenate((X_train[:,2], X_test[:,2])).min(), np.concatenate((X_train[:,2], X_test[:,2])).max()
[…]

### 2023-04-04 hw1/paper/main.tex

@@
 % \usepackage[pdftex]{graphicx}
+\usepackage{graphicx} 
 \usepackage{epsfig}
@@
   Another way to find $k$ nearest neighbors is approximate nearest neighbors oh yeah (ANNOY). This approximate algorithm is used at Spotify 
-  for music recommendations. The process of ANNOY is described follow: In every iteration, two points are randomly chosen, denoted $\vec x_1,\vec x_2$, 
+  for music recommendations. 
+  \begin{figure*}[htb]
+    \centering
+    \includegraphics[scale=0.5]{assets/ANNOY-split.png}
+    \caption{The region split by ANNOY.}
+    \label{fig:ANNOY_split}
+  \end{figure*}
+
+  \begin{figure*}[htb]
+    \centering
+    \includegraphics[scale=0.5]{assets/ANNOY-tree.png}
+    \caption{The tree structure used by ANNOY.}
+    \label{fig:ANNOY_tree}
+  \end{figure*}
+  Fig.
+\ref{fig:ANNOY_split} and Fig.
+\ref{fig:ANNOY_tree} give illustrations of how ANNOY works.
+The process of ANNOY is detailed as follow: In every iteration, two points are randomly chosen, denoted $\vec x_1,\vec x_2$,
   and the hyperplane in the middle, whose equation is $\vec n^T\vec x=(\vec x_1-\vec x_2)^T\vec x=(\vec x_1-\vec x_2)^T(\vec x_1+\vec x_2)/2=b$ 

### 2023-04-04 hw1/paper/main.tex
my part of SVM

@@
 \section{SVM}
+ Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
+Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ...
+, X_{in})$, where $X_{in}$ is the i-th individual data of $D$, containing $N$ data points.
+After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
+ In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
+$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
+ After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
+With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.The following are the steps to find the hyperplane:
 

### 2023-04-04 hw1/PLA_pocket/pla_pocket.py
use [sklearn.linear_model] 8D->3D

@@ -1,59 +1,50 @@
 import pandas as pd
-import numpy as np
+from sklearn.linear_model import Perceptron
 import matplotlib.pyplot as plt
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
 
-# input the data
+# 讀取 train_data.csv 和 test_data.csv
 train_data = pd.read_csv('train_data.csv')
 test_data = pd.read_csv('test_data.csv')
-X_train = train_data.iloc[:,:-1].values
-X_test = test_data.iloc[:,:-1].values
-y_train = train_data.iloc[:,-1].values
-y_test = test_data.iloc[:,-1].values
 
-# add bias term
-X_train = np.insert(X_train, 0, 1, axis=1)
-X_test = np.insert(X_test, 0, 1, axis=1)
+# 從資料中分離出特徵和標籤
+X_train = train_data.iloc[:, :-1]
+y_train = train_data.iloc[:, -1]
+X_test = test_data.iloc[:, :-1]
+y_test = test_data.iloc[:, -1]
 
-# initialize weights
-w = np.zeros(X_train.shape[1])
+# 建立 Perceptron 模型
+clf = Perceptron()
 
-# Pocket Perceptron Learning Algorithm
-num_iterations = 1000
-min_error = len(y_train)
-best_w = w
-for i in range(num_iterations):
-    y_pred = np.sign(X_train.dot(w))
-    errors = (y_pred != y_train)
-    num_errors = errors.sum()
-    if num_errors < min_error:
-        min_error = num_errors
-        best_w = w
-    if num_errors == 0:
-        break
-    random_index = np.random.choice(np.where(errors)[0])
-    w = w + y_train[random_index] * X_train[random_index]
+# 訓練模型
+clf.fit(X_train, y_train)
 
-# predict labels for test data
-y_pred = np.sign(X_test.dot(best_w))
+# 評估模型
+accuracy = clf.score(X_test, y_test)
+print("Accuracy:", accuracy)
 
-# calculate accuracy
-accuracy = (y_pred == y_test).mean()
-print(f"Accuracy: {accuracy:.5f}")
+# 繪製超平面
+w = clf.coef_[0]
+b = clf.intercept_[0]
+X_min = X_train.min() - 1
+X_max = X_train.max() + 1
 
[…]

### 2023-04-04 hw1/PLA_pocket/pla_pocket.py
use [Perceptron] 8D->3D :[

@@ -2,9 +2,8 @@ import pandas as pd
 from sklearn.linear_model import Perceptron
 import matplotlib.pyplot as plt
 import numpy as np
-from mpl_toolkits.mplot3d import Axes3D
 
-# 讀取 train_data.csv 和 test_data.csv
+
 train_data = pd.read_csv('train_data.csv')
 test_data = pd.read_csv('test_data.csv')
 
@@ -24,7 +23,7 @@ clf.fit(X_train, y_train)
 accuracy = clf.score(X_test, y_test)
 print("Accuracy:", accuracy)
 
-# 繪製超平面
+# plot hyperplane
 w = clf.coef_[0]
 b = clf.intercept_[0]
 X_min = X_train.min() - 1
@@ -34,15 +33,15 @@ fig = plt.figure()
 ax = fig.add_subplot(111, projection='3d')
 ax.scatter(X_train.iloc[:, 0], X_train.iloc[:, 1], X_train.iloc[:, 2], c=y_train)
 
-# 產生網格點
+# 網格
 xx, yy = np.meshgrid(np.arange(X_min[0], X_max[0], 0.2), 
                      np.arange(X_min[1], X_max[1], 0.2))
 zz = (-w[0]*xx - w[1]*yy - b) / w[2]
 
-# 繪製超平面
+# hyperplane
 ax.plot_surface(xx, yy, zz, alpha=0.6)
 
-# 設定軸標籤
+# xyz axis
 ax.set_xlabel('X1')
 ax.set_ylabel('X2')
 ax.set_zlabel('X3')

### 2023-04-04 hw1/paper/main.tex
svm is written (but it wasn't written very accurately)

@@
 
-  \bf{support vector machine (SVM)}:
+  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic binary linear classifier.
+In addition, SVM can also use a method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional feature space.
 
@@
  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
-Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ...
-, X_{in})$, where $X_{in}$ is the i-th individual data of $D$, containing $N$ data points.
+Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$.
 After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
@@
  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
-With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.The following are the steps to find the hyperplane:
+With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
+The following are the steps to find the hyperplane using a genetic algorithm:
+Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
+Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
+In the second step, use $w^t \cdot x - b$ to compare the binary labels of the training data.
+If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.
+This determines the accuracy of the $n$ hyperplanes.
+Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover.
+The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane.
+During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$.
+After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.
 

### 2023-04-04 hw1/PLA_pocket/pla_pocket.py
照老大說的做ㄌ🦈🦈🦈

@@ -1,49 +1,33 @@
 import pandas as pd
-from sklearn.linear_model import Perceptron
-import matplotlib.pyplot as plt
 import numpy as np
+from sklearn.linear_model import Perceptron
 
+# input the data
+AorB = input('Select your data (A or B ?) : ')
+if (AorB == 'A' or 'a'):
+    train_data = pd.read_csv('../data/testA/train_data.csv')
+    test_data = pd.read_csv('../data/testA/test_data.csv')
+else:
+    train_data = pd.read_csv('../data/testB/train_data.csv')
+    test_data = pd.read_csv('../data/testB/test_data.csv')
 
-train_data = pd.read_csv('train_data.csv')
-test_data = pd.read_csv('test_data.csv')
+num_test = input('Number of tests: ')
+num_test = int(num_test)
+i = 0
+sum_accuracy = 0
+while i < num_test:
 
-# 從資料中分離出特徵和標籤
-X_train = train_data.iloc[:, :-1]
-y_train = train_data.iloc[:, -1]
-X_test = test_data.iloc[:, :-1]
-y_test = test_data.iloc[:, -1]
+    X_train = train_data.iloc[:,:-1].values
+    X_test = test_data.iloc[:,:-1].values
+    y_train = train_data.iloc[:,-1].values
+    y_test = test_data.iloc[:,-1].values
 
-# 建立 Perceptron 模型
-clf = Perceptron()
+    clf = Perceptron()
+    # train model
+    clf.fit(X_train, y_train)
+    # calculate accuracy
+    accuracy = clf.score(X_test, y_test)
+    sum_accuracy += accuracy
+    i += 1
 
-# 訓練模型
-clf.fit(X_train, y_train)
-
-# 評估模型
-accuracy = clf.score(X_test, y_test)
-print("Accuracy:", accuracy)
-
-# plot hyperplane
-w = clf.coef_[0]
-b = clf.intercept_[0]
-X_min = X_train.min() - 1
-X_max = X_train.max() + 1
-
-fig = plt.figure()
-ax = fig.add_subplot(111, projection='3d')
-ax.scatter(X_train.iloc[:, 0], X_train.iloc[:, 1], X_train.iloc[:, 2], c=y_train)
-
-# 網格
-xx, yy = np.meshgrid(np.arange(X_min[0], X_max[0], 0.2), 
[…]

### 2023-04-04 hw1/NN/csv_parser.py
min-max normalizaion in csv_parser

@@ -1,4 +1,5 @@
 from random import randint
+import numpy as np
 TYPE_FUNC=[float,float,float,float,float,float,float,float,int]
 def type_convert(li):
     for i,j in enumerate(li): 
@@ -40,6 +41,14 @@ def csv_parser(dir):
             empty_data_remove(li)
             data_list.append(li[:-1])
             tag_list.append(li[-1])
+        print(data_list)
+        np_li=np.array(data_list)
+        np_li_max=np_li.max(0)
+        np_li_min=np_li.min(0)
+        for data in data_list:
+            for ind,ite in enumerate(data):
+                data[ind]=(ite-np_li_min[ind])/(np_li_max[ind]-np_li_min[ind])
+        print(data_list)
     return (data_list,tag_list)
 if __name__ == "__main__":
     csv_parser("../data/testA/train_data.csv")

### 2023-04-04 hw1/paper/main.tex
add some references

@@
   \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic binary linear classifier.
-In addition, SVM can also use a method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional feature space.
+In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional feature space.
 
@@
 With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
-The following are the steps to find the hyperplane using a genetic algorithm:
+In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
 Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
 Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
-In the second step, use $w^t \cdot x - b$ to compare the binary labels of the training data.
+In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data.
 If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.

### 2023-04-04 hw1/PLA_pocket/pla_pocket.py
input foolproof

@@ -3,8 +3,13 @@ import numpy as np
 from sklearn.linear_model import Perceptron
 
 # input the data
-AorB = input('Select your data (A or B ?) : ')
-if (AorB == 'A' or 'a'):
+while 1:
+    AorB = input('Select your data (A or B ?) : ')
+    if (AorB == 'A' or AorB == 'B' or AorB == 'a' or AorB == 'b'):
+        break
+    else:
+        continue
+if (AorB == 'A' or AorB == 'a'):
     train_data = pd.read_csv('../data/testA/train_data.csv')
     test_data = pd.read_csv('../data/testA/test_data.csv')
 else:
@@ -30,4 +35,4 @@ while i < num_test:
     sum_accuracy += accuracy
     i += 1
 
-print(f"Using data {AorB}. {num_test} times average accuracy: {sum_accuracy / num_test:.5f}")
+print(f"Using data {AorB}. The {num_test} times average accuracy rate: {sum_accuracy / num_test:.5f}")

### 2023-04-04 hw1/paper/main.tex
adjust the layout
Update main.tex

@@
 
-  \bf{naive Bayes classifier}:
+  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds.
+And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most likely outcome according to the conditional probability it just recorded.
 
@@
 \section{SVM}
- Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
-Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$.
-After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
- In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
+Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
+or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
+a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
+After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
+data is non-linearly separable. 
+In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
+the occurrence of non-linear separability: 
   $$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
- After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
-With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
-In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
-Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
-Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
-In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data.
-If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.
-This determines the accuracy of the $n$ hyperplanes.
-Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover.
-The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane.
-During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$.
-After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.
+After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
+the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
+not have binary class labels. 
+In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the 
+steps to find the hyperplane using a genetic algorithm: Firstly, decide the level of generations ($l$), population size ($n$), 
+variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
+of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
+In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
+$w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
+Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
+the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
+During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
+$0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
+is found.
 

### 2023-04-04 hw1/paper/main.tex
Update main.tex

@@
 \section{Naive Bayes classifier}
-
+First, let's explain the princple of Naive Bayes classifier, here is a very intuitive and easy-to-understand example, consider you are a scientist who study earthquake, what a intresting relation attract you is when there are eqrthquake, the number of rainy days is particular high while its low when there are no earthquake.
+Although it may sounds nonsense, we can assume there may exists a positive relation betweeen earthquake and rainy days.
+Here we talk about the Bayesian theorem, which is the basis of naive Bayes classifier.
+What the formula it give is $P(A|B) = \frac{P(A\capB)}{P(B)}$.
+Consider we need to predict the result by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A|B) = \frac{P(B|A)*P(A)}{P(B)}$.
+We can consider $A$ as the outcome and $B$ as data.
+Given a data that contains a sequence of data and various outcomes.
+We just record each event in each dimension and compute their conditional probabilities for each outcome and store these result in other place.
+When predicting the outcome using given data, find the conditional probability of each event in given data for one outcome and multiply them.
+Keep repeating until we had computed all conditional probability for each outcome, then find the maximum one, which is the most likely outcome.
+The problem is, when given is a continuous value instead of individual events, it look like we need to partition this continuous interval as individual events.
+However, the difficulty is how to find the best partition that can fit the model best.
+What I use to slove this problem is gene alogrithm.
+First ecord maximum and minimum values of given data in each dimension.
+Step2 is randomly partition data in each dimension according the maximum and minimum value we record before and repeat 100 times to generate enoguh species.
+Step3 is test the accuracy of the model on the training data and keep top 15 good species and kill the rest.
+Step4 is let the these elite to crossover, which means let them pass their partition to kids.
+Step4 is when there is enough offspring, all offspring will start mutation, which means their partitions will slightly shift, merge, split, or disapar etc..., make each animal different to optmize the model.
+And back to step2, here I called an evolution.
+We thus find the partition that is close to optimal solution after enough evolution.
 \section{PLA}

### 2023-04-05 hw1/paper/main.tex
SA added.PPT.TEX

--- 2023-04-04 hw1/paper/main.tex
@@
 
-  \bf{neural network}:
+  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer,hidden layer and output layer constructed by neurons,each data in dataset is processed while passing through neurons,layer by layer.After the processing,the outcome can be used to predict.Using back propogation,the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient,NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer,increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021},many neural network have been constructed and trained already,with high efficiency and accuracy in prediction of diabetes.
 
@@
 \section{neural network}
+Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or not,we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model,we have to find the structure of the hidden layer with NAS.
+We set the number of the layer to 10,with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$,which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers,which is more then 16 and less than 256,like above.We are aiming to find the approximate solution $f= \{x_1,x_2,...,x_{10}|16\leq x_i \leq 256,1\leq i \leq 10\}$ $\in$ $\mathcal{F}$,which increase the accuracy of the model in the short term.With simulating annealing algorithm\cite{17235},we can find the approximate solutions.First,set the initial temperature $T$,the end temperature $T_E$,temperature decreasing rate $R_T$,and a random solution $f^*$.Second,create a model based on the parameter in the $f^*$,and train with the dataset.We use cross entropy loss as loss function and Adam as optimization function.After training,we get the average loss of every epoch,$L^*$.Then,start the iteration by swap two of the parameters in $f^*$,get a new array $f^{**}$,train it with dataset,and get its average loss,$L^{**}$.After getting $L^*$ and $L^{**}$,we calculating the difference $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$,we update $f^* = f^{**}$.Otherwise,we use $e^{\frac{\Delta L}{T}}$ as the probability of the $f^{**}$ accepted as the new solution,get a random number $R^*$ $\in$ [1,0] from random number generator,if $R^*$ is less than $e^{\frac{\Delta L}{T}}$,we update $f^* = f^{**}$.Then repeat the iteration,but replace the swapping with changing one of the number in $f^*$ to $n,16 \leq n \leq 256$.
+ \begin{equation}
+    f^* = 
+    \begin{cases}
+    f^{**}, &\Delta L\le 0 \\
+    f^{**}, &\Delta L \ge 0 \text{ and } R^*<e^{\frac{\Delta L}{T}} \\ 
+    f^{*},  &\text{else}\\
+    \end{cases}
+\end{equation}
 
+After the end of the iteration,multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then,we get the approximate solution$f=f^*$.Every 2 iteration,the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS,we can now predict with untrained data with $80\%$ or so accuracy.
 \section{Naive Bayes classifier}

### 2023-04-05 hw1/NN/NN_test.py

@@ -4,7 +4,7 @@ from NN_train import NN,BATCH_SIZE
 from torch.utils.data import TensorDataset,DataLoader
 
 
-test_data_A_dir="../data/testA/train_data.csv"
+test_data_A_dir="../data/testA/test_data.csv"
 
 test_data,test_tag=csv_parser(test_data_A_dir)
 tensor_test_data=torch.tensor(test_data)
@@ -13,8 +13,8 @@ test_dataset=TensorDataset(tensor_test_data,tensor_test_tag)
 
 test_dataloader=DataLoader(test_dataset,batch_size=BATCH_SIZE)
 
-model=NN().to("cuda")
-model.load_state_dict(torch.load('diabete_model.pth'))
+# model=NN([52, 229, 230, 74, 105, 151, 50, 191, 161, 168]).to("cuda")
+model=torch.load('diabete_model.pth')
 
 loss_fn = torch.nn.CrossEntropyLoss()
 size = len(test_dataloader.dataset)

### 2023-04-05 hw1/NN/NN_train.py

@@ -1,31 +1,42 @@
+from random import randint
 import torch
 import numpy as np
 from csv_parser import csv_parser
 from torch.utils.data import TensorDataset,DataLoader
+from sa import sa
 class NN(torch.nn.Module):
-    def __init__(self):
+    def __init__(self,layer_nums):
         super(NN,self).__init__()
-        self.nn=torch.nn.Sequential(
-            torch.nn.Linear(8,16),
-            torch.nn.Linear(16,32),
-            torch.nn.Linear(32,64),
-            torch.nn.Linear(64,128),
-            torch.nn.ELU(),
-            torch.nn.Linear(128,256),
-            torch.nn.Mish(),
-            torch.nn.Linear(256,128),
-            torch.nn.ELU(),
-            torch.nn.Linear(128,64),
-            torch.nn.Linear(64,32),
-            torch.nn.Linear(32,16),
-            torch.nn.Linear(16,8),
-            torch.nn.Linear(8,4),
-            torch.nn.Linear(4,2),
-        )
-    def forward(self,x):
-        return self.nn(x)
+        self.layer_nums=[8]+layer_nums+[2]
+        self.nn = torch.nn.ModuleList([torch.nn.Linear(self.layer_nums[i],self.layer_nums[i+1]) for i in range(len(self.layer_nums)-1)])
+        self.acti=torch.nn.ReLU()
+        # self.nn=torch.nn.Sequential(
+        #     torch.nn.Linear(8,16),
+        #     torch.nn.Linear(16,32),
+        #     torch.nn.Linear(32,64),
+        #     torch.nn.Linear(64,128),
+        #     torch.nn.ReLU(),
+        #     torch.nn.Linear(128,256),
+        #     torch.nn.ReLU(),
+        #     torch.nn.Linear(256,128),
+        #     torch.nn.ReLU(),
+        #     torch.nn.Linear(128,64),
+        #     torch.nn.Linear(64,32),
+        #     torch.nn.Linear(32,16),
+        #     torch.nn.Linear(16,8),
+        #     torch.nn.Linear(8,4),
+        #     torch.nn.Linear(4,2),
+        # )
 
-EPOCH=10
+    def forward(self,x):
+        for f in self.nn:
+            x = f(x)
+            if randint(0,1):
+               x = self.acti(x)
+        return x
+
+
+
 BATCH_SIZE=8
 NUM_WORKER=4
 
@@ -46,43 +57,63 @@ def main():
[…]

### 2023-04-05 hw1/NN/csv_parser.py

@@ -27,8 +27,21 @@ def empty_data_remove(li):
                 li[i]=float(randint(180,450))
             # print(li)
             
-        
+def normalization(data_list):
+    np_li=np.array(data_list)
+    np_li_max=np_li.max(0)
+    np_li_min=np_li.min(0)
+    for data in data_list:
+        for ind,ite in enumerate(data):
+            data[ind]=float((ite-np_li_min[ind])/(np_li_max[ind]-np_li_min[ind]))        
 
+def standardization(data_list):
+    np_li=np.array(data_list)
+    std=np.std(np_li,1,ddof=1)
+    mean=np.mean(np_li,1)
+    for data in data_list:
+        for ind,ite in enumerate(data):
+            data[ind]=float((ite-mean[ind])/std[ind])
 def csv_parser(dir):
     with open(dir,"r") as f:
         raw_data=f.read()
@@ -41,14 +54,11 @@ def csv_parser(dir):
             empty_data_remove(li)
             data_list.append(li[:-1])
             tag_list.append(li[-1])
-        print(data_list)
-        np_li=np.array(data_list)
-        np_li_max=np_li.max(0)
-        np_li_min=np_li.min(0)
-        for data in data_list:
-            for ind,ite in enumerate(data):
-                data[ind]=(ite-np_li_min[ind])/(np_li_max[ind]-np_li_min[ind])
-        print(data_list)
+        normalization(data_list)
+        standardization(data_list)
+        # print(data_list)
+        
+        # print(type(data_list[0][0]))
     return (data_list,tag_list)
 if __name__ == "__main__":
     csv_parser("../data/testA/train_data.csv")

### 2023-04-05 hw1/NN/sa.py

@@ -1,0 +1,66 @@
+from random import sample, shuffle, uniform, randint
+import numpy as np
+from math import exp
+# import matplotlib.pyplot as plt
+# N=100
+# MAXT=1000
+# MINT=0.01
+# RATE=0.99
+# K=50
+
+def sa(N,MAXT,MINT,RATE,K,LNMA,LNMI,solu_func):
+    SAMPLE_LIST=[i for i in range(1,N)]
+    solution=[randint(LNMI,LNMA) for i in range(N)]
+    def change(solution):
+        pos=sample(SAMPLE_LIST,2)
+        solution[pos[0]],solution[pos[1]]=solution[pos[1]],solution[pos[0]]
+    def change2(solution):
+        pos=randint(0,N-1)
+        solution[pos]=randint(LNMI,LNMA)
+    print("Start\n=================\n",end="")
+    print(solution)
+    end_max=solu_func(solution)
+    t=MAXT
+    # dislist=[end_max]
+    # print("i:",solution)
+    # print("i dis:",end_max)
+    while t>MINT:
+        for k in range(K):
+            solution2=solution.copy()
+            if k%2==0:
+                change(solution2)
+            else:
+                change2(solution2)
+            print(t,k,"\n=================\n",end="")
+            
+            new_max=solu_func(solution2)
+            diff = new_max - end_max
+            print(new_max,end_max,diff,exp(-diff/t))
+            if diff<=0:
+                solution=solution2
+                end_max=new_max
+            else:
+                prob=exp(-diff/t)
+                randnum=uniform(0,1)
+                if randnum<prob:
+                    solution=solution2
+                    end_max=new_max
+                else:
+                    pass
+        t*=RATE
+        # dislist.append(end_max)
+    # print(solution)
+    # print(end_max)
+    # plt.figure(figsize = (15,8))
+    # plt.xlabel("Iteration",fontsize = 15)
+    # plt.ylabel("Distance",fontsize = 15)
+
+    # plt.plot(dislist,linewidth = 2.5, label = "Everytime smallest distance", color = 'r')
+    # plt.legend()
+    # plt.show(block=False)
+    # plt.pause(2)
+    # plt.close()
+    return solution
+# for i in range(10):
+#     solution=sa(1)
+    # sa(-1,solution)

### 2023-04-05 hw1/paper/main.tex
, add space

--- 2023-04-04 hw1/paper/main.tex
@@
 
-  \bf{neural network}:
+  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
 
-  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds.
-And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most likely outcome according to the conditional probability it just recorded.
+  \bf{naive Bayes classifier}:
 
@@
 \section{SVM}
-Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
-or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
-a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
-After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
-data is non-linearly separable. 
-In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
-the occurrence of non-linear separability: 
+ Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
+Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$.
+After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
+ In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
 $$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
-After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
-the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
-not have binary class labels. 
-In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the 
-steps to find the hyperplane using a genetic algorithm: Firstly, decide the level of generations ($l$), population size ($n$), 
-variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
-of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
-In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
-$w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
-Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
-the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
-During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
-$0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
-is found.
+ After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
+With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
+In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
+Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
+Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
+In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data.
+If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.
+This determines the accuracy of the $n$ hyperplanes.
+Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover.
+The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane.
+During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$.
+After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.
 
 \section{neural network}
+Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have to find the structure of the hidden layer with NAS.
+We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, which is more then 16 and less than 256, like above.We are aiming to find the approximate solution $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number in $f^*$ to $n, 16 \leq n \leq 256$.
+ \begin{equation}
+    f^* = 
+    \begin{cases}
+    f^{**},  &\Delta L\le 0 \\
+    f^{**},  &\Delta L \ge 0 \text{ and } R^*<e^{\frac{\Delta L}{T}} \\ 
+    f^{*},   &\text{else}\\
+    \end{cases}
+\end{equation}
 
+After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
 \section{Naive Bayes classifier}

### 2023-04-05 hw1/paper/main.tex

@@
 \section{SVM}
- Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
-Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$.
-After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
- In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
+  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
+  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
+  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
+  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
+  data is non-linearly separable. 
+  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
+  the occurrence of non-linear separability: 
 	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
- After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
-With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
-In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
-Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
-Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
-In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data.
-If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.
-This determines the accuracy of the $n$ hyperplanes.
-Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover.
-The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane.
-During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$.
-After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.
+  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
+  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
+  not have binary class labels. 
+  In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the 
+  steps to find the hyperplane using a genetic algorithm: Firstly, decide the level of generations ($l$), population size ($n$), 
+  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
+  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
+  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
+  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
+  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
+  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
+  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
+  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
+  is found.
 
 \section{neural network}
-Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have to find the structure of the hidden layer with NAS.
-We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, which is more then 16 and less than 256, like above.We are aiming to find the approximate solution $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number in $f^*$ to $n, 16 \leq n \leq 256$.
+  Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or 
+  not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have 
+  to find the structure of the hidden layer with NAS.
+  We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, 
+  which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, 
+  which is more then 16 and less than 256, like above.We are aiming to find the approximate solution 
+  $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in 
+  the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature 
+  $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the 
+  parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, 
+  we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, 
+  train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference 
+  $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability 
+  of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than 
+  $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number 
+  in $f^*$ to $n, 16 \leq n \leq 256$.
   \begin{equation}
@@
 
-After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
+  After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate 
+  solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing 
+  can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
+
 \section{Naive Bayes classifier}
+  First, let's explain the princple of Naive Bayes classifier, here is a very intuitive and easy-to-understand example, consider 
+  you are a scientist who study earthquake, what a intresting relation attract you is when there are eqrthquake, the number of 
+  rainy days is particular high while its low when there are no earthquake. Although it may sounds nonsense, we can assume there 
+  may exists a positive relation betweeen earthquake and rainy days. Here we talk about the Bayesian theorem, which is the basis 
+  of naive Bayes classifier. What the formula it give is $P(A|B) = \frac{P(A\capB)}{P(B)}$. Consider we need to predict the result 
+  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A|B) = \frac{P(B|A)*P(A)}{P(B)}$. 
+  We can consider $A$ as the outcome and $B$ as data. Given a data that contains a sequence of data and various outcomes. We just 
+  record each event in each dimension and compute their conditional probabilities for each outcome and store these result in other 
+  place. When predicting the outcome using given data, find the conditional probability of each event in given data for one outcome 
+  and multiply them. Keep repeating until we had computed all conditional probability for each outcome, then find the maximum one, 
+  which is the most likely outcome. The problem is, when given is a continuous value instead of individual events, it look like we 
+  need to partition this continuous interval as individual events. However, the difficulty is how to find the best partition that 
+  can fit the model best. What I use to slove this problem is gene alogrithm. First ecord maximum and minimum values of given data 
+  in each dimension. Step2 is randomly partition data in each dimension according the maximum and minimum value we record before 
+  and repeat 100 times to generate enoguh species. Step3 is test the accuracy of the model on the training data and keep top 15 
+  good species and kill the rest. Step4 is let the these elite to crossover, which means let them pass their partition to kids. 
+  Step4 is when there is enough offspring, all offspring will start mutation, which means their partitions will slightly shift, 
+  merge, split, or disapar etc..., make each animal different to optmize the model. And back to step2, here I called an evolution. 
+  We thus find the partition that is close to optimal solution after enough evolution.
 

### 2023-04-05 hw1/paper/main.tex
merge NN

@@
 \label{sec:Related works}
+
   \bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
@@
 
-  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic binary linear classifier.
-In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional feature space.
+  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
+  $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
+  binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
+  method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
+  feature space.
 
-  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
+  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
+  layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
+  After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
+  training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
+  structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
+  have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
 
-  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds.
-And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most likely outcome according to the conditional probability it just recorded.
+  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
+  theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
+  And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
+  likely outcome according to the conditional probability it just recorded.
 
@@
   may exists a positive relation betweeen earthquake and rainy days. Here we talk about the Bayesian theorem, which is the basis 
-  of naive Bayes classifier. What the formula it give is $P(A|B) = \frac{P(A\capB)}{P(B)}$. Consider we need to predict the result 
-  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A|B) = \frac{P(B|A)*P(A)}{P(B)}$. 
+  of naive Bayes classifier. What the formula it give is $P(A\mid B) = \frac{P(A\cap B)}{P(B)}$. Consider we need to predict the result 
+  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A\mid B) = \frac{P(B\mid A)\cdot P(A)}{P(B)}$ 
   We can consider $A$ as the outcome and $B$ as data. Given a data that contains a sequence of data and various outcomes. We just 

### 2023-04-05 hw1/paper/main.tex
update experiment result and modify the section of naive Bayes classifier

--- 2023-04-05 hw1/paper/main.tex
@@
 
-  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic binary linear classifier.
-In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional feature space.
+  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
+  $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
+  binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
+  method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
+  feature space.
 
-  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
+  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
+  layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
+  After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
+  training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
+  structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
+  have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
 
-  \bf{naive Bayes classifier}:
+  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
+  theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
+  And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
+  likely outcome according to the conditional probability it just recorded.
 
@@
 \section{decision tree}
-  Given a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
+  Consider a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
   below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
@@
   The function of calculating information, $I$, can be various from implementation. The most famous two information function is 
-  entropy, and gini impurity. The formula of information entropy is $I_H(X)=-\sum_{x}p(x)\log_2p(x)$ 
-  and gini impurity is $I_G(X)=1-\sum_{x}p(x)^2$.
+  entropy, and gini impurity. The formula of information entropy is 
+  \begin{equation}
+    I_H(X)=-\sum_{x}p(x)\log_2p(x) 
+  \end{equation}
+  and gini impurity is 
+  \begin{equation}
+    I_G(X)=1-\sum_{x}p(x)^2
+  \end{equation}
 
@@
 \section{SVM}
- Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively.
-Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$.
-After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
- In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
+  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
+  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
+  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
+  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
+  data is non-linearly separable. 
+  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
+  the occurrence of non-linear separability: 
 	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
- After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points.
-With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels.
-In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
-Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$).
-Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
-In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data.
-If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$.
-This determines the accuracy of the $n$ hyperplanes.
-Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover.
-The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane.
-During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$.
-After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.
+  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
+  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
+  not have binary class labels. 
+  Based on \cite{santhanam2015application}, we can use genetic algorithm (GA) to achieve finding better hyperplanes. The following are the 
+  steps to find the hyperplane using a GA: Firstly, decide the level of generations ($l$), population size ($n$), 
+  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
+  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
+  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
+  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
+  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
+  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
+  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
+  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
+  is found.
 
 \section{neural network}
-Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have to find the structure of the hidden layer with NAS.
-We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, which is more then 16 and less than 256, like above.We are aiming to find the approximate solution $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number in $f^*$ to $n, 16 \leq n \leq 256$.
+  Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or 
+  not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have 
+  to find the structure of the hidden layer with NAS.
+  We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, 
+  which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, 
+  which is more then 16 and less than 256, like above.We are aiming to find the approximate solution 
+  $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in 
+  the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature 
+  $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the 
+  parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, 
+  we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, 
+  train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference 
+  $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability 
+  of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than 
+  $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number 
+  in $f^*$ to $n, 16 \leq n \leq 256$.
   \begin{equation}
@@
 
-After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
+  After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate 
+  solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing 
+  can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
+
 \section{Naive Bayes classifier}
+  Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 
+  $i$-th class is $P(C_k\mid \bf{x})$ where $C_k$ is the event that data points $\bf{x}=(x_1,\cdots,x_n)$ belongs to $k$-th class.
+  By using Bayes' theorem, the probability can be rewritten as 
+  \begin{equation}
+    \label{eqn:bayes}
+    P(C_k\mid x)=\frac{P(C_k)P(\bf{x}\mid C_k)}{P(\bf{x})}
+  \end{equation}
+  In partice, 
+  there is interest only in the numerator of that fraction, because the denominator does not depend on $C_k$ and the values of the 
+  features that are given, so the denominator is effectively constant. 
+  Then, by chain rule of conditional probability, the numerator of Eq. \ref{eqn:bayes} can be rewritten as
+  \begin{equation}
+    \label{eqn:rebayes}
+    \begin{split}
+      &P(C)P(x_1\mid C_k)P(x_2,\cdots,x_n\mid C_k,x_1)
+      \\&=\cdots
+      \\&=P(C)P(x_1\mid C_k)\cdots P(x_n\mid C_k,x_1,\cdots,x_{n-1})
+    \end{split}
+  \end{equation}
+
+  Now assume that all features in $\bf{x}$ is mutually independent, $P(x_i\mid x_j, C_k)$ will be equal to $P(x_i\mid C_k)$. 
+  Thus, the probability is 
+  \begin{equation}
+    \label{eqn:prob_classifier}
+    P(C_k\mid x)=\frac{P(C_k)\prod^n_{i=1}P(x_i\mid C_k)}{Z}
+  \end{equation}
+  where $Z$ is a constant. 
+  With Eq. \ref{eqn:prob_classifier}, a data points with unknown class label can be classified by choosing the most possible class: 
+  \begin{equation}
+    \label{eqn:classifier}
+    \arg\max_k P(C_k)\prod^n_{i=1}P(x_i=x'_i\mid C_k)
+  \end{equation}
+
+  The problem is, when given is a continuous value instead of individual events, it need to be partitioned accroding to specific value 
+  which below this value is an individual event while above is other evnet. However, the difficulty is how to find the best partition 
+  that can fit the model best. By using gene alogrithm, the answer can be easily found. First, record maximum and minimum values of 
+  given data in each dimension. Second, randomly partition data in each dimension according the maximum and minimum value recorded before 
+  and repeat 100 times to generate enoguh species. Third, testing the accuracy of the model on the training data and keep top $K$ 
+  good species and kill the rest. Then, let the these elites prodece offsprings, which means pass their partitions to offsprings. 
+  When there is enough offsprings, all offsprings are going to have mutation, the partitions may slightly shift, 
+  merge, split, disappear, or keep originally. Finally, repeat the whole iteration until found the partition that is close to optimal 
+  solution after $T$ iterations.
 
@@
 \section{Experiment result}
+  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
+  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
+  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
+  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
+  Table \ref{table:overall} compares all datasets, which show that ...
+  \begin{table*}[htb]
+    %\normalsize
+    %\centering
+    \newcommand{\z}{\phantom{0}}
+    \caption{\textsc{Comparison of Classification Techniques.}}
+      \vspace{-\baselineskip}
+    \begin{tabular}{@{}lccccccl@{}}\toprule
+    Technique & Search (s) & testA & testA-normalized & testB & testB-normalized \\ \midrule
+    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
+    KNN-ANNOY-DFS    & $0.003$ & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
+    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
+    decision tree    & $0.009$ & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
+    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
+    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
+    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
+    \end{tabular}
+    \label{table:overall}
+      \vspace{-\baselineskip}
+  \end{table*}
 
 \section{Conclusion}
-
+  The experiment result shows that ...
 \bibliographystyle{IEEEtran}

### 2023-04-05 hw1/paper/main.tex
modify the section title SVM to SVM-GA, also Naive Bayes classifier to Naive Bayes classifier-GA

@@
 
-\section{SVM}
+\section{SVM-GA}
   Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
@@
 
-\section{Naive Bayes classifier}
+\section{Naive Bayes classifier-GA}
   Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 

### 2023-04-05 hw1/paper/main.tex
finished data experiment

@@
     SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
-    Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    Neural Network   & $3.2$ & $81.7910 \pm \z{2.0294}$          & $80.2985 \pm 1.4106$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
     Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\

### 2023-04-05 hw1/NN/NN_test.py

@@ -2,6 +2,8 @@ import torch
 from csv_parser import csv_parser
 from NN_train import NN,BATCH_SIZE
 from torch.utils.data import TensorDataset,DataLoader
+import time
+
 
 
 test_data_A_dir="../data/testA/test_data.csv"
@@ -21,6 +23,7 @@ size = len(test_dataloader.dataset)
 num_batches = len(test_dataloader)
 model.eval()
 test_loss,correct=0,0
+s=time.time()
 with torch.no_grad():
     for inputs,target in test_dataloader:
         inputs,target=inputs.to("cuda"),target.to("cuda")
@@ -29,4 +32,5 @@ with torch.no_grad():
         correct += (pred.argmax(1) == target).type(torch.float).sum().item()
 test_loss /= num_batches
 correct /= size
-print(f"Test Error: \n Accuracy: {(100*correct):>0.1f}%, Avg loss: {test_loss:>8f} \n")
+e=time.time()
+print(f"Test Error: \n Accuracy: {(100*correct):>0.4f}%, Avg loss: {test_loss:>8f} , time: {e-s:>3f}\n")

### 2023-04-05 hw1/NN/NN_train.py

@@ -51,7 +51,7 @@ def main():
     
 
     train_dataloader=DataLoader(dataset=train_dataset,batch_size=BATCH_SIZE,num_workers=NUM_WORKER)
-    test_data_A_dir="../data/testA/train_data.csv"
+    test_data_A_dir="../data/testA/test_data.csv"
     test_data,test_tag=csv_parser(test_data_A_dir)
     tensor_test_data=torch.tensor(test_data)
     tensor_test_tag=torch.tensor(test_tag)
@@ -63,14 +63,14 @@ def main():
     def train(solu,output_mode=False):
         model=NN(solu).to("cuda")
         if output_mode:
-            EPOCH=200
+            EPOCH=100
         else:
             EPOCH=5
-    
+
 
         opt = torch.optim.Adam(model.parameters(), lr=1e-4)
         loss_fn = torch.nn.CrossEntropyLoss()
-
+        min_loss=9999
         for epoch in range(EPOCH):
             for step,(inputs,target) in enumerate(train_dataloader):
                 
@@ -98,10 +98,11 @@ def main():
             test_loss /= num_batches
             correct /= size
             print(f"Test Error: \n Accuracy: {(100*correct):>0.8f}%, Avg loss: {test_loss:>8f} \n")
+            if output_mode and min_loss>test_loss:
+                min_loss=test_loss
+                torch.save(model,"diabete_model.pth")
         if not output_mode:
             return test_loss
-        else:
-            torch.save(model,"diabete_model.pth")
     #SA parameter
     N=10
     MAXT=0.1
@@ -112,7 +113,8 @@ def main():
     LNMI=16 #max number of node in a layer
 
     #SA
-    solution=sa(N,MAXT,MINT,RATE,K,LNMA,LNMI,train)
+    # solution=sa(N,MAXT,MINT,RATE,K,LNMA,LNMI,train)
+    solution=[31,110,253,240,223,99,212,163,243,73]
     train(solution,output_mode=True)
     
 if __name__ == "__main__":

### 2023-04-05 hw1/paper/main.tex
test B

--- 2023-04-05 hw1/paper/main.tex
@@
     SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
-    Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    Neural Network   & $3.2$   & $81.7910 \pm \z{2.0294}$           & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
     Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\

### 2023-04-06 hw1/paper/main.tex
adding SVM-GA's data

--- 2023-04-05 hw1/paper/main.tex
@@
     random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
-    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    SVM-GA           & $1.8462$ & $76.6616 \pm \z{4.0301}$          & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                  & $75 \pm \z{4}$\\
     Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\

### 2023-04-06 hw1/paper/main.tex
update PLA related work

--- 2023-04-05 hw1/paper/main.tex
@@
 
-\author{Hsieh Cheng-Han}
-\date{October 2022}
+\author{Hsieh Cheng-Han, Hsu Ting Hao, Sun Shih Yu}
+\date{April 2023}
 \maketitle
@@
 
+  \bf{perceptron learning algorithm (PLA)}: \rm{Perceptron} learning algorithm \cite{gallant1990perceptron} is proposed by Gallant 
+  in 1990, which is a fast and simple classification algorithm. However, the limitation of perceptron learning algorithm is that it 
+  can only address the data which is linear separable. Thus, the following model connecting layers of perceptrons is proposed:
+
   \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
@@
   likely outcome according to the conditional probability it just recorded.
-
-  \bf{perceptron learning algorithm (PLA)}:
 
@@
 
+\section{PLA}
+  Assume that in a dataset $D$, there are two class labels. A perceptron will determine a data point with unknown class label by formula 
+  \begin{equation}
+    \rm{sign}(w^Tx)
+  \end{equation}
+  where $w$ is
+
 \section{neural network}
@@
 
-\section{PLA}
-
 \section{Experiment result}

### 2023-04-06 hw1/paper/main.tex
update SVM-GA result

@@
   \end{equation}
-  where $w$ is
+  where $w$ is the weight
 
@@
     random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
-    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
+    SVM-GA           & $1.8462$ & $76.6616 \pm \z{4.0301}$          & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                  & $75 \pm \z{4}$\\
     Neural Network   & $3.2$   & $81.7910 \pm \z{2.0294}$           & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\

### 2023-04-06 hw1/paper/main.tex
update PLA

@@
 \section{PLA}
-  Assume that in a dataset $D$, there are two class labels. A perceptron will determine a data point with unknown class label by formula 
+  Assume that in a dataset $D$, there are two class labels, $0$ and $1$. A perceptron will determine a data point with unknown 
+  class label by formula 
   \begin{equation}
@@
   \end{equation}
-  where $w$ is the weight
+  where $w$ is the weight, and the $\rm{sign}$ function is defined as 
+  \begin{equation}
+    \rm{sign}(x)=\begin{cases}1&,\rm{if }x>0\\0&,\rm{otherwise}\end{cases}
+  \end{equation}
+  The perceptron can update the weight dynamically by formula 
+  \begin{equation}
+    w_{t+1}\leftarrow w_t+y_{n(t)}x_{n(t)} \text{ when sign}(w^T_tx_{n(t)})\neq y_{n(t)}
+  \end{equation}
+  In \cite{gallant1990perceptron}, Gallant prove that if the dataset is linear separable, the perceptron learning algorithm will 
+  eventually find a weight $w_T$ which satisfies $\rm{sign}(w^Tx_i)=y_i,\forall i$, in other words, $w_T$ can separate the dataset 
+  by its class labels perfectly.
+  In partice, the dataset is not always linear separable. Therefore, Gallant proposed a algorithm, PLA-pocket. Instead of find a 
+  perfect weight, PLA-pocket picks a weight which minimize the errors in dataset.
 

### 2023-04-06 hw1/PLA_pocket/pla_pocket.py
exe time-add

@@ -1,5 +1,5 @@
 import pandas as pd
-import numpy as np
+import time
 from sklearn.linear_model import Perceptron
 
 # input the data
@@ -20,6 +20,7 @@ num_test = input('Number of tests: ')
 num_test = int(num_test)
 i = 0
 sum_accuracy = 0
+sum_search_time = 0
 while i < num_test:
 
     X_train = train_data.iloc[:,:-1].values
@@ -31,8 +32,15 @@ while i < num_test:
     # train model
     clf.fit(X_train, y_train)
     # calculate accuracy
+    start = time.time()
     accuracy = clf.score(X_test, y_test)
+    end = time.time()
+    search_time = end - start
+    
+    sum_search_time += search_time
     sum_accuracy += accuracy
     i += 1
 
-print(f"Using data {AorB}. The {num_test} times average accuracy rate: {sum_accuracy / num_test:.5f}")
+print(f"Using data {AorB}.")
+print(f" The {num_test} times average accuracy rate: {sum_accuracy / num_test:.5f}")
+print(f" The {num_test} times average search time: {sum_search_time / num_test:.5f}")

### 2023-04-06 hw1/PLA_pocket/pla_pocket.py
search time - add

@@ -36,9 +36,10 @@ while i < num_test:
     accuracy = clf.score(X_test, y_test)
     end = time.time()
     search_time = end - start
-    
+
     sum_search_time += search_time
     sum_accuracy += accuracy
+    
     i += 1
 
 print(f"Using data {AorB}.")

### 2023-04-06 hw1/PLA_pocket/pla_pocket.py
calculte result data

@@ -1,6 +1,8 @@
 import pandas as pd
 import time
 from sklearn.linear_model import Perceptron
+from sklearn import preprocessing
+import numpy as np
 
 # input the data
 while 1:
@@ -21,6 +23,7 @@ num_test = int(num_test)
 i = 0
 sum_accuracy = 0
 sum_search_time = 0
+array = [0 for i in range(num_test)]
 while i < num_test:
 
     X_train = train_data.iloc[:,:-1].values
@@ -39,9 +42,18 @@ while i < num_test:
 
     sum_search_time += search_time
     sum_accuracy += accuracy
+    array[i] = accuracy
     
     i += 1
 
+avg_accuracy = array.mean()
+std_accuracy = array.std()
+normalized_arr = preprocessing.normalize([array])
+nor_avg_acc = normalized_arr.mean()
+nor_std_acc = normalized_arr.std()
 print(f"Using data {AorB}.")
-print(f" The {num_test} times average accuracy rate: {sum_accuracy / num_test:.5f}")
 print(f" The {num_test} times average search time: {sum_search_time / num_test:.5f}")
+print(f" The {num_test} times average accuracy rate: {avg_accuracy:.5f}")
+print(f" The {num_test} times average accuracy rate std: {std_accuracy:.5f}")
+print(f" The {num_test} times normalized average accuracy rate: {nor_avg_acc:.5f}")
+print(f" The {num_test} times normalized average accuracy rate std: {nor_std_acc / num_test:.5f}")

### 2023-04-06 hw1/PLA_pocket/pla_pocket.py
result data-add

@@ -23,7 +23,7 @@ num_test = int(num_test)
 i = 0
 sum_accuracy = 0
 sum_search_time = 0
-array = [0 for i in range(num_test)]
+array = np.array([0.0 for i in range(num_test)])
 while i < num_test:
 
     X_train = train_data.iloc[:,:-1].values
@@ -39,21 +39,19 @@ while i < num_test:
     accuracy = clf.score(X_test, y_test)
     end = time.time()
     search_time = end - start
-
     sum_search_time += search_time
-    sum_accuracy += accuracy
+    # sum_accuracy += accuracy
     array[i] = accuracy
-    
     i += 1
 
 avg_accuracy = array.mean()
 std_accuracy = array.std()
 normalized_arr = preprocessing.normalize([array])
-nor_avg_acc = normalized_arr.mean()
-nor_std_acc = normalized_arr.std()
+avg_nor_acc = normalized_arr.mean()
+std_nor_acc = normalized_arr.std()
 print(f"Using data {AorB}.")
-print(f" The {num_test} times average search time: {sum_search_time / num_test:.5f}")
-print(f" The {num_test} times average accuracy rate: {avg_accuracy:.5f}")
-print(f" The {num_test} times average accuracy rate std: {std_accuracy:.5f}")
-print(f" The {num_test} times normalized average accuracy rate: {nor_avg_acc:.5f}")
-print(f" The {num_test} times normalized average accuracy rate std: {nor_std_acc / num_test:.5f}")
+print(f"The {num_test} times average search time: {sum_search_time / num_test:.5f}")
+print(f"The {num_test} times average accuracy rate: {avg_accuracy:.5f}")
+print(f"The {num_test} times standard deviation of accuracy rate: {std_accuracy:.5f}")
+print(f"The {num_test} times average normalized accuracy rate: {avg_nor_acc:.5f}")
+print(f"The {num_test} times standard deviation of normalized accuracy rate: {std_nor_acc / num_test:.5f}")

### 2023-04-30 midterm/paper/main.tex
rename

--- 2023-04-06 hw1/paper/main.tex
@@
 
-\author{Hsieh Cheng-Han, Hsu Ting Hao, Sun Shih Yu}
+\author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
 \date{April 2023}
@@
 
-  The result show that XXX is the most accurate on the prediction of diabetes.
+  The result show that KNN is the most accurate on the prediction of diabetes and balance the cost of time between accuracy, and since
+  it is deterministic algorithm, it is very stable.
 
@@
 \section{Experiment result}
-  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
-  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
-  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
-  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
-  Table \ref{table:overall} compares all datasets, which show that ...
   \begin{table*}[htb]
@@
     Technique & Search (s)       & testA                              & testA-normalized             & testB                          & testB-normalized \\ \midrule
-    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
+    KNN-Brute-Force  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
     KNN-ANNOY-DFS    & $0.003$   & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
-    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
+    KNN-ANNOY-BFS    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
     decision tree    & $0.009$   & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
-    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
-    SVM-GA           & $1.8462$ & $76.6616 \pm \z{4.0301}$          & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                  & $75 \pm \z{4}$\\
-    Neural Network   & $3.2$   & $81.7910 \pm \z{2.0294}$           & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
-    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
-    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
+    random forest    & $0.004$   & $78.6965 \pm \z{1.7510}$           & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
+    SVM-GA           & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    Neural Network   & $3.2$     & $\bf{81.7910 \pm \z{2.0294}}$      & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
+    Naive Bayes classifier-GA  & $14.29$ & $78.5353 \pm \z{0.0322}$   & $72.6866 \pm 0.0237$         & $77.4038 \pm \z{0.0626}$       & $71 \pm \z{0.0289}$\\
+    PLA-pocket       & $0.00052$ & $63.682 \pm \z{0}$                 & $3.162 \pm 0$                & $63 \pm \z{0}$                 & $3.162 \pm \z{0}$\\ \midrule
     %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
@@
   \end{table*}
+  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
+  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
+  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
+  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
+  Table \ref{table:overall} compares all datasets, which show that KNN with brute force is the best method to predict 
+  diabetes. And since it is deterministic algorithm, it is very stable. The only drawback is the time complexity is $O(n)$ where 
+  $n$ is the number of the data points in dataset. But with ANNOY technique, the time complexity can be reduce to almost $O(\log n)$, 
+  which solve the huge cost of brute force.
 
 \section{Conclusion}
-  The experiment result shows that ...
+  Though PLA-pocket is the fastest method, the accuracy is not ideal. The neural network performs better, but it is not so stable. 
+  While naive Bayes classifier modified by GA has surpurising good performance and stability, which can compete with random forests 
+  in un-normalized dataset. The experiment result shows that KNN method fits best to early predict diabetes. 
+  One thing to note that KNN performs better after normalized the dataset, while others perform the same or even worse, e.g. PLA-pocket. 
+  The reason behind is normalization can make the data points scatter uniformly, which make KNN have better immunity to the wide gap 
+  of data range.
 \bibliographystyle{IEEEtran}

### 2023-04-30 final/paper/main.tex
update final

--- 2023-04-30 midterm/paper/main.tex
@@
 
-\title{The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes}
+\title{TBD}
 
 \author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
-\date{April 2023}
+\date{June 2023}
 \maketitle
@@
 \section*{Abstract}
-  This work compares the accuracy of some classifiers for early the prediction of diabetes. More specifically, 
-  the research compares the accuracy of k-nearest neighbors (KNN) algorithm, decision tree, random forest, 
-  support vector machine (SVM), neural network, naive Bayes classifier, and perceptron learning algorithm (PLA) on the prediction of diabetes, which 
-  the dataset is collected with eight features, times of pregnancy, concentration of glucose in blood, blood 
-  pressure, skin thickness,  concentration of insulin in blood, body mass index (BMI), the value of diabetes 
-  pedigree function and age.
-
-  The result show that KNN is the most accurate on the prediction of diabetes and balance the cost of time between accuracy, and since
-  it is deterministic algorithm, it is very stable.
 
@@
 \label{sec:Introduction}
-  Diabetes is a chronic disease which may cause many complications. There're lots of reason that can put a person 
-  at the highly risk of having diabetes, such as age, obesity, lack of exercies, and more on. So many reasons 
-  interweave together making the manual prediction on diabetes is nearly impossible. However, lots of works \cite{MUJUMDAR2019292} \cite{MAHBOOBALAM2019100204} \cite{10.3389/fgene.2018.00515}
-  show that it is possible to have high accuracy by using machine learning techniques, such as random forest, 
-  K-means clustering, neural network, and so on.
 
-  By collecting the essential data of human body, prediction of diabetes can be turn into classification problem. 
-  Imagine that an individual case with essential data is a point in hyperspace, if it is closer to the cluster
-  having diabetes, this case is more likely to have diabetes in the future, otherwise, this case is more likely 
-  healthy. But there are lots of machine learning techniques born to solve classification problem, it remains a 
-  problem that which technique having the hightest accuracy on the prediction of diabetes.
-
-  To find out which techniques is more suitable to predict diabetes, this work examines the diagnosis of diabetes 
-  using KNN algorithm, decision tree, random forest, SVM, neural network naive Bayes classifier, and PLA.
 \section{Related works}
@@
 
-  \bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
-  method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
-  "birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
-  can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
-  well for prediction of diabetes disease.
-
-  \bf{decision tree}: \rm{Unlike} KNN uses distance to determine the outcome, 
-  decision tree uses a sequence of deicsion that maximize the information gain, which can distinguish the class label of 
-  data as much as possible, to determine the outcome. Many works \cite{5893838} \cite{8342938} have applied deicsion tree 
-  method and gain a good accuracy. The advantage of decision tree is fast, easy to implement, and the decision is clear. 
-  But the disadvantage is that it is very likely over-fitting and the structure of tree will become more complex with the 
-  more the class labels. To solve this problem, the following techniques is developed:
-
-  \bf{random forst}: \rm{Instead} of a signle decision tree, random forest use lots of decision trees, which form a "forest". 
-  The decision trees are constructed by random subset of dataset. The key differs random forest from decision tree is that 
-  while decision trees consider all the possible feature splits, random forests only select a subset of those features, which 
-  reduce the risk of overfitting, bias, and overall variance. In \cite{7972337} \cite{10.1007/978-981-16-2164-2_19}, random 
-  forest shows that it can greatly reduce the problem of over-fitting of the single decision tree, and gain an ever higher accuracy.
-
-  \bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
-  $0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
-  binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
-  method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
-  feature space.
-
-  \bf{perceptron learning algorithm (PLA)}: \rm{Perceptron} learning algorithm \cite{gallant1990perceptron} is proposed by Gallant 
-  in 1990, which is a fast and simple classification algorithm. However, the limitation of perceptron learning algorithm is that it 
-  can only address the data which is linear separable. Thus, the following model connecting layers of perceptrons is proposed:
-
-  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
-  layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
-  After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
-  training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
-  structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
-  have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
-
-  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
-  theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
-  And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
-  likely outcome according to the conditional probability it just recorded.
-
-\section{KNN}
-  \rm{The} rough process of KNN algorithm is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
-  $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
-  a data with unknown class label is given, denoted $(X, Y)$. By a preset distance function $d(P, Q)$, ordering the dataset 
-  as $(X_{(1)}, Y_{(1)}), (X_{(2)}, Y_{(2)}), \cdots, (X_{(N)}, Y_{(N)})$ where $d(X_{(1)}, X)\leq d(X_{(2)}, X)\leq\cdots\leq d(X_{(N)}, X)$. 
-  Pick the $k$-first class labels to determine the unknow class label, $Y$.
-
-  The algorithm to find $k$ nearest neighbors is the soul of KNN algorithm. The naive way to do that is brute force. By calculating every 
-  distance between the dataset and the undetermined data, the desired class can be easily obtained. The time complexity of brute force is $O(n)$. 
-  Another way to find $k$ nearest neighbors is approximate nearest neighbors oh yeah (ANNOY). This approximate algorithm is used at Spotify 
-  for music recommendations. 
-  \begin{figure*}[htb]
-    \centering
-    \includegraphics[scale=0.5]{assets/ANNOY-split.png}
-    \caption{The region split by ANNOY.}
-    \label{fig:ANNOY_split}
-  \end{figure*}
-
-  \begin{figure*}[htb]
-    \centering
-    \includegraphics[scale=0.5]{assets/ANNOY-tree.png}
-    \caption{The tree structure used by ANNOY.}
-    \label{fig:ANNOY_tree}
-  \end{figure*}
-  Fig.
-\ref{fig:ANNOY_split} and Fig.
-\ref{fig:ANNOY_tree} give illustrations of how ANNOY works.
-The process of ANNOY is detailed as follow: In every iteration, two points are randomly chosen, denoted $\vec x_1,\vec x_2$,
-  and the hyperplane in the middle, whose equation is $\vec n^T\vec x=(\vec x_1-\vec x_2)^T\vec x=(\vec x_1-\vec x_2)^T(\vec x_1+\vec x_2)/2=b$ 
-  separates all the points in dataset into two kind, "below" ($\vec n^T\vec x<b$) or "above" ($\vec n^T\vec x>b$). Also, in every iteration, a 
-  binary tree structure is constructed whose left child contains all the points "below" the hyperplane and right child contains all the points "above". 
-  The end condition is when a side of hyperplane contains points no more than $M$, which is a preset parameter. 
-  When query a $k$ nearest neighbors of a point, recursively determine if the point "below" or "above" the hyperplane until reaching the leaf node. 
-  The time complexity of construction is $O(n)$, and the time complexity of query is $O(\log n)$.
-  But since the region searched may have less $k$ points, the search path shall cover both nodes if the point is too close to the hyperplane. This 
-  techniques though may increase the search time, still, it can greatly increase the accuracy of searching.
-
-\section{decision tree}
-  Consider a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
-  below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
-  $D'_j$. The decision tree will adopt $\arg\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
-  and then recursively construct the tree until the data in separated dataset have the same class label. 
-  When a data with unknown class label comes, a decision tree determines recursively by the decision node until the leaf node.
-  The function of calculating information, $I$, can be various from implementation. The most famous two information function is 
-  entropy, and gini impurity. The formula of information entropy is 
-  \begin{equation}
-    I_H(X)=-\sum_{x}p(x)\log_2p(x) 
-  \end{equation}
-  and gini impurity is 
-  \begin{equation}
-    I_G(X)=1-\sum_{x}p(x)^2
-  \end{equation}
-
-\section{random forest}
-  Given the fact that a signle decision tree can be easily over-fitting, a technique called "random forest" is developed. By 
-  constructing $m$ decision trees with randomized subsets of training dataset, the different decision trees forms a "forest". 
-  The process that random forest determine a data with unknown class label can be outlined as follow: suppose for a coming data, 
-  $c_i$ decision trees in a random forest classify it as class $i$. Then the random forest will classify the data as class $\arg\max c_i$.
-
-\section{SVM-GA}
-  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
-  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
-  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
-  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
-  data is non-linearly separable. 
-  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
-  the occurrence of non-linear separability: 
-	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
-  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
-  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
-  not have binary class labels. 
-  Based on \cite{santhanam2015application}, we can use genetic algorithm (GA) to achieve finding better hyperplanes. The following are the 
-  steps to find the hyperplane using a GA: Firstly, decide the level of generations ($l$), population size ($n$), 
-  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
-  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
-  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
-  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
-  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
-  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
-  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
-  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
-  is found.
-
-\section{PLA}
-  Assume that in a dataset $D$, there are two class labels, $0$ and $1$. A perceptron will determine a data point with unknown 
-  class label by formula 
-  \begin{equation}
-    \rm{sign}(w^Tx)
-  \end{equation}
-  where $w$ is the weight, and the $\rm{sign}$ function is defined as 
-  \begin{equation}
-    \rm{sign}(x)=\begin{cases}1&,\rm{if }x>0\\0&,\rm{otherwise}\end{cases}
-  \end{equation}
-  The perceptron can update the weight dynamically by formula 
-  \begin{equation}
-    w_{t+1}\leftarrow w_t+y_{n(t)}x_{n(t)} \text{ when sign}(w^T_tx_{n(t)})\neq y_{n(t)}
-  \end{equation}
-  In \cite{gallant1990perceptron}, Gallant prove that if the dataset is linear separable, the perceptron learning algorithm will 
-  eventually find a weight $w_T$ which satisfies $\rm{sign}(w^Tx_i)=y_i,\forall i$, in other words, $w_T$ can separate the dataset 
-  by its class labels perfectly.
-  In partice, the dataset is not always linear separable. Therefore, Gallant proposed a algorithm, PLA-pocket. Instead of find a 
-  perfect weight, PLA-pocket picks a weight which minimize the errors in dataset.
-
-\section{neural network}
-  Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or 
-  not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have 
-  to find the structure of the hidden layer with NAS.
-  We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, 
-  which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, 
-  which is more then 16 and less than 256, like above.We are aiming to find the approximate solution 
-  $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in 
-  the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature 
-  $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the 
-  parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, 
-  we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, 
-  train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference 
-  $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability 
-  of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than 
-  $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number 
-  in $f^*$ to $n, 16 \leq n \leq 256$.
-  \begin{equation}
-	  f^* = 
-	  \begin{cases}
-	  f^{**},  &\Delta L\le 0 \\
-	  f^{**},  &\Delta L \ge 0 \text{ and } R^*<e^{\frac{\Delta L}{T}} \\ 
-	  f^{*},   &\text{else}\\
-	  \end{cases}
-  \end{equation}
-
-  After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate 
-  solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing 
-  can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
-
-\section{Naive Bayes classifier-GA}
-  Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 
-  $i$-th class is $P(C_k\mid \bf{x})$ where $C_k$ is the event that data points $\bf{x}=(x_1,\cdots,x_n)$ belongs to $k$-th class.
-  By using Bayes' theorem, the probability can be rewritten as 
-  \begin{equation}
-    \label{eqn:bayes}
-    P(C_k\mid x)=\frac{P(C_k)P(\bf{x}\mid C_k)}{P(\bf{x})}
-  \end{equation}
-  In partice, 
-  there is interest only in the numerator of that fraction, because the denominator does not depend on $C_k$ and the values of the 
-  features that are given, so the denominator is effectively constant. 
-  Then, by chain rule of conditional probability, the numerator of Eq. \ref{eqn:bayes} can be rewritten as
-  \begin{equation}
-    \label{eqn:rebayes}
-    \begin{split}
-      &P(C)P(x_1\mid C_k)P(x_2,\cdots,x_n\mid C_k,x_1)
-      \\&=\cdots
-      \\&=P(C)P(x_1\mid C_k)\cdots P(x_n\mid C_k,x_1,\cdots,x_{n-1})
-    \end{split}
-  \end{equation}
-
-  Now assume that all features in $\bf{x}$ is mutually independent, $P(x_i\mid x_j, C_k)$ will be equal to $P(x_i\mid C_k)$. 
-  Thus, the probability is 
-  \begin{equation}
-    \label{eqn:prob_classifier}
-    P(C_k\mid x)=\frac{P(C_k)\prod^n_{i=1}P(x_i\mid C_k)}{Z}
-  \end{equation}
-  where $Z$ is a constant. 
-  With Eq. \ref{eqn:prob_classifier}, a data points with unknown class label can be classified by choosing the most possible class: 
-  \begin{equation}
-    \label{eqn:classifier}
-    \arg\max_k P(C_k)\prod^n_{i=1}P(x_i=x'_i\mid C_k)
-  \end{equation}
-
-  The problem is, when given is a continuous value instead of individual events, it need to be partitioned accroding to specific value 
-  which below this value is an individual event while above is other evnet. However, the difficulty is how to find the best partition 
-  that can fit the model best. By using gene alogrithm, the answer can be easily found. First, record maximum and minimum values of 
-  given data in each dimension. Second, randomly partition data in each dimension according the maximum and minimum value recorded before 
-  and repeat 100 times to generate enoguh species. Third, testing the accuracy of the model on the training data and keep top $K$ 
-  good species and kill the rest. Then, let the these elites prodece offsprings, which means pass their partitions to offsprings. 
-  When there is enough offsprings, all offsprings are going to have mutation, the partitions may slightly shift, 
-  merge, split, disappear, or keep originally. Finally, repeat the whole iteration until found the partition that is close to optimal 
-  solution after $T$ iterations.
+\section{main section}
 
@@
   \begin{table*}[htb]
-    %\normalsize
-    %\centering
     \newcommand{\z}{\phantom{0}}
@@
     PLA-pocket       & $0.00052$ & $63.682 \pm \z{0}$                 & $3.162 \pm 0$                & $63 \pm \z{0}$                 & $3.162 \pm \z{0}$\\ \midrule
-    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
     \end{tabular}
@@
   \end{table*}
-  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
-  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
-  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
-  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
-  Table \ref{table:overall} compares all datasets, which show that KNN with brute force is the best method to predict 
-  diabetes. And since it is deterministic algorithm, it is very stable. The only drawback is the time complexity is $O(n)$ where 
-  $n$ is the number of the data points in dataset. But with ANNOY technique, the time complexity can be reduce to almost $O(\log n)$, 
-  which solve the huge cost of brute force.
 
 \section{Conclusion}
-  Though PLA-pocket is the fastest method, the accuracy is not ideal. The neural network performs better, but it is not so stable. 
-  While naive Bayes classifier modified by GA has surpurising good performance and stability, which can compete with random forests 
-  in un-normalized dataset. The experiment result shows that KNN method fits best to early predict diabetes. 
-  One thing to note that KNN performs better after normalized the dataset, while others perform the same or even worse, e.g. PLA-pocket. 
-  The reason behind is normalization can make the data points scatter uniformly, which make KNN have better immunity to the wide gap 
-  of data range.
+
 \bibliographystyle{IEEEtran}

### 2023-04-30 final/include/Data.h

@@ -1,0 +1,495 @@
+#ifndef __DATA_H__
+#define __DATA_H__
+#include <vector>
+#include <iostream>
+#include <initializer_list>
+#include <cmath>
+#include <functional>
+#include <limits>
+#include <utility>
+
+constexpr double minerr = std::numeric_limits<double>::epsilon();
+
+template<typename T>
+class point_t;
+
+template<typename T>
+class hyperplane_t;
+
+template<typename T, typename U>
+class dataset_t;
+
+// add
+template<typename T> point_t<T>  operator+(const point_t<T>& a, const point_t<T>& b);
+// dot
+template<typename T> T operator*(const point_t<T>& a, const point_t<T>& b);
+// scale
+template<typename T> point_t<T> operator*(const point_t<T>& a, T scale);
+template<typename T> point_t<T> operator*(T scale, const point_t<T>& a);
+template<typename T> point_t<T> operator/(const point_t<T>& a, T scale);
+// minus
+template<typename T> point_t<T> operator-(const point_t<T>& a, const point_t<T>& b);
+// point_t cout
+template<typename T> std::ostream& operator<<(std::ostream& os, const point_t<T>& a);
+
+// distance
+template<typename T> point_t<T> midpoint(const point_t<T>& a, const point_t<T>& b);
+template<typename T> double euclidean_dist(const point_t<T>& a, const point_t<T>& b);
+template<typename T> double euclidean_dist(const point_t<T>& x0, const hyperplane_t<T>& plane);
+template<typename T> double euclidean_dist(const hyperplane_t<T>& plane, const point_t<T>& x0);
+template<typename T> double minkowski_dist(const point_t<T>& a, const point_t<T>& b, int p);
+
+// hyperplane utility
+template<typename T> bool operator<(const hyperplane_t<T>& plane, const point_t<T>& x);
+template<typename T> bool operator>(const hyperplane_t<T>& plane, const point_t<T>& x);
+template<typename T> bool operator<(const point_t<T>& x, const hyperplane_t<T>& plane);
+template<typename T> bool operator>(const point_t<T>& x, const hyperplane_t<T>& plane);
+template<typename T> bool onplane(const point_t<T>& x, const hyperplane_t<T>& plane);
+// hyperplane_t cout
[…]

### 2023-04-30 final/include/Dataloader.h

@@ -1,0 +1,131 @@
+#ifndef __DATALOADER_H__
+#define __DATALOADER_H__
+#include <vector>
+#include <utility>
+#include <string>
+#include <string_view>
+#include <map>
+#include <fstream>
+#include <charconv>
+#include "Data.h"
+
+template<typename T, typename U>
+class Dataloader_t
+{
+public:
+    // record the name of i-th field
+    std::vector<std::string_view> tags;
+    // data
+    dataset_t<T, U> train_data, test_data;
+
+    std::fstream fs;
+
+    Dataloader_t() = default;
+
+    void load(std::string_view& path, dataset_t<T, U>& dataset);
+    void load_test(std::string_view&& path);
+    void load_test(std::string_view& path);
+    void load_train(std::string_view&& path);
+    void load_train(std::string_view& path);
+	
+	void load_train(const dataset_t<T, U>& dataset);
+	void load_train(dataset_t<T, U>&& dataset);
+	void load_test(const dataset_t<T, U>& dataset);
+	void load_test(dataset_t<T, U>&& dataset);
+};
+
+static std::vector<std::string_view> split(std::string_view s, char delimiter = ',')
+{
+    std::vector<std::string_view> ret;
+
+    std::size_t cur;
+    while ((cur = s.find(delimiter)) != std::string_view::npos)
+    {
+        ret.emplace_back(s.substr((size_t)0, cur));
+        s = s.substr(cur+1);
+    }
+    ret.emplace_back(s);
+    return ret;
+}
+
+template<typename T, typename U>
+void Dataloader_t<T, U>::load(std::string_view& path, dataset_t<T, U>& dataset)
+{
+    dataset.clear();
+
+    std::fstream fs;
+    fs.open(path.data());
+    if (fs.fail())
+    {
+        std::cerr << "fail to open the file: " << path << std::endl;
+        std::cerr << "stop the process ..." << std::endl;
+        exit(1);
+    }
+    auto& tags = this->tags;
+    std::string s; fs >> s;
+    std::string_view rawlabels{s};
+    tags = split(rawlabels, ',');
+    while (fs >> s)
+    {
+        std::string_view rawdata{s};
+        std::vector<std::string_view> alldata = split(rawdata, ',');
+
+        U label = std::atoi(alldata.back().data());
+        alldata.pop_back();
+
+        point_t<T> data;
+        for (auto& s : alldata)
+        {
+            char *end_;
[…]

### 2023-04-30 final/include/Datatransformer.h

@@ -1,0 +1,136 @@
+#ifndef __DATATRANSFORMER_H__
+#define __DATATRANSFORMER_H__
+#include "Data.h"
+#include <vector>
+#include <algorithm>
+#include <random>
+
+template<typename T, typename U>
+class Datatransformer_t
+{
+public:
+	Datatransformer_t() = default;
+	static dataset_t<T, U> gaussian_noise(const dataset_t<T, U>& dataset, double mu, double sigma);
+	static dataset_t<T, U> normalize(const dataset_t<T, U>& dataset);
+    static dataset_t<T, U> random_pick(const dataset_t<T, U>& dataset, std::size_t n);
+    static std::vector<dataset_t<T, U>> split(const dataset_t<T, U>& dataset, std::size_t n);
+	static dataset_t<T, U> drop_attr_is_x(const dataset_t<T, U>& dataset, std::size_t attr, const T& x);
+	static dataset_t<T, U> drop_attrs_are_xs(const dataset_t<T, U>& dataset, const std::vector<std::size_t>& attrs, const std::vector<T>& xs);
+};
+
+template<typename T, typename U>
+dataset_t<T, U> Datatransformer_t<T, U>::gaussian_noise(const dataset_t<T, U>& dataset_, double mu, double sigma)
+{
+    std::default_random_engine genator;
+	std::normal_distribution<T> normal_rd(mu, sigma);
+	auto rd = std::bind(normal_rd, genator);
+	dataset_t<T, U> dataset{dataset_};
+	for (auto& data : dataset.data)
+		data += point_t<T>{data.point.size(), rd};
+	return dataset;
+}
+
+struct sigma_mu
+{
+	double sigma, mu;
+	sigma_mu() = default;
+	sigma_mu(double mu_, double sigma_): sigma{sigma_}, mu{mu_} {}
+};
+
+template<typename T, typename U>
+dataset_t<T, U> Datatransformer_t<T, U>::normalize(const dataset_t<T, U>& dataset_)
+{
+	dataset_t<T, U> dataset{dataset_};
+	std::vector<sigma_mu> colinfo;
+	std::vector<T> sum, sum2;
+
+	sum.resize(dataset_.column());
+	std::fill(sum.begin(), sum.end(), 0);
+	sum2.resize(dataset_.column());
+	std::fill(sum2.begin(), sum2.end(), 0);
+	colinfo.resize(dataset_.column());
+
[…]

### 2023-04-30 final/KNN/main.cpp
update KNN

@@ -1,0 +1,88 @@
+#include <iostream>
+#include <memory>
+#include <cmath>
+#include <chrono>
+#include "src/KNN.h"
+#include "src/Brute.h"
+#include "src/Annoy.h"
+#include "../include/Dataloader.h"
+#include "../include/Datatransformer.h"
+
+using data_t = double;
+using label_t = int;
+
+int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
+{
+    std::string_view train_path = argv[4];
+    std::string_view test_path  = argv[6];
+    //std::cerr << "Train data path is " << train_path << std::endl;
+    //std::cerr << "Test data path is " << test_path << std::endl;
+
+    
+    std::size_t k = (std::size_t)std::atoi(argv[12]);
+
+    // data is double, label is int
+    Dataloader_t<data_t, label_t> dataloader;
+    
+    //std::cerr << "Load the train data..." << std::endl;
+    dataloader.load_train(train_path);
+    //dataloader.load_train(Datatransformer_t<data_type, label_type>::drop_attrs_are_xs(dataloader.train_data, std::vector<std::size_t>{2,3,4}, std::vector<data_type>{0,0,0}));
+
+    //std::cerr << "Load the test data..." << std::endl;
+    dataloader.load_test(test_path);
+    //std::cerr << "Complete loading" << std::endl << std::endl;
+	if (strcmp(argv[8], "true") == 0)
+	{
+		//std::cerr << "Normalize the dataset..." << std::endl;
+		dataloader.load_train(Datatransformer_t<data_t, label_t>::normalize(dataloader.train_data));
+		dataloader.load_test(Datatransformer_t<data_t, label_t>::normalize(dataloader.test_data));
+	}
+	//std::cerr << "===================================================================" << std::endl;
+	
+    KNN_t<data_t, label_t> KNN;
+    //std::cerr << "Set knn search algorithm: " << argv[10] << std::endl;
+	if (strcmp(argv[10], "brute") == 0)
+		KNN.set_knn_method(std::make_shared<brute_force<data_t, label_t>>());
+	else if (strcmp(argv[10], "annoy") == 0)
+	{
+		std::size_t maxpoint = (std::size_t)std::atoi(argv[16]);
+	    //std::cerr << "ANNOY: Max point count in the leaf of search tree = " << maxpoint << std::endl;
[…]

### 2023-04-30 final/KNN/src/Annoy.h

@@ -1,0 +1,157 @@
+#ifndef __ANNOY_H__
+#define __ANNOY_H__
+#include "../../include/Data.h"
+#include <vector>
+#include <queue>
+#include <random>
+
+template<typename T, typename U>
+class node_t
+{
+public:
+	bool leaf = false;
+	dataset_t<T, U> dataset;
+	
+	hyperplane_t<T> mid;
+
+	node_t<T, U> *l, *r;
+	node_t() = default;
+	node_t(const hyperplane_t<T>& mid_): mid{mid_} {}
+	node_t(hyperplane_t<T>&& mid_): mid{std::forward<decltype(mid_)>(mid_)} {}
+};
+
+template<typename T, typename U>
+class tree_t
+{
+public:
+	node_t<T, U>* root;
+};
+
+template<typename T, typename U>
+class annoy : public KNN_Method_t<T, U>
+{
+public:
+    tree_t<T, U> tree;
+	std::size_t maxpoint = 13;
+	std::string search_method = "bfs";
+	double bfs_threhold = 20;
+	annoy() = default;
+	annoy(std::size_t maxp): maxpoint{maxp} {}
+	dataset_t<T, U> knn(const dataset_t<T, U>& dataset, const point_t<T>& data, std::size_t k);
+	void build(const dataset_t<T, U>& dataset) override;
+    void dfs_build(node_t<T, U>*& now, const dataset_t<T, U>& dataset);
+    dataset_t<T, U> dfs(node_t<T, U>* now, const point_t<T>& data);
+	dataset_t<T, U> bfs(node_t<T, U>* root, const point_t<T>& data, double threhold);
+};
+
+template<typename T, typename U>
+dataset_t<T, U> annoy<T, U>::dfs(node_t<T, U>* now, const point_t<T>& data)
+{
+    if (now == nullptr)
+    {
+        std::cerr << "annoy<T, U>::dfs(): now is nullptr" << std::endl;
+        exit(1);
+    }
+	if (now->leaf) return now->dataset;
+	if (data < now->mid)
+		return dfs(now->l, data);
+	return dfs(now->r, data);
+}
+
+template<typename T, typename U>
+dataset_t<T, U> annoy<T, U>::bfs(node_t<T, U>* root, const point_t<T>& data, double threhold)
+{
+	std::priority_queue<std::pair<double, node_t<T, U>*>> pq;
+	pq.emplace(euclidean_dist(root->mid, data), root);
+	dataset_t<T, U> ret;
+	while (!pq.empty())
+	{
[…]

### 2023-04-30 final/KNN/src/Brute.h

@@ -1,0 +1,44 @@
+#ifndef __BRUTE_H__
+#define __BRUTE_H__
+#include <iostream>
+#include <algorithm>
+#include <cstring>
+#include <utility>
+#include "../../include/Data.h"
+#include "KNN_Method.h"
+
+template<typename T, typename U>
+class brute_force: public KNN_Method_t<T, U>
+{
+public:
+    // find k-nearest points related to "data"
+	dataset_t<T, U> knn(const dataset_t<T, U>& dataset, const point_t<T>& data, std::size_t k) override;
+};
+
+static std::vector<std::size_t> argsort(const std::vector<double>& dist)
+{
+    std::vector<std::pair<std::size_t, double>> arg;
+    std::vector<std::size_t> result;
+    for (std::size_t i = 0; i < dist.size(); ++i)
+        arg.emplace_back(i, dist[i]);
+    std::sort(arg.begin(), arg.end(), [](const auto& lhs, const auto& rhs) { return lhs.second < rhs.second; });
+    for (std::size_t i = 0; i < dist.size(); ++i)
+        result.emplace_back(arg[i].first);
+    return result;
+}
+
+template<typename T, typename U>
+dataset_t<T, U> brute_force<T, U>::knn(const dataset_t<T, U>& dataset, const point_t<T>& target, std::size_t k)
+{
+    std::vector<double> dist;
+    for (const auto& data : dataset.data)
+        dist.emplace_back(euclidean_dist(data, target));
+
+    std::vector<std::size_t> arg = argsort(dist);
+    arg.erase(arg.begin() + k, arg.end());
+    dataset_t<T, U> ret;
+    for (const auto& id : arg) ret.emplace_back(dataset.data[id], dataset.label[id]);
+    return ret;
+}
+
+#endif

### 2023-04-30 final/KNN/src/KNN.h

@@ -1,0 +1,55 @@
+#ifndef __KNN_H__
+#define __KNN_H__
+#include <vector>
+#include <memory>
+#include <utility>
+#include "../../include/Data.h"
+#include "KNN_Method.h"
+
+template<typename T, typename U>
+class KNN_t
+{
+public:
+    dataset_t<T, U> train_data;
+    std::shared_ptr<KNN_Method_t<T, U>> KNN_Method;
+
+    KNN_t() = default;
+    
+    void train(const dataset_t<T, U>& dataset)
+	{
+		if (KNN_Method == nullptr)
+		{
+			std::cerr << "KNN_Method is nullptr, please set knn method first." << std::endl;
+			exit(1);
+		}
+		this->train_data = dataset;
+		this->KNN_Method->build(this->train_data);
+	}
+    void train(dataset_t<T, U>&& dataset) 
+	{ 
+		if (KNN_Method == nullptr)
+		{
+			std::cerr << "KNN_Method is nullptr, please set knn method first." << std::endl;
+			exit(1);
+		}
+		this->train_data = std::move(dataset); 
+		this->KNN_Method->build(this->train_data);
+	}
+
+	point_t<U> predict(const dataset_t<T, U>& test_data, std::size_t k)
+    {
+	    return this->KNN_Method->predict(this->train_data, test_data, k);
+    }
+    point_t<U> predict(const std::vector<point_t<T>>& test_data, std::size_t k)
+    {
+        return this->KNN_Method->predict(this->train_data, test_data, k);
+    }
+	void set_knn_method(std::shared_ptr<KNN_Method_t<T, U>> km)
+    {
+    	this->KNN_Method = km;
+    }
+};
+// KNN_t<T, U> KNN;
+// KNN.train(...);
+// KNN.predict(test_data, k);
+#endif

### 2023-04-30 final/KNN/src/KNN_Method.h

@@ -1,0 +1,55 @@
+#ifndef __KNN_METHOD_H__
+#define __KNN_METHOD_H__
+#include <algorithm>
+#include <vector>
+#include <map>
+#include "../../include/Data.h"
+
+template<typename T, typename U>
+class KNN_Method_t
+{
+public:
+	KNN_Method_t() = default;
+	virtual ~KNN_Method_t() = default;
+	
+	// build essential data structure if need
+	virtual void build([[maybe_unused]]const dataset_t<T, U>& dataset) {}
+    // find the k-nearest points related to "data"
+	virtual dataset_t<T, U> knn(const dataset_t<T, U>& dataset, const point_t<T>& data, std::size_t k) = 0;
+    // classify the target
+	virtual U predict(const dataset_t<T, U>& dataset, const point_t<T>& target, std::size_t k);
+    // classify the targets
+	virtual point_t<U> predict(const dataset_t<T, U>& dataset, const dataset_t<T, U>& targets, std::size_t k);
+	virtual point_t<U> predict(const dataset_t<T, U>& dataset, const std::vector<point_t<T>>& targets, std::size_t k);
+};
+
+// classify the target
+template<typename T, typename U>
+U KNN_Method_t<T, U>::predict(const dataset_t<T, U>& dataset, const point_t<T>& target, std::size_t k)
+{
+    dataset_t<T, U> knns = this->knn(dataset, target, k);
+	std::map<U, std::size_t> cnt;
+	std::pair<std::size_t, U> maxkind{0, 0};
+	for (std::size_t nearby = 0; nearby < knns.size(); ++nearby) { ++cnt[knns.label[nearby]]; }
+	for (auto& [label, howmany] : cnt) maxkind = std::max(maxkind, std::pair{howmany, label});
+	return maxkind.second;
+}
+
+// classify the targets
+template<typename T, typename U>
+point_t<U> KNN_Method_t<T, U>::predict(const dataset_t<T, U>& dataset, const dataset_t<T, U>& targets, std::size_t k)
+{
+    point_t<U> ret;
+    for (const auto& data : targets)
+        ret.emplace_back(this->predict(dataset, data, k));
+    return ret;
+}
+template<typename T, typename U>
+point_t<U> KNN_Method_t<T, U>::predict(const dataset_t<T, U>& dataset, const std::vector<point_t<T>>& targets, std::size_t k)
+{
+    point_t<U> ret;
+    for (const auto& data : targets)
[…]

### 2023-04-30 final/preprocess/Autoencoder/Autoencoder.py
update Autoencoder

@@ -1,0 +1,45 @@
+import torch
+from torch import nn
+
+class encoder(nn.Module):
+    def __init__(self, input_dim, output_dim):
+        super().__init__()
+        self.net = nn.Sequential(
+            nn.Linear(input_dim, 128)
+            nn.Linear(128, 64)
+            nn.Linear(64, 32)
+            nn.Linear(32, output_dim)
+        )
+    def forward(self, x):
+        return self.net(x)
+
+class decoder(nn.Module):
+    def __init__(self, input_dim, output_dim):
+        super.__init__()
+        self.net = nn.Sequential(
+            nn.Linear(input_dim, 32)
+            nn.Linear(32, 64)
+            nn.Linear(64, 128)
+            nn.Linear(128, output_dim)
+        )
+    def forward(self, x):
+        return self.net(x)
+
+class autoencoder(nn.Module):
+    def __init__(self, input_dim, output_dim, opt, lr):
+        super.__init__()
+        self.encoder = encoder(input_dim, output_dim)
+        self.decoder = decoder(output_dim, input_dim)
+        self.net = nn.Sequential(
+            encoder(input_dim, output_dim),
+            decoder(output_dim, input_dim)
+        )
+        self.opt = opt(self.parameters(), lr=lr)
+    def forward(self, x):
+        return self.net(x)
+    def train(self, x, y, loss_fn):
+        loss = loss_fn(self.net(x), y)
+
+        self.opt.zero_grad()
+        loss.backward()
+        self.opt.step()

### 2023-04-30 final/preprocess/Autoencoder/main.py

@@ -1,0 +1,9 @@
+import sys
+import torch
+from Autoencoder import autoencoder
+import pandas as pd
+
+input_dim = int(sys.argv[1])
+output_dim = int(sys.argv[2])
+encoder = autoencoder(input_dim, output_dim)
+

### 2023-05-01 final/preprocess/Autoencoder/Autoencoder.py
update autoencoder

@@ -43,3 +43,6 @@ class autoencoder(nn.Module):
         self.opt.zero_grad()
         loss.backward()
         self.opt.step()
+        return loss
+    def encode(self, x):
+        return self.encoder(x)

### 2023-05-01 final/preprocess/Autoencoder/main.py

@@ -1,9 +1,31 @@
 import sys
 import torch
+from torch import nn
 from Autoencoder import autoencoder
 import pandas as pd
 
+batch_size = 16
+
 input_dim = int(sys.argv[1])
 output_dim = int(sys.argv[2])
+device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
 encoder = autoencoder(input_dim, output_dim)
+encoder.to(device)
+rX = pd.read_csv(sys.argv[3]).to_numpy()
+rY = pd.read_csv(sys.argv[4]).to_numpy()
 
+X = np.array([rX[i:(i+1)*batch_size] for i in range(len(X)//batch_size)])
+Y = np.array([rY[i:(i+1)*batch_size] for i in range(len(Y)//batch_size)])
+X = torch.Tensor(X).to(device)
+Y = torch.Tensor(Y).to(device)
+
+for i in range(ecoph):
+    loss = encoder.train(X[i % len(X)], Y[i % len(Y)], nn.CrossEntropyLoss)
+    if _ % 100:
+        print(f"loss = {loss}")
+
+X = pd.read_csv(sys.argv[5]).to_numpy()
+Y = pd.read_csv(sys.argv[6]).to_numpy()
+Z = encoder.encode(X)
+
+Z.to_csv(sys.argv[7])

### 2023-05-01 final/preprocess/Autoencoder/Autoencoder.py
update Autoencoder

@@ -5,9 +5,9 @@ class encoder(nn.Module):
     def __init__(self, input_dim, output_dim):
         super().__init__()
         self.net = nn.Sequential(
-            nn.Linear(input_dim, 128)
-            nn.Linear(128, 64)
-            nn.Linear(64, 32)
+            nn.Linear(input_dim, 128),
+            nn.Linear(128, 64),
+            nn.Linear(64, 32),
             nn.Linear(32, output_dim)
         )
     def forward(self, x):
@@ -15,11 +15,11 @@ class encoder(nn.Module):
 
 class decoder(nn.Module):
     def __init__(self, input_dim, output_dim):
-        super.__init__()
+        super().__init__()
         self.net = nn.Sequential(
-            nn.Linear(input_dim, 32)
-            nn.Linear(32, 64)
-            nn.Linear(64, 128)
+            nn.Linear(input_dim, 32),
+            nn.Linear(32, 64),
+            nn.Linear(64, 128),
             nn.Linear(128, output_dim)
         )
     def forward(self, x):
@@ -27,7 +27,7 @@ class decoder(nn.Module):
 
 class autoencoder(nn.Module):
     def __init__(self, input_dim, output_dim, opt, lr):
-        super.__init__()
+        super().__init__()
         self.encoder = encoder(input_dim, output_dim)
         self.decoder = decoder(output_dim, input_dim)
         self.net = nn.Sequential(

### 2023-05-01 final/preprocess/Autoencoder/main.py

@@ -1,5 +1,7 @@
 import sys
+import math
 import torch
+import numpy as np
 from torch import nn
 from Autoencoder import autoencoder
 import pandas as pd
@@ -9,13 +11,21 @@ batch_size = 16
 input_dim = int(sys.argv[1])
 output_dim = int(sys.argv[2])
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-encoder = autoencoder(input_dim, output_dim)
+encoder = autoencoder(input_dim, output_dim, torch.optim.Adadelta, 1)
 encoder.to(device)
+print(f"read_csv:{sys.argv[3]}")
 rX = pd.read_csv(sys.argv[3]).to_numpy()
+print(f"read_csv:{sys.argv[4]}")
 rY = pd.read_csv(sys.argv[4]).to_numpy()
 
-X = np.array([rX[i:(i+1)*batch_size] for i in range(len(X)//batch_size)])
-Y = np.array([rY[i:(i+1)*batch_size] for i in range(len(Y)//batch_size)])
+print(rX.shape)
+print(rY.shape)
+X = np.array_split(rX, len(rX)//batch_size)
+X = np.array(X)
+print(X[-1].shape)
+Y = np.ndarray(np.array_split(rY, batch_size), dtype=np.float64)
+print(X.shape)
+print(Y.shape)
 X = torch.Tensor(X).to(device)
 Y = torch.Tensor(Y).to(device)
 
@@ -24,8 +34,11 @@ for i in range(ecoph):
     if _ % 100:
         print(f"loss = {loss}")
 
+Z = encoder.encode(X).detach().cpu().numpy()
+np.savetxt(sys.argv[7], Z, delimiter = ',')
+
 X = pd.read_csv(sys.argv[5]).to_numpy()
 Y = pd.read_csv(sys.argv[6]).to_numpy()
-Z = encoder.encode(X)
 
-Z.to_csv(sys.argv[7])
+Z = encoder.encode(X).detach().cpu().numpy()
+np.savetxt(sys.argv[8], Z, delimiter = ',')

### 2023-05-01 final/preprocess/Autoencoder/run.sh

@@ -1,0 +1,1 @@
+python main.py 279 32 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv

### 2023-05-01 final/preprocess/Autoencoder/Autoencoder.py
update Autoencoder

@@ -5,11 +5,17 @@ class encoder(nn.Module):
     def __init__(self, input_dim, output_dim):
         super().__init__()
         self.net = nn.Sequential(
-            nn.Linear(input_dim, 128),
+            nn.Linear(input_dim, 512),
+            nn.ReLU(),
+            nn.Linear(512, 256),
+            nn.ReLU(),
+            nn.Linear(256, 128),
+            nn.ReLU(),
             nn.Linear(128, 64),
-            nn.Linear(64, 32),
-            nn.Linear(32, output_dim)
+            nn.ReLU(),
+            nn.Linear(64, output_dim)
         )
+        self.flatten = nn.Flatten()
     def forward(self, x):
         return self.net(x)
 
@@ -17,11 +23,17 @@ class decoder(nn.Module):
     def __init__(self, input_dim, output_dim):
         super().__init__()
         self.net = nn.Sequential(
-            nn.Linear(input_dim, 32),
-            nn.Linear(32, 64),
+            nn.Linear(input_dim, 64),
+            nn.ReLU(),
             nn.Linear(64, 128),
-            nn.Linear(128, output_dim)
+            nn.ReLU(),
+            nn.Linear(128, 256),
+            nn.ReLU(),
+            nn.Linear(256, 512),
+            nn.ReLU(),
+            nn.Linear(512, output_dim),
         )
+        self.flatten = nn.Flatten()
     def forward(self, x):
         return self.net(x)
 
@@ -30,19 +42,14 @@ class autoencoder(nn.Module):
         super().__init__()
         self.encoder = encoder(input_dim, output_dim)
         self.decoder = decoder(output_dim, input_dim)
-        self.net = nn.Sequential(
-            encoder(input_dim, output_dim),
-            decoder(output_dim, input_dim)
-        )
         self.opt = opt(self.parameters(), lr=lr)
+        self.flatten = nn.Flatten()
+    
     def forward(self, x):
-        return self.net(x)
-    def train(self, x, y, loss_fn):
-        loss = loss_fn(self.net(x), y)
+        code = self.encoder(x)
+        decode = self.decoder(code)
+        return code, decode
 
-        self.opt.zero_grad()
-        loss.backward()
-        self.opt.step()
-        return loss
+   
     def encode(self, x):
         return self.encoder(x)

### 2023-05-01 final/preprocess/Autoencoder/main.py

@@ -1,44 +1,76 @@
 import sys
 import math
+import random
 import torch
 import numpy as np
 from torch import nn
 from Autoencoder import autoencoder
 import pandas as pd
+import matplotlib.pyplot as plt
 
-batch_size = 16
+seed = 1
+torch.manual_seed(seed)
+torch.cuda.manual_seed(seed)
+torch.cuda.manual_seed_all(seed)
+np.random.seed(seed)
+random.seed(seed)
+torch.backends.cudnn.benchmark = False
+torch.backends.cudnn.deterministic = True
+
+batch_size = 4
+epoch = 1000
 
 input_dim = int(sys.argv[1])
 output_dim = int(sys.argv[2])
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-encoder = autoencoder(input_dim, output_dim, torch.optim.Adadelta, 1)
+encoder = autoencoder(input_dim, output_dim, torch.optim.Adadelta, 0.5)
 encoder.to(device)
 print(f"read_csv:{sys.argv[3]}")
 rX = pd.read_csv(sys.argv[3]).to_numpy()
+rX = np.nan_to_num(rX, nan = 0, posinf = 999999, neginf = -999999)
 print(f"read_csv:{sys.argv[4]}")
 rY = pd.read_csv(sys.argv[4]).to_numpy()
 
-print(rX.shape)
-print(rY.shape)
-X = np.array_split(rX, len(rX)//batch_size)
-X = np.array(X)
-print(X[-1].shape)
-Y = np.ndarray(np.array_split(rY, batch_size), dtype=np.float64)
-print(X.shape)
-print(Y.shape)
+X = np.array_split(rX, rX.shape[0]//batch_size)
+Y = np.array_split(rY, rY.shape[0]//batch_size)
+X = np.array(X, dtype = np.float64)
+Y = np.array(Y, dtype = np.float64)
 X = torch.Tensor(X).to(device)
 Y = torch.Tensor(Y).to(device)
 
-for i in range(ecoph):
-    loss = encoder.train(X[i % len(X)], Y[i % len(Y)], nn.CrossEntropyLoss)
-    if _ % 100:
-        print(f"loss = {loss}")
+sigma = 1
+loss_fn = nn.MSELoss()
+#loss_fn = nn.CrossEntropyLoss()
+losses = []
+for i in range(epoch):
[…]

### 2023-05-01 final/preprocess/Autoencoder/run.sh

@@ -1,1 +1,1 @@
-python main.py 279 32 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv
+python main.py 279 50 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv loss.png

### 2023-05-01 final/preprocess/Autoencoder/main.py
update Autoencoder

@@ -18,7 +18,7 @@ torch.backends.cudnn.benchmark = False
 torch.backends.cudnn.deterministic = True
 
 batch_size = 4
-epoch = 1000
+epoch = 500
 
 input_dim = int(sys.argv[1])
 output_dim = int(sys.argv[2])

### 2023-05-01 final/preprocess/Autoencoder/main.py
find good autoencoder model

@@ -23,8 +23,6 @@ epoch = 500
 input_dim = int(sys.argv[1])
 output_dim = int(sys.argv[2])
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-encoder = autoencoder(input_dim, output_dim, torch.optim.Adadelta, 0.5)
-encoder.to(device)
 print(f"read_csv:{sys.argv[3]}")
 rX = pd.read_csv(sys.argv[3]).to_numpy()
 rX = np.nan_to_num(rX, nan = 0, posinf = 999999, neginf = -999999)
@@ -38,6 +36,8 @@ Y = np.array(Y, dtype = np.float64)
 X = torch.Tensor(X).to(device)
 Y = torch.Tensor(Y).to(device)
 
+encoder = autoencoder(input_dim, output_dim, torch.optim.Adadelta, 0.5)
+encoder.to(device)
 sigma = 1
 loss_fn = nn.MSELoss()
 #loss_fn = nn.CrossEntropyLoss()
@@ -52,9 +52,11 @@ for i in range(epoch):
     encoder.opt.step()
  
     losses.append(loss.detach().cpu().numpy())
+    """
     if i % 10 == 0:
         Z, decode = encoder(X)
         print(f"[{i}/{epoch}] loss = {loss_fn(X, decode)}")
+    """
 
 plt.plot(losses)
 plt.savefig(sys.argv[-1])
@@ -63,6 +65,7 @@ X = torch.Tensor(rX).to(device)
 Z, decode = encoder(X)
 print(f"final loss = {loss_fn(X, decode)}")
 Z = Z.detach().cpu().numpy()
+print("save csv", sys.argv[7])
 np.savetxt(sys.argv[7], Z, delimiter = ',')
 
 rX = pd.read_csv(sys.argv[5]).to_numpy()
@@ -73,4 +76,5 @@ X = torch.Tensor(rX).to(device)
 Z, decode = encoder(X)
 print(f"final loss = {loss_fn(X, decode)}")
 Z = Z.detach().cpu().numpy()
+print("save csv", sys.argv[8])
 np.savetxt(sys.argv[8], Z, delimiter = ',')

### 2023-05-01 final/preprocess/Autoencoder/run.sh

@@ -1,1 +1,1 @@
-python main.py 279 50 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv loss.png
+python main.py 279 25 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv loss.png

### 2023-05-01 final/preprocess/Autoencoder/run.sh
update PCA

@@ -1,1 +1,1 @@
-python main.py 279 25 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_label.csv loss.png
+python main.py 279 25 ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/autoencoder_train_data.csv ../../data/Arrhythmia_data_set/autoencoder_test_data.csv loss.png

### 2023-05-17 final/main/main.cpp
remove debug info

@@ -242,14 +242,11 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
         for (auto& x : dataset_.label) x = (x == (label_t)i ? 1LL : -1LL);
 		
         SVM_t<data_t, label_t> SVM{punishment, converge_lim};
-        std::cerr << "SVM fitting..." << std::endl;
     	SVM.fit(dataloader.train_data);
-        std::cerr << "SVM fitting completed" << std::endl;
     	point_t<label_t> result_ =  SVM.predict(dataloader.test_data);
         for (std::size_t j = 0; j < result_.size(); ++j)
             result[j] = (result_[j] == 1LL ? (label_t)i : 0LL);
     }
-    std::cerr << result << std::endl;
     return result;
 }
 

### 2023-05-17 final/paper/main.tex

@@
 \author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
-\date{June 2023}
+\date{May 2023}
 \maketitle
@@
 
+\subsection*{Data preprocess}
+
+\bf{Autoencoder (AE)}: \rm{Autoencoder}
+
+\bf{Principal components analysis (PCA)}: \rm{Principal components analysis}
+
+\subsection*{Classification algorithm}
+
+\bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
+method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
+"birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
+can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
+well for prediction of diabetes disease.
+
+\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
+$0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
+binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
+method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
+feature space.
+
+\bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
+layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
+After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
+training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
+structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
+have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
+
+\subsection*{Clustering algorithm}
+
+\bf{DBSCAN}: \rm{DBSCAN}
+
+\bf{kmeans}: \rm{kmeans}
+
 \section{main section}
@@
     \newcommand{\z}{\phantom{0}}
-    \caption{\textsc{Comparison of Classification Techniques.}}
+    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia data set)}}
       \vspace{-\baselineskip}
     \begin{tabular}{@{}lccccccl@{}}\toprule
-    Technique & Search (s)       & testA                              & testA-normalized             & testB                          & testB-normalized \\ \midrule
-    KNN-Brute-Force  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
-    KNN-ANNOY-DFS    & $0.003$   & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
-    KNN-ANNOY-BFS    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
-    decision tree    & $0.009$   & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
-    random forest    & $0.004$   & $78.6965 \pm \z{1.7510}$           & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
-    SVM-GA           & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
-    Neural Network   & $3.2$     & $\bf{81.7910 \pm \z{2.0294}}$      & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
-    Naive Bayes classifier-GA  & $14.29$ & $78.5353 \pm \z{0.0322}$   & $72.6866 \pm 0.0237$         & $77.4038 \pm \z{0.0626}$       & $71 \pm \z{0.0289}$\\
-    PLA-pocket       & $0.00052$ & $63.682 \pm \z{0}$                 & $3.162 \pm 0$                & $63 \pm \z{0}$                 & $3.162 \pm \z{0}$\\ \midrule
+    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
+    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
+    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
+    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
+    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
+    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
     \end{tabular}
-    \label{table:overall}
+    \label{table:Arrhythmia_result}
+      \vspace{-\baselineskip}
+  \end{table*}
+
+  \begin{table*}[htb]
+    \newcommand{\z}{\phantom{0}}
+    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq data set)}}
+      \vspace{-\baselineskip}
+    \begin{tabular}{@{}lccccccl@{}}\toprule
+    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
+    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
+    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
+    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
+    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
+    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    \end{tabular}
+    \label{table:gene_expression_result}
       \vspace{-\baselineskip}

### 2023-05-18 final/clustering/kmeans/src/kmeans.h
avoid the situation that kmeans can't find a proper center

@@ -18,80 +18,73 @@ public:
 
     point_t<U> fit(const std::vector<point_t<T>>& X);
     point_t<U> fit(const dataset_t<T, U>& dataset);
-private:
-	U assignment(const point_t<T>& x, const std::vector<point_t<T>>& centers);
 };
-
-template<typename T, typename U>
-U kmeans_t<T, U>::assignment(const point_t<T>& x, const std::vector<point_t<T>>& centers)
-{
-    std::pair<double, U> p = std::make_pair(std::numeric_limits<double>::max(), (U)0);
-    for (std::size_t i = 0; i < this->k; ++i)
-        p = std::min(p, std::make_pair(euclidean_dist(x, centers[i]), (U)i));
-    return p.second;
-}
 
 template<typename T, typename U>
 point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 {
     // random initialize center
-    std::vector<point_t<T>> centers;
-    std::vector<point_t<T>> ncenters;
-    point_t<U> labels;
-    std::vector<std::size_t> label_sizes;
-    
-    centers.resize(this->k);
-	for (auto& x : centers) x.resize(X.front().size());
-    ncenters.resize(this->k);
-	for (auto& x : ncenters) x.resize(X.front().size());
-    labels.resize(X.size());
-    label_sizes.resize(this->k);
-    for (std::size_t i = 0; i < this->k; ++i)
-        centers[i] = X[random() % X.size()];
-    
-    bool bk = false;
-    while (true)
-    {
-        // assignment
-        for (auto& ls : label_sizes) ls = 0;
-        for (std::size_t i = 0; i < X.size(); ++i)
-        {
-            labels[i] = assign(X[i], centers);
-            ++label_sizes[labels[i]];
-        }
+	auto try_cnt = 0;
+	while (try_cnt++ <= 1000)
+	{
+		std::vector<point_t<T>> centers;
+		std::vector<point_t<T>> ncenters;
+		point_t<U> labels;
+		std::vector<std::size_t> label_sizes;
+		
+		centers.resize(this->k);
+		for (auto& x : centers) x.resize(X.front().size());
+		ncenters.resize(this->k);
+		for (auto& x : ncenters) x.resize(X.front().size());
+		labels.resize(X.size());
+		label_sizes.resize(this->k);
+		for (std::size_t i = 0; i < this->k; ++i)
[…]

### 2023-05-18 final/main/main.cpp
simplify the test script

@@ -79,29 +79,30 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     std::string_view test_data_path  = args["-test_data_path"];
     std::string_view train_label_path = args["-train_label_path"];
     std::string_view test_label_path  = args["-test_label_path"];
-    std::cerr << "Train data path is " << train_data_path << std::endl;
-    std::cerr << "Train label path is " << train_label_path << std::endl;
-    std::cerr << "Test data path is " << test_data_path << std::endl;
-    std::cerr << "Test label path is " << test_label_path << std::endl;
+	std::cout << "===================================================" << std::endl;
+    std::cout << "Train data: " << train_data_path << std::endl;
+    std::cout << "Train label: " << train_label_path << std::endl;
+    std::cout << "Test data: " << test_data_path << std::endl;
+    std::cout << "Test label: " << test_label_path << std::endl << std::endl;
 
     // data is double, label is int
     Dataloader_t<data_t, label_t> dataloader;
     
-    std::cerr << "Load the train data..." << std::endl;
+    std::cout << "Load the train data..." << std::endl;
     dataloader.load_train(train_data_path, false);
     dataloader.load_train_label(train_label_path);
 
-    std::cerr << "Load the test data..." << std::endl;
+    std::cout << "Load the test data..." << std::endl;
     dataloader.load_test(test_data_path, false);
     dataloader.load_test_label(test_label_path);
     std::cerr << "Complete loading" << std::endl << std::endl;
 	if (args["normalize"] == "true" or args["normalize"] == "1")
 	{
-		//std::cerr << "Normalize the dataset..." << std::endl;
+		std::cout << "Normalize the dataset..." << std::endl;
 		dataloader.load_train(Datatransformer_t<data_t, label_t>::normalize(dataloader.train_data));
 		dataloader.load_test(Datatransformer_t<data_t, label_t>::normalize(dataloader.test_data));
 	}
-	std::cerr << "===================================================================" << std::endl;
+	std::cout << "===================================================================" << std::endl;
 	
 	double macc_ = 0, sum_ = 0, sum2_ = 0;
 	std::chrono::steady_clock::time_point st = std::chrono::steady_clock::now();
[…]

### 2023-05-18 final/clustering/kmeans/src/kmeans.h
imporve the performance

@@ -25,19 +25,23 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 {
     // random initialize center
 	auto try_cnt = 0;
+
+	point_t<U> labels;
+	std::vector<point_t<T>> centers;
+	std::vector<point_t<T>> ncenters;
+	std::vector<std::size_t> label_sizes;
+
+	centers.resize(this->k);
+	for (auto& x : centers) x.resize(X.front().size());
+		ncenters.resize(this->k);
+	for (auto& x : ncenters) x.resize(X.front().size());
+	labels.resize(X.size());
+	label_sizes.resize(this->k);
+
 	while (try_cnt++ <= 1000)
 	{
-		std::vector<point_t<T>> centers;
-		std::vector<point_t<T>> ncenters;
-		point_t<U> labels;
-		std::vector<std::size_t> label_sizes;
-		
-		centers.resize(this->k);
-		for (auto& x : centers) x.resize(X.front().size());
-		ncenters.resize(this->k);
-		for (auto& x : ncenters) x.resize(X.front().size());
-		labels.resize(X.size());
-		label_sizes.resize(this->k);
+		std::fill(label_sizes.begin(), label_sizes.end(), 0);
+		for (auto& x : ncenters) x.fill0();
 		for (std::size_t i = 0; i < this->k; ++i)
 			centers[i] = X[random() % X.size()];
 		
@@ -85,6 +89,7 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 
 		return labels;
 	}
+	return labels;
 }
 
 template<typename T, typename U>

### 2023-05-18 final/clustering/kmeans/src/kmeans.h
kmeans bug fix

@@ -23,7 +23,6 @@ public:
 template<typename T, typename U>
 point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 {
-    // random initialize center
 	auto try_cnt = 0;
 
 	point_t<U> labels;
@@ -38,10 +37,13 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 	labels.resize(X.size());
 	label_sizes.resize(this->k);
 
-	while (try_cnt++ <= 1000)
+RETRY:
+	while (try_cnt++ <= 10)
 	{
 		std::fill(label_sizes.begin(), label_sizes.end(), 0);
 		for (auto& x : ncenters) x.fill0();
+		
+		// random initialize center
 		for (std::size_t i = 0; i < this->k; ++i)
 			centers[i] = X[random() % X.size()];
 		
@@ -68,7 +70,7 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 				ncenters[labels[i]] += X[i];
 			for (std::size_t i = 0; i < this->k; ++i)
 			{
-				if (label_sizes[i] == 0) { std::cerr << "label(" << i << ") has zero member. exit..." << std::endl; exit(1); }
+				if (label_sizes[i] == 0) goto RETRY;
 				ncenters[i] /= (double)label_sizes[i];
 			}
 			std::swap(centers, ncenters);

### 2023-05-18 final/include/utility.h
bug fix

@@ -7,7 +7,7 @@
 template<typename T, typename U>
 std::size_t assign(const U& x, const std::vector<T>& centers)
 {
-    std::pair<double, std::size_t> res{std::numeric_limits<double>::lowest(), 0};
+    std::pair<double, std::size_t> res{std::numeric_limits<double>::max(), 0};
     for (std::size_t i = 0; i < centers.size(); ++i)
         res = std::min(res, std::pair{euclidean_dist(centers[i], x), i});
     return res.second;

### 2023-05-18 final/main/main.cpp
remove dummy file

@@ -141,7 +141,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
         for (std::size_t i = 1; i <= KNOWN_CNT; ++i)
             centers[i] /= kindscnt[i];
 
-        std::cerr << classifying_result << std::endl;
+        //std::cerr << classifying_result << std::endl;
         std::cerr << "classify unknown cnt = " << kindscnt[0] << std::endl;
         std::cerr << "truely unknown cnt = " << unknowncnt << std::endl;
         std::cerr << "classify acc = " << (double)classify_correct / (dataloader.test_data.size() - unknowncnt) << std::endl;
@@ -151,7 +151,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
         
 		std::cerr << "clustering..." << std::endl;
         auto clustering_result = Fn[args["-clustering"]](args, unknown_dataloader, UNKNOWN_CNT);
-        std::cerr << clustering_result << std::endl;
+        //std::cerr << clustering_result << std::endl;
 		
         for (std::size_t i = 0; i < unknown_dataloader.test_data.size(); ++i)
         {

### 2023-05-18 final/clustering/kmeans/src/kmeans.h
centers will be the same data point any more

@@ -3,6 +3,7 @@
 #include <vector>
 #include <limits>
 #include <cstdlib>
+#include <random>
 #include "Data.h"
 #include "utility.h"
 
@@ -23,6 +24,9 @@ public:
 template<typename T, typename U>
 point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 {
+    std::random_device rd;
+    std::default_random_engine gen(rd());
+
 	auto try_cnt = 0;
 
 	point_t<U> labels;
@@ -37,15 +41,21 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 	labels.resize(X.size());
 	label_sizes.resize(this->k);
 
+    std::vector<std::size_t> choosep;
+    for (std::size_t i = 0; i < X.size(); ++i)
+        choosep.emplace_back(i);
+
 RETRY:
 	while (try_cnt++ <= 10)
 	{
+        std::shuffle(choosep.begin(), choosep.end(), gen);
+
 		std::fill(label_sizes.begin(), label_sizes.end(), 0);
 		for (auto& x : ncenters) x.fill0();
-		
+
 		// random initialize center
 		for (std::size_t i = 0; i < this->k; ++i)
-			centers[i] = X[random() % X.size()];
+            centers[i] = X[choosep[i]];
 		
 		bool bk = false;
 		while (true)

### 2023-05-18 final/include/utility.h
add sign function

@@ -13,4 +13,7 @@ std::size_t assign(const U& x, const std::vector<T>& centers)
     return res.second;
 }
 
+template<typename T>
+double sign(T x) { return (x > 0 ? 1 : -1); }
+
 #endif

### 2023-05-18 final/classifying/SVM/src/SVM.h
update svm kernel ver.

@@ -2,7 +2,10 @@
 #define __SVM_H__
 #include <vector>
 #include <cstdlib>
+#include <memory>
+#include <vector>
 #include "Data.h"
+#include "svm_kernel.h"
 
 // U must be double or int
 // note that SVM::predict returns +1 or -1
@@ -12,25 +15,31 @@ class SVM_t
 public:
     double C;
     double P;
-    hyperplane_t<T> H;
-    SVM_t() = default;
-    SVM_t(double c, double p): C(c), P(p) {}
+    std::shared_ptr<svm_kernel_t<double>> kernel;
+    point_t<double> alpha;
+    std::vector<point_t<T>> X;
+    point_t<U> Y;
+    double b;
+
+    SVM_t() { kernel = std::make_shared<linear_kernel<T>>(); };
+    SVM_t(double c, double p): C(c), P(p) { kernel = std::make_shared<linear_kernel<T>>(); }
 
     void fit(const std::vector<point_t<T>>& X, const point_t<U>& Y);
     void fit(const dataset_t<T, U>& dataset);
     U predict(const point_t<T>& X);
 	std::vector<U> predict(const dataset_t<T, U>& X);
 private:
-    point_t<T> SMO(const std::vector<point_t<T>>& X, const point_t<U>& Y);
-    void set_hp(const point_t<T>& alpha, const std::vector<point_t<T>>& X, const point_t<U>& Y);
+    void SMO();
+    void set_shift();
 };
 
 template<typename T, typename U>
 void SVM_t<T, U>::fit(const std::vector<point_t<T>>& X, const point_t<U>& Y)
 {
-	this->H.n.resize(X.front().size());
-    point_t<T> alpha = this->SMO(X, Y);
-    this->set_hp(alpha, X, Y);
+    this->X = X, this->Y = Y;
+    if (X.empty() or Y.empty()) return;
+    this->SMO();
+    this->set_shift();
 }
 template<typename T, typename U>
 void SVM_t<T, U>::fit(const dataset_t<T, U>& X)
@@ -41,48 +50,60 @@ void SVM_t<T, U>::fit(const dataset_t<T, U>& X)
 template<typename T, typename U> 
 U SVM_t<T, U>::predict(const point_t<T>& x)
 {
-    return (H.n * x + H.b > 0 ? 1 : -1);
+    double res = 0;
+    
+    for (std::size_t i = 0; i < this->alpha.size(); ++i)
[…]

### 2023-05-18 final/include/Data.h
update point_t::empty

@@ -71,6 +71,7 @@ public:
 
 	// size
     std::size_t size() const noexcept { return this->x.size(); }
+    bool empty() const noexcept { return this->x.empty(); }
     void resize(std::size_t n) { this->x.resize(n); }
 
     // clear

### 2023-05-18 final/clustering/kmeans/src/kmeans.h
when dataset.size() < k, return them as noisy

@@ -30,17 +30,17 @@ point_t<U> kmeans_t<T, U>::fit(const std::vector<point_t<T>>& X)
 	auto try_cnt = 0;
 
 	point_t<U> labels;
+    if (X.size() < this->k) { labels.resize(X.size()); return labels; }
 	std::vector<point_t<T>> centers;
 	std::vector<point_t<T>> ncenters;
 	std::vector<std::size_t> label_sizes;
 
 	centers.resize(this->k);
 	for (auto& x : centers) x.resize(X.front().size());
-		ncenters.resize(this->k);
+	ncenters.resize(this->k);
 	for (auto& x : ncenters) x.resize(X.front().size());
 	labels.resize(X.size());
 	label_sizes.resize(this->k);
-
     std::vector<std::size_t> choosep;
     for (std::size_t i = 0; i < X.size(); ++i)
         choosep.emplace_back(i);
@@ -55,7 +55,7 @@ RETRY:
 
 		// random initialize center
 		for (std::size_t i = 0; i < this->k; ++i)
-            centers[i] = X[choosep[i]];
+            centers[i] = X[choosep[i % choosep.size()]];
 		
 		bool bk = false;
 		while (true)

### 2023-05-18 final/main/main.cpp
use kernel method

@@ -7,6 +7,7 @@
 #include "Brute.h"
 #include "Annoy.h"
 #include "SVM.h"
+#include "svm_kernel.h"
 #include "kmeans.h"
 #include "DBSCAN.h"
 #include "Dataloader.h"
@@ -177,7 +178,8 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 			double acc = (double)sum/dataloader.test_data.size()*100;
 			final_acc = std::max(final_acc, acc);
 		} while (next_permutation(mapping.begin(), mapping.end()));
-
+        
+        std::cout << "acc: " << final_acc << std::endl << std::endl;
 		macc_ += final_acc;
 		sum_ += final_acc;
 		sum2_ += final_acc*final_acc;
@@ -245,6 +247,7 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
         for (auto& x : dataset_.label) x = (x == (label_t)i ? 1LL : -1LL);
 		
         SVM_t<data_t, label_t> SVM{punishment, converge_lim};
+        SVM.kernel = std::make_shared<sigmoid_kernel<data_t>>(0.000001, 1);
     	SVM.fit(dataloader.train_data);
     	point_t<label_t> result_ =  SVM.predict(dataloader.test_data);
         for (std::size_t j = 0; j < result_.size(); ++j)
@@ -258,6 +261,5 @@ point_t<label_t> kmeans_fit(auto& args, const auto& dataloader, std::size_t k)
 	double converge_lim = std::stod(args["-kmeans_converge_lim"]);
 
     kmeans_t<data_t, label_t> kmeans{k, converge_lim};
-	std::cerr << "kmeans fitting..." << std::endl;
 	return kmeans.fit(dataloader.test_data);
 }

### 2023-05-25 final/paper/main.tex

@@
 
-\title{TBD}
+\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures}
 
@@
 \section*{Abstract}
+Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
+In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
+learning techniques, including data preprocessing, 
+e.g., Principal components analysis (PCA), Autoencoder (AE), classification, e.g., k-nearest neighbors (KNN), 
+support vector machine (SVM), neural network (NN), and clustering for dealing with unknown types, 
+e.g., k-means, density-based spatial clustering of applications with noise (DBSCAN). 
+The experiment results show that with PCA reducing the dimension of the dataset to 32, using KNN for classifying
+the known types, and finally use DBSCAN to cluster the unknown types, the accuracy of predicting can 
+reach about 94\%, which beats the other methods out.
+
+breast invasive carcinoma (BRCA)
+colon adenocarcinoma (COAD)
+kidney renal clear cell carcinoma (KIRC)
+lung adenocarcinoma (LUAD)
+prostate adenocarcinoma (PRAD)
 
@@
 \label{sec:Introduction}
+Over the years, machine learning methods for early predict various disease are widely used in medical field. 
+\cite{kourou2015machine} \cite{cruz2006applications} From diabetes \cite{kavakiotis2017machine}, 
+heart disease \cite{learning2017heart}, to lung adenocarcinoma \cite{huang2020machine} etc., machine learning 
+methods is universally studied attributed to the promising perspective. With a well-built database of disease 
+and a well-choose combination of machine learning mathods, within seconds, a machine may determine the type of disease that 
+this person may have by collecting the data from the person, and thereby achieve the goal of personalized medicine. 
+As a result, machine learning methods have become a popular tool for medical researchers.
+
+In real application, besides from the konwn cancers in the train data, there're numerous unkown types of cancers. 
+When a new type of cancer appears, how shall the machine results? In ideal situation, this new type of cancer should be 
+reported as an unkonwn type, which can be done by the combination of classification and clustering. 
+However, how to choose the proper machine learning methods is a hot potato, since the different combinations 
+of machine learning methods have different performance.
+
+In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
+in the train data, and 2 new types in test data. To find out which techniques is more suitable to predict 
+cancer by RNA sequence, this work examines the the accuracy of the combinations of some major machine 
+learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.
 
@@
 
-\bf{Autoencoder (AE)}: \rm{Autoencoder}
+\bf{Autoencoder (AE)}: \rm{An} AE is a type of neural network used for unsupervised 
+learning and dimensionality reduction. It is designed to learn efficient representations or encodings of 
+input data by training the network to reconstruct its own inputs. The AE consists of an encoder 
+and a decoder. The encoder compresses the input data into a lower-dimensional representation, often called 
+the latent space or code. The decoder then aims to reconstruct the original input data from this compressed 
+representation. By learning a compact representation of the input data, AEs can capture important features 
+and discard noise or irrelevant information. This makes them effective in tasks such as image or 
+text classification, where reducing the dimensionality of the data can improve performance.
 
-\bf{Principal components analysis (PCA)}: \rm{Principal components analysis}
+\bf{Principal components analysis (PCA)}: \rm{PCA} is a statistical technique used for dimensionality 
+reduction and data exploration. It aims to transform a dataset with a large number of variables into 
+a lower-dimensional space while preserving the most important information. PCA accomplishes this by 
+identifying the principal components, which are linear combinations of the original variables. 
+Applications of PCA span various fields, including image and signal processing, finance, genetics, 
+and social sciences. It is particularly useful in scenarios where the dataset is high-dimensional 
+and the interpretation and visualization of the data are challenging.
 
@@
 
-\bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
+\bf{neural network (NN)}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
 layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
@@
 training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
-structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
+structure for hidden layer, increasing the accuracy. According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
 have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
@@
 
-\bf{DBSCAN}: \rm{DBSCAN}
+\bf{k-means}: \rm{k-means} is a popular and easily implemented clustering method in machine learning and data analysis. With $n$
+data points in a dataset, k-means algorithm partition them into $k$ distinct clusters. The algorithm works iteratively and 
+converges to a solution by minimizing the sum of squared distance between the data points and the center of their cluster. 
+K-means is a useful algorithm for clustering data, which is widely applied on many researches, e.g. \cite{oyelade2010application}, 
+\cite{NIDHEESH2017213}, \cite{kadhm2018accurate}.
 
-\bf{kmeans}: \rm{kmeans}
+\bf{Density-based spatial clustering of applications with noise (DBSCAN)}: \rm{DBSCAN} is a data clustering algorithm proposed by
+Ester et al. \cite{10.5555/3001460.3001507} DBSCAN is particularly effective in discovering clusters of arbitrary shapes and 
+handling noise in the data. Unlike k-means need user specify how many clusters, DBSCAN determine the clusters and noise 
+automatically by the density of data points. This characteristic makes it particularly useful when addressing the datasets 
+where the number of cluster is unkonwn. DBSCAN is the major clustering algorithm in machine learning field, since the ability to 
+discover the number of clusters automatically. And the variants of DBSCAN \cite{6814687} is also developed widely.
 
@@
       \vspace{-\baselineskip}
-    \begin{tabular}{@{}lccccccl@{}}\toprule
-    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
-    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
-    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
-    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
-    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
-    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
-    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    \begin{tabular}{@{}lccccccccl@{}}\toprule
+    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-32)                & acc (PCA-32-normalized)    & acc (AE-32)            & acc (AE-32-normalized) \\ \midrule
+    KNN-Brute-Force + DBSCAN  & $0.014$    & $44.3038 \pm \z{0}$               & $46.2025 \pm \z{0}$          & $38.6076 \pm \z{0}$         & $42.4051\pm\z{0}$          & $34.8101 \pm \z{0}$    & $44.3038 \pm \z{0}$\\
+    SVM (linear) + DBSCAN     & $1.048$    & $25.9494 \pm \z{0}$               & $35.4430 \pm \z{0}$          & $32.2785 \pm \z{0}$         & $29.7468 \pm \z{0}$        & $31.6456 \pm \z{0}$    & $27.8481 \pm \z{0}$\\
+    SVM (polynomial) + DBSCAN & $0.765$    & $25.9494 \pm \z{0}$               & $25.3165 \pm \z{0}$          & $1.2658 \pm \z{0}$          & $33.5443 \pm \z{0}$        & $30.3797 \pm \z{0}$    & $30.2785 \pm \z{0}$\\
+    SVM (RBF) + DBSCAN        & $5.298$    & $25.9494 \pm \z{0}$               & $22.7848 \pm \z{0}$          & $0.6329 \pm \z{0}$          & $30.3797 \pm \z{0}$        & $22.1519 \pm \z{0}$    & $34.1772 \pm \z{0}$\\
+    SVM (sigmoid) + DBSCAN    & $2.298$    & $28.4810 \pm \z{0}$               & $20.2532 \pm \z{0}$          & $30.3797 \pm \z{0}$         & $36.0759 \pm \z{0}$        & $22.1519 \pm \z{0}$    & $24.6835 \pm \z{0}$\\
+    KNN-Brute-Force + kmeans  & $0.014$    & $44.3038 \pm \z{0}$               & $41.7722 \pm \z{0}$          & $43.0380 \pm \z{0}$         & $43.0380 \pm \z{0}$        & $36.0759 \pm \z{0}$    & $41.7722 \pm \z{0}$\\
+    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (polynomial) + kmeans & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (sigmoid) + kmeans    & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    \bottomrule
     \end{tabular}
@@
       \vspace{-\baselineskip}
-    \begin{tabular}{@{}lccccccl@{}}\toprule
-    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
-    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
-    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
-    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
-    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
-    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
-    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
+    \begin{tabular}{@{}lccccccccl@{}}\toprule
+    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                & acc (PCA-30-normalized)    & acc (AE-30)            & acc (AE-30-normalized)\\ \midrule
+    KNN-Brute-Force + DBSCAN  & $4.317$    & $59.0361 \pm \z{0}$               & $66.5663 \pm \z{0}$          & $94.5783 \pm \z{0}$         & $78.3133 \pm \z{0}$        & $64.4578 \pm \z{0}$    & $59.3373 \pm \z{0}$\\
+    SVM (linear) + DBSCAN     & $131.809$  & $61.7470 \pm \z{0}$               & $9.9398 \pm \z{0}$           & $9.9398 \pm \z{0}$          & $10.5422 \pm \z{0}$         & $63.2530 \pm \z{0}$    & $13.5542 \pm \z{0}$\\
+    SVM (polynomial) + DBSCAN & $31.221$   & $61.7470 \pm \z{0}$               & $1.2048 \pm \z{0}$           & $64.4578 \pm \z{0}$         & $61.1446 \pm \z{0}$        & $63.2530 \pm \z{0}$    & $50.3012 \pm \z{0}$\\
+    SVM (RBF) + DBSCAN        & $3.988$    & $X$                               & $X$                          & $9.9398 \pm \z{0}$          & $63.2530 \pm \z{0}$        & $40.3614 \pm \z{0}$    & $49.6988 \pm \z{0}$\\
+    SVM (sigmoid) + DBSCAN    & $0.446$    & $X$                               & $X$                          & $71.6867 \pm \z{0}$         & $65.9639 \pm \z{0}$        & $44.2771 \pm \z{0}$    & $38.2530 \pm \z{0}$\\
+    KNN-Brute-Force + kmeans  & $4.859$    & $74.0964 \pm \z{0}$               & $53.6145 \pm \z{0}$          & $94.8795 \pm \z{0}$         & $84.9398 \pm \z{0}$        & $42.1687 \pm \z{0}$    & $65.9639 \pm \z{0}$\\
+    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (polynomial) + kmeans & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    SVM (sigmoid) + kmeans    & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+    \bottomrule
     \end{tabular}

### 2023-05-25 final/clustering/kmeans/src/kmeans.h
prevent the situation that WCSS = nan

@@ -91,7 +91,7 @@ RETRY:
 			double WCSS = 0;
 			for (std::size_t j = 0; j < X.size(); ++j)
 				WCSS += euclidean_dist(X[j], centers[labels[j]]);
-			if ((WCSS - WCSS0) / WCSS0 <= this->theta)
+			if (not std::isfinite((WCSS - WCSS0) / WCSS0) or (WCSS - WCSS0) / WCSS0 <= this->theta)
 				bk = true;
 		}
 

### 2023-05-26 final/main/SA/main.cpp
SA hyperparameter search

@@ -1,0 +1,268 @@
+#include <iostream>
+#include <cstdlib>
+#include <cstring>
+#include <memory>
+#include <cmath>
+#include <chrono>
+#include <unordered_map>
+#include <random>
+#include "argparser.h"
+
+std::string exe_with_args(auto& args)
+{
+    std::string s = "../main.elf -repeats 1 -classifying " + args["-classifying"] + " -clustering " + args["-clustering"] + \
+                    " -verbose false " + "-train_data_path " + args["-train_data_path"] + " -train_label_path " + args["-train_label_path"] + \
+                    " -test_data_path " + args["-test_data_path"] + " -test_data_path " + args["-test_data_path"] + \
+                    " -test_label_path " + args["-test_label_path"] + " -normalize " + args["-normalize"] + " -KNOWN_CNT " + args["-KNOWN_CNT"] + \
+                    " -UNKNOWN_CNT " + args["-UNKNOWN_CNT"];
+
+    if (args["-classifying"] == "KNN")
+    {
+        // -KNN_k
+        // -KNN_maxdis
+        // -KNN_problim
+        s += " -KNN_method brute -KNN_k " + args["-KNN_k"] + " -KNN_maxdis " + args["-KNN_maxdis"] + " -KNN_problim " + args["-KNN_problim"];
+    }
+    else if (args["-classifying"] == "SVM")
+    {
+        // -SVM_converge_lim 1e-7
+        // -SVM_punishment 1
+        // -SVM_kernel 
+        // -SVM_kernel_gamma
+        // -SVM_kernel_degree
+        // -SVM_kernel_r
+        s += " -SVM_converge_lim 1e-7 -SVM_punishment 1 -SVM_kernel " + args["-SVM_kernel"] + \
+             " -SVM_kernel_gamma " + args["-SVM_kernel_gamma"] + " -SVM_kernel_degree 2" + \
+             " -SVM_kernel_r " + args["-SVM_kernel_r"];
+    }
+
+    if (args["-clustering"] == "kmeans")
+    {
+        // -kmeans_converge_lim
+        s += " -kmeans_converge_lim 1e-5";
+    }
+    else if (args["-clustering"] == "DBSCAN")
+    {
+        // -DBSCAN_minPts
[…]

### 2023-05-26 final/paper/main.tex
update

@@
       \vspace{-\baselineskip}
+    \resizebox{\textwidth}{!}{
       \begin{tabular}{@{}lccccccccl@{}}\toprule
       Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-32)                & acc (PCA-32-normalized)    & acc (AE-32)            & acc (AE-32-normalized) \\ \midrule
-    KNN-Brute-Force + DBSCAN  & $0.014$    & $44.3038 \pm \z{0}$               & $46.2025 \pm \z{0}$          & $38.6076 \pm \z{0}$         & $42.4051\pm\z{0}$          & $34.8101 \pm \z{0}$    & $44.3038 \pm \z{0}$\\
-    SVM (linear) + DBSCAN     & $1.048$    & $25.9494 \pm \z{0}$               & $35.4430 \pm \z{0}$          & $32.2785 \pm \z{0}$         & $29.7468 \pm \z{0}$        & $31.6456 \pm \z{0}$    & $27.8481 \pm \z{0}$\\
-    SVM (polynomial) + DBSCAN & $0.765$    & $25.9494 \pm \z{0}$               & $25.3165 \pm \z{0}$          & $1.2658 \pm \z{0}$          & $33.5443 \pm \z{0}$        & $30.3797 \pm \z{0}$    & $30.2785 \pm \z{0}$\\
-    SVM (RBF) + DBSCAN        & $5.298$    & $25.9494 \pm \z{0}$               & $22.7848 \pm \z{0}$          & $0.6329 \pm \z{0}$          & $30.3797 \pm \z{0}$        & $22.1519 \pm \z{0}$    & $34.1772 \pm \z{0}$\\
-    SVM (sigmoid) + DBSCAN    & $2.298$    & $28.4810 \pm \z{0}$               & $20.2532 \pm \z{0}$          & $30.3797 \pm \z{0}$         & $36.0759 \pm \z{0}$        & $22.1519 \pm \z{0}$    & $24.6835 \pm \z{0}$\\
-    KNN-Brute-Force + kmeans  & $0.014$    & $44.3038 \pm \z{0}$               & $41.7722 \pm \z{0}$          & $43.0380 \pm \z{0}$         & $43.0380 \pm \z{0}$        & $36.0759 \pm \z{0}$    & $41.7722 \pm \z{0}$\\
-    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (polynomial) + kmeans & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (sigmoid) + kmeans    & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+      KNN-Brute-Force + DBSCAN  & $0.014$    & $44.3038 \pm 0$                   & $46.8354 \pm 0$              & $38.6076 \pm 0$             & $42.4051\pm 0$             & $34.8101 \pm 0$        & $44.3038 \pm 0$\\
+      SVM (linear) + DBSCAN     & $1.048$    & $25.9494 \pm 0$                   & $35.4430 \pm 0$              & $32.2785 \pm 0$             & $29.7468 \pm 0$            & $31.6456 \pm 0$        & $27.8481 \pm 0$\\
+      SVM (polynomial) + DBSCAN & $0.765$    & $25.9494 \pm 0$                   & $25.3165 \pm 0$              & $1.2658 \pm 0$              & $33.5443 \pm 0$            & $30.3797 \pm 0$        & $30.2785 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $5.298$    & $25.9494 \pm 0$                   & $22.7848 \pm 0$              & $0.6329 \pm 0$              & $30.3797 \pm 0$            & $22.1519 \pm 0$        & $34.1772 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $2.298$    & $28.4810 \pm 0$                   & $20.2532 \pm 0$              & $30.3797 \pm 0$             & $36.0759 \pm 0$            & $22.1519 \pm 0$        & $24.6835 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $0.014$    & $53.1646 \pm 0$                   & $50.6329 \pm 0$              & $43.0380 \pm 0$             & $43.0380 \pm 0$            & $36.0759 \pm 0$        & $41.7722 \pm 0$\\
+      SVM (linear) + kmeans     & $X$        & $25.3165 \pm 0$                   & $37.9747 \pm 0$              & $25.3165 \pm 0$             & $27.8481 \pm 0$            & $24.0506 \pm 0$        & $20.2532 \pm 0$\\
+      SVM (polynomial) + kmeans & $X$        & $25.3165 \pm 0$                   & $26.5823 \pm 0$              & $14.5570 \pm 0$             & $28.4810 \pm 0$            & $24.0506 \pm 0$        & $25.3165 \pm 0$\\
+      SVM (RBF) + kmeans        & $X$        & $8.8608 \pm 0$                    & $29.7468 \pm 0$              & $0.6329 \pm 0$              & $1.2658 \pm 0$             & $22.7848 \pm 0$        & $27.2152 \pm 0$\\
+      SVM (sigmoid) + kmeans    & $X$        & $22.6582 \pm 0$                   & $17.7848 \pm 0$              & $25.3165 \pm 0$             & $12.0253 \pm 0$            & $17.7215 \pm 0$        & $28.4810 \pm 0$\\
       \bottomrule
       \end{tabular}
+    }
     \label{table:Arrhythmia_result}
@@
       \vspace{-\baselineskip}
+    \resizebox{\textwidth}{!}{
       \begin{tabular}{@{}lccccccccl@{}}\toprule
       Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                & acc (PCA-30-normalized)    & acc (AE-30)            & acc (AE-30-normalized)\\ \midrule
-    KNN-Brute-Force + DBSCAN  & $4.317$    & $59.0361 \pm \z{0}$               & $66.5663 \pm \z{0}$          & $94.5783 \pm \z{0}$         & $78.3133 \pm \z{0}$        & $64.4578 \pm \z{0}$    & $59.3373 \pm \z{0}$\\
-    SVM (linear) + DBSCAN     & $131.809$  & $61.7470 \pm \z{0}$               & $9.9398 \pm \z{0}$           & $9.9398 \pm \z{0}$          & $10.5422 \pm \z{0}$         & $63.2530 \pm \z{0}$    & $13.5542 \pm \z{0}$\\
-    SVM (polynomial) + DBSCAN & $31.221$   & $61.7470 \pm \z{0}$               & $1.2048 \pm \z{0}$           & $64.4578 \pm \z{0}$         & $61.1446 \pm \z{0}$        & $63.2530 \pm \z{0}$    & $50.3012 \pm \z{0}$\\
-    SVM (RBF) + DBSCAN        & $3.988$    & $X$                               & $X$                          & $9.9398 \pm \z{0}$          & $63.2530 \pm \z{0}$        & $40.3614 \pm \z{0}$    & $49.6988 \pm \z{0}$\\
-    SVM (sigmoid) + DBSCAN    & $0.446$    & $X$                               & $X$                          & $71.6867 \pm \z{0}$         & $65.9639 \pm \z{0}$        & $44.2771 \pm \z{0}$    & $38.2530 \pm \z{0}$\\
-    KNN-Brute-Force + kmeans  & $4.859$    & $74.0964 \pm \z{0}$               & $53.6145 \pm \z{0}$          & $94.8795 \pm \z{0}$         & $84.9398 \pm \z{0}$        & $42.1687 \pm \z{0}$    & $65.9639 \pm \z{0}$\\
-    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (polynomial) + kmeans & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (linear) + kmeans     & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
-    SVM (sigmoid) + kmeans    & $X$        & $X \pm \z{0}$                     & $X \pm \z{0}$           & $X \pm \z{0}$                  & $X \pm \z{0}$         & $0 \pm \z{0}$                    & $0 \pm \z{0}$\\
+      KNN-Brute-Force + DBSCAN  & $4.317$    & $59.0361 \pm 0$                   & $66.5663 \pm 0$              & $94.5783 \pm 0$             & $78.3133 \pm 0$            & $64.4578 \pm 0$        & $59.3373 \pm 0$\\
+      SVM (linear) + DBSCAN     & $131.809$  & $61.7470 \pm 0$                   & $9.9398 \pm 0$               & $9.9398 \pm 0$              & $10.5422 \pm 0$            & $63.2530 \pm 0$        & $13.5542 \pm 0$\\
+      SVM (polynomial) + DBSCAN & $31.221$   & $61.7470 \pm 0$                   & $1.2048 \pm 0$               & $64.4578 \pm 0$             & $61.1446 \pm 0$            & $63.2530 \pm 0$        & $50.3012 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $3.988$    & $X$                               & $X$                          & $9.9398 \pm 0$              & $63.2530 \pm 0$            & $40.3614 \pm 0$        & $49.6988 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $0.446$    & $X$                               & $X$                          & $71.6867 \pm 0$             & $65.9639 \pm 0$            & $44.2771 \pm 0$        & $38.2530 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $4.859$    & $74.0964 \pm 0$                   & $53.6145 \pm 0$              & $94.8795 \pm 0$             & $84.9398 \pm 0$            & $42.1687 \pm 0$        & $65.9639 \pm 0$\\
+      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
+      SVM (polynomial) + kmeans & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
+      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
+      SVM (sigmoid) + kmeans    & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
       \bottomrule
       \end{tabular}
+    }
     \label{table:gene_expression_result}

### 2023-05-26 final/main/main.cpp
fix typo

@@ -211,7 +211,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 	std::chrono::steady_clock::time_point ed = std::chrono::steady_clock::now();
 	std::cout << "acc = " << macc_ << "%(" << stand_ << ")" << std::endl;
 	auto duration = std::chrono::duration_cast<std::chrono::microseconds>(ed - st).count() / 1000000.0 / repeats;
-	std::cout << "time: " << duration << std::endl << std::endl;;
+	std::cout << "time: " << duration << std::endl << std::endl;
 
     return 0;
 }

### 2023-05-27 final/paper/main.tex
update parper

@@
 \usepackage{dblfloatfix}
+\usepackage{hyperref}
 % ==========================
 %\usepackage[a4paper, margin = 2.5cm]{geometry}
+
+\algrenewcommand\alglinenumber[1]{\footnotesize #1}
+\algnewcommand\algorithmicassume{\textbf{Assumption:}}
+\algnewcommand\Assume{\item[\algorithmicassume]}
 
@@
 
-\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures}
+\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types}
 
@@
 In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
-learning techniques, including data preprocessing, 
-e.g., Principal components analysis (PCA), Autoencoder (AE), classification, e.g., k-nearest neighbors (KNN), 
-support vector machine (SVM), neural network (NN), and clustering for dealing with unknown types, 
-e.g., k-means, density-based spatial clustering of applications with noise (DBSCAN). 
-The experiment results show that with PCA reducing the dimension of the dataset to 32, using KNN for classifying
-the known types, and finally use DBSCAN to cluster the unknown types, the accuracy of predicting can 
-reach about 94\%, which beats the other methods out.
+learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
+(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
+and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
+applications with noise (DBSCAN).
 
-breast invasive carcinoma (BRCA)
-colon adenocarcinoma (COAD)
-kidney renal clear cell carcinoma (KIRC)
-lung adenocarcinoma (LUAD)
-prostate adenocarcinoma (PRAD)
+The result of gene dataset shows that, with PCA reducing the dimension of the dataset to 32, use KNN for 
+classifying the known types, and finally apply DBSCAN on the remaining data, the accuracy of predicting 
+can reach about 94\%, which beats the other methods out. In the other way, the result of arrhythmia 
+dataset shows that, with raw data, use KNN and k-means, the highest accuracy of predicting can reach about 
+53\%.
+
+The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{here}.
 
@@
 methods is universally studied attributed to the promising perspective. With a well-built database of disease 
-and a well-choose combination of machine learning mathods, within seconds, a machine may determine the type of disease that 
-this person may have by collecting the data from the person, and thereby achieve the goal of personalized medicine. 
-As a result, machine learning methods have become a popular tool for medical researchers.
+and a well-choose combination of machine learning mathods, within seconds, a machine may determine the type of 
+disease that this person may have by collecting the data from the person, and thereby achieve the goal of 
+personalized medicine. As a result, machine learning methods have become a popular tool for medical researchers.
 
-In real application, besides from the konwn cancers in the train data, there're numerous unkown types of cancers. 
-When a new type of cancer appears, how shall the machine results? In ideal situation, this new type of cancer should be 
+In real application, besides from the konwn diseases in the train data, there're numerous unkown types of diseases. 
+When a new type of disease appears, how shall the machine results? In ideal situation, this new type of disease should be 
 reported as an unkonwn type, which can be done by the combination of classification and clustering. 
@@
 In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
-in the train data, and 2 new types in test data. To find out which techniques is more suitable to predict 
-cancer by RNA sequence, this work examines the the accuracy of the combinations of some major machine 
+in the train data, i.e., kidney renal clear cell carcinoma (KIRC), breast invasive carcinoma (BRCA), 
+lung adenocarcinoma (LUAD), and 2 new types in test data, i.e., colon adenocarcinoma (COAD), 
+prostate adenocarcinoma (PRAD). And also, the dataset of arrhythmia is included, which caintains
+8 types in train data, and 5 new types in test data. To find out which techniques is more suitable to fit 
+these two datasets, this work examines the the accuracy of the combinations of some major machine 
 learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.
@@
 representation. By learning a compact representation of the input data, AEs can capture important features 
-and discard noise or irrelevant information. This makes them effective in tasks such as image or 
-text classification, where reducing the dimensionality of the data can improve performance.
+and discard noise or irrelevant information \cite{lu2013speech}. This makes them effective in tasks such as 
+image \cite{zhang2018better} \cite{lore2017llnet} \cite{cheng2018deep} or text classification \cite{xu2017variational} 
+\cite{xu2019semisupervised}, where reducing the dimensionality of the data can improve performance.
 
@@
 identifying the principal components, which are linear combinations of the original variables. 
-Applications of PCA span various fields, including image and signal processing, finance, genetics, 
-and social sciences. It is particularly useful in scenarios where the dataset is high-dimensional 
-and the interpretation and visualization of the data are challenging.
+Applications of PCA span various fields, including image \cite{ma2019dimension} \cite{YANG20021997} 
+and signal processing \cite{6497960} \cite{castells2007principal}, genetics \cite{reich2008principal} 
+\cite{novembre2008interpreting}. It is particularly useful in scenarios where the dataset is 
+high-dimensional and the interpretation and visualization of the data are challenging.
 
@@
 
-\bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
-method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
-"birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
-can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
-well for prediction of diabetes disease.
+\bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a 
+supervised learning method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea 
+of KNN is based on the idiom, "birds of a feather flock together". By picking the $k$-nearest neighbors 
+of a data point, the unkonwn class label can be determined. Lots of works \cite{6528591} \cite{8276012} 
+\cite{vijayan2014study} show the fact that KNN performs  well for prediction of diabetes disease.
 
-\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
-$0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
-binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
-method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
+\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a 
+binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to 
+the binay labels by making it a non-probabilistic binary linear classifier. In addition, accroding to 
+\cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to 
+effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
 feature space.
 
-\bf{neural network (NN)}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
-layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
-After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
-training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
-structure for hidden layer, increasing the accuracy. According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
-have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.
+\bf{neural network (NN)}: \rm{Neural} network have been used in many fields to deal with intricate datas. 
+With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed 
+while passing through neurons, layer by layer. After the processing, the outcome can be used to predict. 
+Using back propogation, the accuracy of predictions increase in each training. In order to construct the 
+hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for 
+hidden layer, increasing the accuracy. According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural 
+network have been constructed and trained already, with high efficiency and accuracy in prediction of 
+diabetes.
 
@@
 
-\bf{k-means}: \rm{k-means} is a popular and easily implemented clustering method in machine learning and data analysis. With $n$
-data points in a dataset, k-means algorithm partition them into $k$ distinct clusters. The algorithm works iteratively and 
-converges to a solution by minimizing the sum of squared distance between the data points and the center of their cluster. 
-K-means is a useful algorithm for clustering data, which is widely applied on many researches, e.g. \cite{oyelade2010application}, 
+\bf{k-means}: \rm{K-means} is a popular and easily implemented clustering method in machine learning and 
+data analysis. With $n$ data points in a dataset, k-means algorithm partition them into $k$ distinct 
+clusters. The algorithm works iteratively and converges to a solution by minimizing the sum of squared 
+distance between the data points and the center of their cluster. K-means is a useful algorithm for 
+clustering data, which is widely applied on many researches, e.g. \cite{oyelade2010application}, 
 \cite{NIDHEESH2017213}, \cite{kadhm2018accurate}.
 
-\bf{Density-based spatial clustering of applications with noise (DBSCAN)}: \rm{DBSCAN} is a data clustering algorithm proposed by
-Ester et al. \cite{10.5555/3001460.3001507} DBSCAN is particularly effective in discovering clusters of arbitrary shapes and 
-handling noise in the data. Unlike k-means need user specify how many clusters, DBSCAN determine the clusters and noise 
-automatically by the density of data points. This characteristic makes it particularly useful when addressing the datasets 
-where the number of cluster is unkonwn. DBSCAN is the major clustering algorithm in machine learning field, since the ability to 
+\bf{Density-based spatial clustering of applications with noise (DBSCAN)}: \rm{DBSCAN} is a data clustering 
+algorithm proposed by Ester et al. \cite{10.5555/3001460.3001507} DBSCAN is particularly effective in 
+discovering clusters of arbitrary shapes and handling noise in the data. Unlike k-means need user specify 
+how many clusters, DBSCAN determine the clusters and noise automatically by the density of data points. 
+This characteristic makes it particularly useful when addressing the datasets where the number of cluster 
+is unkonwn. DBSCAN is the major clustering algorithm in machine learning field, since the ability to 
 discover the number of clusters automatically. And the variants of DBSCAN \cite{6814687} is also developed widely.
 
-\section{main section}
+\section{Main Process}
+  The main algorithm to process the dataset is shown as below:
+  \begin{algorithm}
+    \caption{The Main Algorithm}\label{alg:main}
+    \begin{algorithmic}[1]
+      \Require $\text{Dataset}$
+      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
+      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
+      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
+      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
+      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
+    \end{algorithmic}
+  \end{algorithm}
+
+  First, preprocess the dataset, e.g. normalize, apply PCA, apply AE. Second, classify the data after preprocessing. 
+  With this step the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
+  be varied depending on the classification algorithm. For KNN, the criterion is distance and probability. More specifically, 
+  assume a data point $x$, and the k-nearest data points are $p_1,...,p_k$. Only those points whose distance between 
+  $x$ smaller than $L$ will be marked valid. Denote the valid data points as $p'_1,...p'_n$, and the corresponding 
+  labels are $l_1,...,l_n$. If this data point satisifies Eq~\ref{eqn:KNN_prob}, mark it as unkown type.
+  \begin{equation}
+    \label{eqn:KNN_prob}
+    \frac{\arg\max_{t\in\text{types}\{N(t)\}}}{n}<P
+  \end{equation}
+  where $P$ is a manunally set probability and $N(t)$ is the number of type $t$ in those $n$ valid data points.
+
+  As for SVM, the criterion born in the designed. Since SVM is meant to be a binary classifier, the SVM classification 
+  algorithm must be redesigned. As shown in Algo~\ref{alg:SVMs}. 
+  \begin{algorithm}[h]
+    \caption{The SVM Multi-classification Algorithm}\label{alg:SVMs}
+    \begin{algorithmic}[1]
+      \Require $\text{Train Data, Labels, Test Data}$
+      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
+      \For{$t \text{ in Known Types}$}
+        \For{$i \text{ in }[1,N]$}
+          \If{$\text{Labels}[i]\neq t$}
+            \State $\text{Labels}'[i] = +1$
+          \Else
+            \State $\text{Labels}'[i] = -1$
+          \EndIf
+        \EndFor
+        \State $\text{SVM}[t].\text{fit}(\text{Train Data}, \text{Labels}')$
+      \EndFor
+      \For{$t \text{ in Known Types}$}
+        \For{$i\text{ in }[1,M]$}
+          \If{$\text{SVM}[t].\text{predict}() = +1$}
+            \State $\text{Test Labels}[i] = t$
+          \Else
+            \State $\text{Test Labels}[i] = \text{UNKNOWN}$
+          \EndIf
+        \EndFor
+      \EndFor
+    \end{algorithmic}
+  \end{algorithm}
+
+  After classifying, the konwn types and unkonwn types are separated. The data marked as unkonwn types will be thrown 
+  into clustering algorithm, e.g., DBSCAN, k-means. Subsequently, the process is completed.
 
 \section{Experiment result}
+  The experiment result of arrhythmia dataset is shown in Table~\ref{table:Arrhythmia_result}. And the result of gene 
+  expression cancer RNA-Seq data set is in Table~\ref{table:gene_expression_result}.
+
+  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
+  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
+  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
+  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
+  \begin{figure}[htb]
+    \centering
+    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
+    \caption{An example that multiple SVMs fail}
+    \label{fig:SVM_fail}
+  \end{figure}
+  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
+  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
+  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
+  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.
+
   \begin{table*}[htb]
     \newcommand{\z}{\phantom{0}}
-    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia data set)}}
+    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
       \vspace{-\baselineskip}
     \resizebox{\textwidth}{!}{
-      \begin{tabular}{@{}lccccccccl@{}}\toprule
-      Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-32)                & acc (PCA-32-normalized)    & acc (AE-32)            & acc (AE-32-normalized) \\ \midrule
-      KNN-Brute-Force + DBSCAN  & $0.014$    & $44.3038 \pm 0$                   & $46.8354 \pm 0$              & $38.6076 \pm 0$             & $42.4051\pm 0$             & $34.8101 \pm 0$        & $44.3038 \pm 0$\\
-      SVM (linear) + DBSCAN     & $1.048$    & $25.9494 \pm 0$                   & $35.4430 \pm 0$              & $32.2785 \pm 0$             & $29.7468 \pm 0$            & $31.6456 \pm 0$        & $27.8481 \pm 0$\\
-      SVM (polynomial) + DBSCAN & $0.765$    & $25.9494 \pm 0$                   & $25.3165 \pm 0$              & $1.2658 \pm 0$              & $33.5443 \pm 0$            & $30.3797 \pm 0$        & $30.2785 \pm 0$\\
-      SVM (RBF) + DBSCAN        & $5.298$    & $25.9494 \pm 0$                   & $22.7848 \pm 0$              & $0.6329 \pm 0$              & $30.3797 \pm 0$            & $22.1519 \pm 0$        & $34.1772 \pm 0$\\
-      SVM (sigmoid) + DBSCAN    & $2.298$    & $28.4810 \pm 0$                   & $20.2532 \pm 0$              & $30.3797 \pm 0$             & $36.0759 \pm 0$            & $22.1519 \pm 0$        & $24.6835 \pm 0$\\
-      KNN-Brute-Force + kmeans  & $0.014$    & $53.1646 \pm 0$                   & $50.6329 \pm 0$              & $43.0380 \pm 0$             & $43.0380 \pm 0$            & $36.0759 \pm 0$        & $41.7722 \pm 0$\\
-      SVM (linear) + kmeans     & $X$        & $25.3165 \pm 0$                   & $37.9747 \pm 0$              & $25.3165 \pm 0$             & $27.8481 \pm 0$            & $24.0506 \pm 0$        & $20.2532 \pm 0$\\
-      SVM (polynomial) + kmeans & $X$        & $25.3165 \pm 0$                   & $26.5823 \pm 0$              & $14.5570 \pm 0$             & $28.4810 \pm 0$            & $24.0506 \pm 0$        & $25.3165 \pm 0$\\
-      SVM (RBF) + kmeans        & $X$        & $8.8608 \pm 0$                    & $29.7468 \pm 0$              & $0.6329 \pm 0$              & $1.2658 \pm 0$             & $22.7848 \pm 0$        & $27.2152 \pm 0$\\
-      SVM (sigmoid) + kmeans    & $X$        & $22.6582 \pm 0$                   & $17.7848 \pm 0$              & $25.3165 \pm 0$             & $12.0253 \pm 0$            & $17.7215 \pm 0$        & $28.4810 \pm 0$\\
+      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
+        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\
+        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
+                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
+      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
+      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
+      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
+      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
+      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
+      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
+      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
+      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
+      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
+      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
       \bottomrule
@@
     \newcommand{\z}{\phantom{0}}
-    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq data set)}}
+    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
       \vspace{-\baselineskip}
     \resizebox{\textwidth}{!}{
-      \begin{tabular}{@{}lccccccccl@{}}\toprule
-      Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                & acc (PCA-30-normalized)    & acc (AE-30)            & acc (AE-30-normalized)\\ \midrule
-      KNN-Brute-Force + DBSCAN  & $4.317$    & $59.0361 \pm 0$                   & $66.5663 \pm 0$              & $94.5783 \pm 0$             & $78.3133 \pm 0$            & $64.4578 \pm 0$        & $59.3373 \pm 0$\\
-      SVM (linear) + DBSCAN     & $131.809$  & $61.7470 \pm 0$                   & $9.9398 \pm 0$               & $9.9398 \pm 0$              & $10.5422 \pm 0$            & $63.2530 \pm 0$        & $13.5542 \pm 0$\\
-      SVM (polynomial) + DBSCAN & $31.221$   & $61.7470 \pm 0$                   & $1.2048 \pm 0$               & $64.4578 \pm 0$             & $61.1446 \pm 0$            & $63.2530 \pm 0$        & $50.3012 \pm 0$\\
-      SVM (RBF) + DBSCAN        & $3.988$    & $X$                               & $X$                          & $9.9398 \pm 0$              & $63.2530 \pm 0$            & $40.3614 \pm 0$        & $49.6988 \pm 0$\\
-      SVM (sigmoid) + DBSCAN    & $0.446$    & $X$                               & $X$                          & $71.6867 \pm 0$             & $65.9639 \pm 0$            & $44.2771 \pm 0$        & $38.2530 \pm 0$\\
-      KNN-Brute-Force + kmeans  & $4.859$    & $74.0964 \pm 0$                   & $53.6145 \pm 0$              & $94.8795 \pm 0$             & $84.9398 \pm 0$            & $42.1687 \pm 0$        & $65.9639 \pm 0$\\
-      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
-      SVM (polynomial) + kmeans & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
-      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
-      SVM (sigmoid) + kmeans    & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
+      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
+        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\
+        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
+                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
+      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
+      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
+      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $X$        & $X$               & $X$        & $X$                   & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $X$        & $X$               & $X$        & $X$                   & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
+      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
+      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
+      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
+      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
       \bottomrule

### 2023-05-27 final/paper/main.tex
update

@@
   First, preprocess the dataset, e.g. normalize, apply PCA, apply AE. Second, classify the data after preprocessing. 
-  With this step the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
+  In the experiment, we use PCA and AE to reduce the dimension down to 32 and 30 in arrhythmia dataset and gene 
+  expression cancer RNA-Seq dataset, respectively. 
+  With this step, the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
   be varied depending on the classification algorithm. For KNN, the criterion is distance and probability. More specifically, 
@@
 
+  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
+  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
+  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
+  \begin{algorithm}[tb]
+    \caption{Neural Network Classification}\label{alg:NN}
+    \begin{algorithmic}[1]
+      \Require $\text{Train Data, Labels, Test Data}$
+      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
+      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
+      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
+      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
+      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
+    \end{algorithmic}
+  \end{algorithm}
+
   After classifying, the konwn types and unkonwn types are separated. The data marked as unkonwn types will be thrown 
@@
   \end{figure}
+
   In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
@@
 
-  \begin{table*}[htb]
+  \begin{table*}[tb]
     \newcommand{\z}{\phantom{0}}

### 2023-05-27 final/paper/main.tex
update paper

@@
 
-\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types}
+\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
 
@@
 feature space. 
+The idea of kernel trick is transform the data into higher dimension. In ideal situation, the dataset 
+which is not linear separable becomes linear separable. Fig~\ref{fig:SVM_kernel_trick} illurates this 
+case.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[scale=0.25]{assets/SVM_kernel_trick.png}
+    \caption{An example of SVM kernel trick}
+    \label{fig:SVM_kernel_trick}
+\end{figure}
 
@@
 \section{Main Process}
-  The main algorithm to process the dataset is shown as below:
+  The pesudo code of the proposed algorithm to process the dataset is shown below and Fig~\ref{fig:Main_Algo} 
+  illurates the process of this algorithm:
   \begin{algorithm}
@@
   \end{algorithm}
+
+  \begin{figure}[htb]
+    \centering
+    \includegraphics[scale=0.20]{assets/Main_Algo.pdf}
+    \caption{A figure about the main algorithm}
+    \label{fig:Main_Algo}
+  \end{figure}
 
@@
 
-  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
+  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the mult- 
   classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
@@
     \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
-    \caption{An example that multiple SVMs fail}
+    \caption{An example that mult-classification SVMs fail}
     \label{fig:SVM_fail}
@@
 \section{Conclusion}
+In this study, we present a framework of algorithm to deal with the dataset containing 
+out-of-knowledge data. And with in this algorithm, multiple major machine learning 
+techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
+KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
+combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
+dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
+SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
+SVMs design, which make some SVMs hard to separate the target types. However, by customize 
+the kernel for each SVMs, the problem may ease. In the same time, the increasing number of 
+parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
+algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
+the accuracy on these datasets.
+
+\section{Contribution}
+\begin{itemize}
+  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
+  \item Hsu Ting-Hao: 
+  \item Sun Shih-Yu: SVM, k-means, paper
+  \item Lu Che-Yuan: 
+  \item Huang Chia-Yen: 
+\end{itemize}
 

### 2023-05-27 final/paper/main.tex
mark X as not converge in experimental result table

@@
       SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
-      SVM (RBF) + DBSCAN        & $X$        & $X$               & $X$        & $X$                   & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
-      SVM (sigmoid) + DBSCAN    & $X$        & $X$               & $X$        & $X$                   & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
       KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\

### 2023-05-27 final/paper/main.tex
fix typo

@@
 
-The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{here}.
+The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{https://github.com/OEmiliatanO/CSE\_data\_mining}.
 
@@
 SVMs design, which make some SVMs hard to separate the target types. However, by customize 
-the kernel for each SVMs, the problem may ease. In the same time, the increasing number of 
+the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
 parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 

### 2023-05-28 final/main/main.cpp
experimental SVMs

@@ -261,44 +261,83 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
     
     point_t<label_t> result;
 	result.resize(dataloader.test_data.size());
-    for (std::size_t i = 1; i <= KNOWN_CNT; ++i)
+    std::vector<std::vector<size_t>> votes;
+    votes.resize(dataloader.test_data.size());
+    for (auto& x : votes) x.resize(KNOWN_CNT);
+
+    for (std::size_t i = 1; i <= KNOWN_CNT; ++i) // +1
     {
-        dataset_t<data_t, label_t> dataset_{dataloader.train_data};
-        for (auto& x : dataset_.label) x = (x == (label_t)i ? 1LL : -1LL);
-		
-        SVM_t<data_t, label_t> SVM{punishment, converge_lim};
+        for (std::size_t j = i + 1; j <= KNOWN_CNT; ++j) // -1
+        {
+            SVM_t<data_t, label_t> SVM{punishment, converge_lim};
+            dataset_t<data_t, label_t> dataset_;
 
-        if (args["-SVM_kernel"] == "linear")
-            SVM.kernel = std::make_shared<linear_kernel<data_t>>();
-        else if (args["-SVM_kernel"] == "poly")
-        {
-            double g = std::stod(args["-SVM_kernel_gamma"]);
-            double d = std::stod(args["-SVM_kernel_degree"]);
-            double r = std::stod(args["-SVM_kernel_r"]);
-            SVM.kernel = std::make_shared<poly_kernel<data_t>>(g, d, r);
-        }
-        else if (args["-SVM_kernel"] == "rbf")
-        {
-            double g = std::stod(args["-SVM_kernel_gamma"]);
-            SVM.kernel = std::make_shared<rbf_kernel<data_t>>(g);
-        }
-        else if (args["-SVM_kernel"] == "sigmoid")
-        {
-            double g = std::stod(args["-SVM_kernel_gamma"]);
-            double r = std::stod(args["-SVM_kernel_r"]);
-            SVM.kernel = std::make_shared<sigmoid_kernel<data_t>>(g, r);
-        }
-        else
-        {
-            std::cerr << "doesn't support such kernel: " << args["-SVM_kernel"] << std::endl;
-            exit(1);
-        }
+            for (std::size_t k = 0; k < dataloader.train_data.size(); ++k)
+            {
+                if (dataloader.train_data.label[k] == (label_t)i)
[…]

### 2023-05-28 final/include/utility.h
add new argmax function

@@ -16,4 +16,21 @@ std::size_t assign(const U& x, const std::vector<T>& centers)
 template<typename T>
 double sign(T x) { return (x > 0 ? 1 : -1); }
 
+template<typename T>
+std::size_t argmax(std::vector<T> arr)
+{
+    if (arr.empty()) return 0;
+    
+    T maxx = std::numeric_limits<T>::min();
+    std::size_t maxi = 0;
+    for (std::size_t i = 0; i < arr.size(); ++i)
+        if (arr[i] > maxx)
+        {
+            maxx = arr[i];
+            maxi = i;
+        }
+
+    return maxi;
+}
+
 #endif

### 2023-05-30 final/preprocess/PCA/run.sh
Update run.sh

@@ -1,8 +1,4 @@
-#Aout=32
-#python main.py $Aout ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/PCA_train_data_$Aout.csv ../../data/Arrhythmia_data_set/PCA_test_data_$Aout.csv
-#Aout=31
-#python main.py $Aout ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/PCA_train_data_$Aout.csv ../../data/Arrhythmia_data_set/PCA_test_data_$Aout.csv
+Aout=32
+python main.py $Aout ../../data/Arrhythmia_data_set/train_data.csv ../../data/Arrhythmia_data_set/train_label.csv ../../data/Arrhythmia_data_set/test_data.csv ../../data/Arrhythmia_data_set/test_label.csv ../../data/Arrhythmia_data_set/PCA_train_data_$Aout.csv ../../data/Arrhythmia_data_set/PCA_test_data_$Aout.csv
 Bout=30
-python main.py 30 ../../data/gene_expression_cancer_RNA-Seq_data_set/train_data.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/train_label.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/test_data.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/test_label.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/PCA_train_data_$Bout.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/PCA_test_data_$Bout.csv
-Bout=100
[…]

### 2023-05-30 final/paper/main.tex
Update main.tex
add bayes related work and main process

@@
 
+\bf{naive bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
+theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
+And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
+likely outcome according to the conditional probability it just recorded.
+
 \subsection*{Clustering algorithm}
@@
 
+  When it comes to Naive Bayes classifier, Assume there are N known types. Denotes the N Bayes classifiers recognizing each
+  type of known types as BC_1, BC_2, ..., BC_N. For each test data, let BC_1 determine whether it belongs to     type 1, if
+  it does, mark it as type 1 and try classifying next test data, otherwise, BC_2 will determine whether it belongs to class_2
+  or not, and so on. If all Bayes classifiers results false, namely, the data doesn't belong to     any known types, marks it
+  as unknown type.
+
   After classifying, the konwn types and unkonwn types are separated. The data marked as unkonwn types will be thrown 
@@
   \item Lu Che-Yuan: 
-  \item Huang Chia-Yen: 
+  \item Huang Chia-Yen: Bayes, paper, poster
 \end{itemize}

### 2023-05-30 final/main/main.cpp
update new ver.

@@ -263,7 +263,7 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
 	result.resize(dataloader.test_data.size());
     std::vector<std::vector<size_t>> votes;
     votes.resize(dataloader.test_data.size());
-    for (auto& x : votes) x.resize(KNOWN_CNT);
+    for (auto& x : votes) x.resize(KNOWN_CNT + 1);
 
     for (std::size_t i = 1; i <= KNOWN_CNT; ++i) // +1
     {
@@ -283,9 +283,11 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
                     dataset_.emplace_back(dataloader.train_data.data[k], (label_t)-1);
                 }
             }
-
+            
             if (args["-SVM_kernel"] == "linear")
+            {
                 SVM.kernel = std::make_shared<linear_kernel<data_t>>();
+            }
             else if (args["-SVM_kernel"] == "poly")
             {
                 double g = std::stod(args["-SVM_kernel_gamma"]);
@@ -327,6 +329,7 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
         for (auto x : votes[i]) var += (x-mean)*(x-mean);
         var /= (votes[i].size() - 1);
 
+        /*
         for (auto x : votes[i])
             std::cerr << x << ' ';
         std::cerr << "var = " << var << " , true label = ";
@@ -334,7 +337,9 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
             std::cerr << "UNKONWN" << std::endl;
         else
             std::cerr << dataloader.test_data.label[i] << std::endl;
+        */
         result[i] = argmax(votes[i]);
+        if (var > 4.3) result[i] = 0;
     }
     //std::cerr << "==================" << std::endl;
 

### 2023-05-31 final/paper/main.tex
update Bayes

--- 2023-05-27 final/paper/main.tex
@@
 
-\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
+\title{The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
 
@@
 (AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
+Support Vector Data Description (SVDD), naive Bayes classifier; 
 and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
-applications with noise (DBSCAN).
+applications with noise (DBSCAN) and nearest-neighbor chain (NN-chain).
 
@@
 diabetes.
+
+\bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
+theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
+And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
+likely outcome according to the conditional probability it just recorded.
 
@@
 
+  As for Naive Bayes classifier, first assume there are $N$ known types. Denotes the $N$ Bayes classifiers recognizing each 
+  type of known types as $B_1, B_2, ..., B_N$. For each test data, let $B_1$ determine whether it belongs to type 1, if 
+  it does, mark it as type 1 and try classifying next test data, otherwise, $B_2$ will determine whether it belongs to type 2 
+  or not, and so on. If all Bayes classifiers results false, namely, the data doesn't belong to any known types, marks it 
+  as unknown type.
+
   After classifying, the konwn types and unkonwn types are separated. The data marked as unkonwn types will be thrown 
@@
       SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
+      Bayes-GA + kmeans           & $X$        & $X$                            & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $X$        & $X$                      & $0.0297$   & $15.8228 \pm 0$      & $X$        & $X$            \\
       \bottomrule
@@
       SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
+      Bayes-GA + kmeans         & $X$        & $X$               & $X$        & $X$                   & $X$        & $X$                          & $X$        & $X$                      & $0.0338$   & $27.7946 \pm 0$      & $X$        & $X$            \\
       \bottomrule
@@
 techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
-KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
+KNN, SVM, SVDD, NN, Bayes classifier, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
 combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
@@
   \item Lu Che-Yuan: 
-  \item Huang Chia-Yen: 
+  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
 \end{itemize}

### 2023-05-31 final/paper/main.tex
NN NNChain

--- 2023-05-30 final/paper/main.tex
@@
 
+\bf{Standardization and Interpolation}: \rm{With} simple interpolation, the dataset size can be easily increased.
+To ensure that the new produced data would not lower the correctness and precsion of the dataset, standardization to the origin dataset is required.\cite{chen2022doublemix} has used simple interpolation to achieve data augmentation with great outcome.
+With standardization and interpolation, we earn enough data for the latter machine learning.
+
 \subsection*{Classification algorithm}
@@
 
+\bf{Support Vector Data Description(SVDD)}:  \rm{SVDD} is an unsupervised learning algorithm used for one-class classification or outlier detection.
+It defines a hypersphere in the feature space to include some specific data to classify one class from other classes.
+With Deep SVDD, which is the variant of the SVDD which utilize the deep learning, more precise classification can be achieved providing only one class data.\cite{perera2021oneclass} give us the precise explanation how to train a model to classify data with only one class.
+
+\bf{Nearest neighbor chain(NN-Chain)}: \rm{NN-Chain} is data clustering algorithm developed by Jean-Paul Benzécri and J.
+Juan\cite{Benzécri1982}.
+This method cluster the data by merge mutual nearest neighbors nodes to one node, and repeat the same action until the goal clustering number is achieved.
+While the distance can be earned by the normal Euclidean distance, some distance approach is used in the algorithm as well to suit some specific data.\cite{10.1093/comjnl/26.4.354}\cite{müllner2011modern}.
+NN-Chain is one of the hierarchical clustering algorithm which is likely to be presented in tree-like data structure.
 \section{Main Process}
@@
   \end{algorithm}
+  During the known-unknown classification, the SVDD is used.
+First define a model , input every data into it to get the outcome, then use the mean of the outcome as the center of the hypersphere.
+Then, train the model to make every data in the dataset approach to the center of the hypersphere as close as possible.
+After training, we can get the radius of the hypersphere, which can be define according to the outcome of the model.
+Using the radius, we can classify the data to "known", if the distance between the center and the data is less than or equal to the radius, or to "unknown" otherwise.
 
@@
   in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.
+
+  For the NN part, SVDD cannot be trained with data only processed interpolation.
+The hypersphere that the SVDD defines will include all the data in the test dataset, which make the clustering impossible.
+On the other hand, NN classifying can achieve accuracy 100 percent correctness, so the accuracy of Interpolation~NN with gene expression cancer RNA-Seq dataset will be 64.45 percent, in which only known class is predicted correctly.
+
+  On the other hand,SVDD can be trained with PCA-100-dimension data with accuracy up to 98 percent.
+With the NN with 100 percent accuracy and clustering algorithm NN-chain processing gene expression cancer RNA-Seq dataset,the accuray can achieve 75 percent correctness.
 
@@
   \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
-  \item Hsu Ting-Hao: 
+  \item Hsu Ting-Hao: NN, SVDD, NN-Chain, paper, ppt
   \item Sun Shih-Yu: SVM, k-means, paper

### 2023-05-31 final/classifying/DNN/NN/model.py

@@ -1,0 +1,18 @@
+import torch
+import torch.nn as F
+import math
+class DNN(torch.nn.Module):
+    def __init__(self,input_dim,output_dim):
+        super(DNN,self).__init__()
+        base = 2**math.floor(math.log2(input_dim))//32
+        lower_bound = 128 // 32 #//32 for aug
+        if base  < lower_bound:
+            base = lower_bound
+        self.layer_nums = [input_dim]+[base,base*2]+[base*4 for i in range(20)]+[base*2,base]+[output_dim]
+        self.nn = F.ModuleList([torch.nn.Linear(self.layer_nums[i],self.layer_nums[i+1]) for i in range(len(self.layer_nums)-1)])
+        self.acti = F.ReLU()
+    def forward(self,x):
+        for f in self.nn[:-1]:
+            x = f(x)
+            x = self.acti(x)
+        return self.nn[-1](x)

### 2023-05-31 final/classifying/DNN/NN/test.py

@@ -1,0 +1,64 @@
+import torch
+import torch.nn as F
+import torchvision
+from torch.utils.data import TensorDataset,DataLoader
+import numpy as np
+import pandas as pd
+from model import DNN
+import matplotlib.pyplot as plt
+DATA = "AUG3000"
+BATCH_SIZE = 8
+CANCER_OUTPUT_DIM=4
+test_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_data.csv",header=None).to_numpy()
+test_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_label.csv",header=None).to_numpy().squeeze()
+  
+known = pd.read_csv("../known_unknown_clustering_PCA100.csv",header=None).to_numpy().reshape(-1)
+test_data=test_data[known == 1]
+test_label=test_label[known == 1]
+tensor_test_data = torch.tensor(test_data)
+tensor_test_label = torch.tensor(test_label).long()
+test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
+
+def test(dataloader,model=None,write_csv=False):
+    if not model:
+        model = DNN(len(tensor_test_data[0]),CANCER_OUTPUT_DIM).to("cuda")
+        model.load_state_dict(torch.load('classifying-model-from-{}.pth'.format(DATA)))
+    
+
+    loss_fn = F.CrossEntropyLoss()
+    correct=0
+    all_loss=0
+    model.eval()
+    print("Test:")
+    with torch.no_grad():
+        for step,(inputs,target) in enumerate(dataloader):
+            inputs, target = inputs.to(torch.float32).to("cuda"), target.to("cuda")
+            outcome = model(inputs)
+            
+            # a = torch.nn.functional.softmax(outcome,dim=1)
+            # print("target",target)
+            loss = loss_fn(outcome,target)
+            all_loss+=loss.item()
+            correct += (outcome.argmax(1) == target).type(torch.float).sum().item()
+            print("Loss={}, [{}/{}]".format(loss.item(),((step+1)*BATCH_SIZE),len(dataloader)*BATCH_SIZE))
+    print("Accuracy:{:.1f}%, Loss:{}".format(correct/len(dataloader.dataset)*100,all_loss/(len(dataloader.dataset))))
+    if write_csv == True:
+        arr = []
[…]

### 2023-05-31 final/classifying/DNN/NN/train.py

@@ -1,0 +1,87 @@
+import torch
+import torch.nn as F
+import torchvision
+from torch.utils.data import TensorDataset,DataLoader
+import numpy as np
+import pandas as pd
+from model import DNN
+from test import test
+import matplotlib.pyplot as plt
+BATCH_SIZE = 8
+CANCER_OUTPUT_DIM=4
+DATA = "AUG3000"
+
+train_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_3000_train_data.csv",header=None).to_numpy()
+train_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_3000_train_label.csv",header=None).to_numpy().squeeze()
+print(train_data.shape)
+tensor_train_data = torch.tensor(train_data)
+tensor_train_label = torch.tensor(train_label).long()
+train_dataset = TensorDataset(tensor_train_data,tensor_train_label)
+train_dataloader = DataLoader(train_dataset,batch_size=BATCH_SIZE,shuffle=True)
+test_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_data.csv",header=None).to_numpy()
+test_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_label.csv",header=None).to_numpy().squeeze()
+known = pd.read_csv("../known_unknown_clustering_{}.csv".format(DATA),header=None).to_numpy().reshape(-1)
+test_data=test_data[known == 1]
+test_label=test_label[known == 1]
+tensor_test_data = torch.tensor(test_data)
+tensor_test_label = torch.tensor(test_label).long()
+test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+
+
+# data = pd.read_csv("../../data/gene_expression_cancer_RNA-Seq_data_set/test_data.csv").to_numpy()
+# label = pd.read_csv("../../data/gene_expression_cancer_RNA-Seq_data_set/test_label.csv").to_numpy().reshape((-1))
+# print(data.shape,label.shape)
+# tensor_test_data = torch.tensor(data)
+# tensor_test_label = torch.tensor(label).long()
+test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+test_dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
+def train(dataloader):
+    EPOCH = 30
[…]

### 2023-05-31 final/classifying/DNN/SVDD/model.py

@@ -1,0 +1,29 @@
+import torch
+import torch.nn as F
+import math
+class DNN(torch.nn.Module):
+    def __init__(self,input_dim,output_dim):
+        super(DNN,self).__init__()
+        lower_bound = 2**5
+        self.base = 2 # 2**math.floor(math.log2(input_dim))//2**9
+        if self.base < lower_bound:
+            self.base = lower_bound
+        #self.layer_nums = [input_dim]+[self.base,self.base*2]+[self.base*4 for i in range(0)]+[self.base*2,self.base]+[output_dim]
+        self.layer_nums = [input_dim]+[5]+[output_dim]
+        self.li=[F.Linear(self.layer_nums[i],self.layer_nums[i+1],bias=1) for i in range(len(self.layer_nums)-1)]
+        self.bn=[F.BatchNorm1d(i) for i in self.layer_nums[1:]]
+        self.lin = F.ModuleList(self.li)
+        self.bnn = F.ModuleList(self.bn)
+        self.acti = F.ELU()
+        self.dropout = F.Dropout(p=0.3)
+        self.r = None
+    def forward(self,x):
+        for i in range(len(self.bn)-1):
+            x = self.dropout(x)
+            x = self.lin[i](x)
+           # x = self.bnn[i](x)
+            x = self.acti(x)
+        return self.lin[-1](x)
+    def set_r(self,r):
+        self.r = r
+        

### 2023-05-31 final/classifying/DNN/SVDD/test.py

@@ -1,0 +1,95 @@
+import torch
+import torch.nn as F
+import torchvision
+from torch.utils.data import TensorDataset,DataLoader
+import numpy as np
+import pandas as pd
+from model import DNN
+import matplotlib.pyplot as plt
+BATCH_SIZE = 8
+CANCER_OUTPUT_DIM=4
+DATA = "AUG3000"
+# data = pd.read_csv("../../data/gene_expression_cancer_RNA-Seq_data_set/train_data.csv").to_numpy()
+# label = pd.read_csv("../../data/gene_expression_cancer_RNA-Seq_data_set/train_label.csv").to_numpy().reshape((-1))
+# print(data.shape,label.shape)
+# tensor_test_data = torch.tensor(data)
+# tensor_test_label = torch.tensor(label).long()
+
+
+def test(dataloader=None,c=None,r=None,model=None,from_train=True):
+    if not dataloader:
+        test_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_data.csv",header=None).to_numpy()
+        test_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_label.csv",header=None).to_numpy()
+        tensor_test_data = torch.tensor(test_data)
+        tensor_test_label = torch.tensor(test_label).long()
+        tensor_test_label[tensor_test_label<4]=1
+        tensor_test_label[tensor_test_label>=4]=0
+        test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+        
+
+        dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
+    if not model:
+        model = DNN(len(test_dataset[0][0]),len(test_dataset[0][0])).to("cuda")
+        model.load_state_dict(torch.load('one-class-model-from-{}.pth'.format(DATA)))
+    if c==None:
+        c = torch.tensor(pd.read_csv("c_{}.txt".format(DATA),header=None).to_numpy()).squeeze().to(torch.float32).to("cuda")
+        # print(c.shape)
+        # c = torch.zeros(len(tensor_test_data[0]),device="cuda")
+        # print(c.shape)
+        
+
+    correct=0
+    arr = []
+    with torch.no_grad():
+        for step,(inputs,target) in enumerate(dataloader):
+            inputs, target = inputs.to(torch.float32).to("cuda"), target.to("cuda")
+            outcome = model(inputs)
+            # a = torch.nn.functional.softmax(outcome,dim=1)
[…]

### 2023-05-31 final/classifying/DNN/SVDD/train.py

@@ -1,0 +1,98 @@
+import torch
+import torch.nn as F
+import torchvision
+from torch.utils.data import TensorDataset,DataLoader
+import numpy as np
+import pandas as pd
+from model import DNN
+from test import test
+import matplotlib.pyplot as plt
+BATCH_SIZE = 8
+OUTPUT_DIM=100
+DATA = "AUG3000"
+train_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_3000_train_data.csv",header=None).to_numpy()
+
+train_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_3000_train_label.csv",header=None).to_numpy()
+tensor_train_data = torch.tensor(train_data)
+tensor_train_label = torch.tensor(train_label).long()
+tensor_train_label[tensor_train_label<4]=1
+train_dataset = TensorDataset(tensor_train_data,tensor_train_label)
+train_dataloader = DataLoader(train_dataset,batch_size=BATCH_SIZE,shuffle=True)
+test_data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_data.csv",header=None).to_numpy()
+test_label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_test_label.csv",header=None).to_numpy()
+tensor_test_data = torch.tensor(test_data)
+
+tensor_test_label = torch.tensor(test_label).long()
+tensor_test_label[tensor_test_label<4]=1
+tensor_test_label[tensor_test_label>=4]=0
+
+# data = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/test_data.csv").to_numpy()
+# label = pd.read_csv("../../../data/gene_expression_cancer_RNA-Seq_data_set/test_label.csv").to_numpy().reshape((-1))
+# print(data.shape,label.shape)
+# tensor_test_data = torch.tensor(data)
+# tensor_test_label = torch.tensor(label).long()
+test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+test_dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
+def train(dataloader):
+    
+
+
+    EPOCH = 20 
+    model = DNN(len(tensor_train_data[0]),OUTPUT_DIM).to("cuda")
+    #model.load_state_dict(torch.load("one-class-model-from-{}.pth".format(DATA)))
[…]

### 2023-05-31 final/clustering/NNChain/main.cpp

@@ -1,0 +1,122 @@
+#include <iostream>
+#include <iomanip>
+#include <memory>
+#include <cmath>
+#include <chrono>
+#include <string>
+#include <cstring>
+#include <fstream>
+#include <ranges>
+#include <set>
+#include <map>
+#include <algorithm>
+#include <string_view>
+#include "NNChain.h"
+#include "Dataloader.h"
+#include "Datatransformer.h"
+
+using data_t = double;
+using label_t = std::size_t;
+
+void read_file(std::string& data_path, std::string& label_path,dataset_t<data_t,label_t>& dataset){
+    std::fstream fsd,fsl;
+    fsd.open(data_path);
+    fsl.open(label_path);
+    if(fsd.fail()){
+        std::cerr << "Reading File Error:" << data_path << std::endl;
+        exit(1);
+    }
+    if(fsl.fail()){
+        std::cerr << "Reading File Error:" << label_path << std::endl;
+        exit(1);
+    }
+    std::string sd,sl;
+    while(fsd>>sd && fsl>>sl){
+        // std::cout << sl << std::endl;
+        if(sl!="0") continue;
+        std::string delimiter = ",";
+        point_t<data_t> data;
+        for(auto x:std::ranges::views::split(sd,delimiter)){
+            data.emplace_back(std::stod(std::string_view(x).data()));
+        }
+        dataset.emplace_back(std::move(data),std::move(std::stoull(sl)));
+    }
+}
+
+label_t fact(label_t i){
+    if(i==1 || i==0) return 1;
+    return i*fact(i-1);
+}
+
+void compare(std::string& test_label_path,std::string& predict_label_path,point_t<label_t>& labels,int cluster_number,int cluster_label_start){
+    std::set<label_t> se(labels.begin(),labels.end());
+    std::map<label_t,label_t> mp;
+    label_t p=0;
+    for(auto x:se){
+        mp[x]=p++;
+    }
+    std::fstream fstl,fspl;
+    fstl.open(test_label_path);
+    fspl.open(predict_label_path);
+    if(fstl.fail()){
+        std::cerr << "Reading File Error:" << test_label_path << std::endl;
+        exit(1);
+    }
+    if(fspl.fail()){
+        std::cerr << "Reading File Error:" << predict_label_path << std::endl;
+        exit(1);
+    }
+    label_t cnt=0;
+    label_t pp=0;
+    label_t all=0;
[…]

### 2023-05-31 final/clustering/NNChain/src/NNChain.h

@@ -1,0 +1,111 @@
+#ifndef __NNChain_H__
+#define __NNChain_H__
+#include <algorithm>
+#include <vector>
+#include <limits>
+#include <cstdlib>
+#include <iostream>
+#include "Data.h"
+#include "utility.h"
+
+template<typename T,typename U>
+class NNChain_t{
+public:
+    std::size_t cluster_num;
+    NNChain_t() = default;
+    NNChain_t(std::size_t cluster_num_): cluster_num{cluster_num_} {};
+
+    point_t<U> fit(const std::vector<point_t<T>>& X);
+    point_t<U> fit(const dataset_t<T,U>& dataset);
+};
+
+template<typename T, typename U>
+point_t<U> NNChain_t<T,U>::fit(const std::vector<point_t<T>>& X){
+    point_t<U> labels;
+    auto XX(X);
+    labels.resize(X.size());
+    std::size_t now_cluster_num = X.size();
+    std::vector<std::size_t> chain;
+    std::vector<U> set_num(X.size(),1);
+    auto merge = [&set_num,&XX](U x,U y){
+        auto sum1 = XX[x]*(T)set_num[x];
+        auto sum2 = XX[y]*(T)set_num[y];
+        XX[x] = (sum1+sum2) / (T)(set_num[x]+set_num[y]);
+        set_num[x]+=set_num[y];
+        set_num[y]=0;
+        // XX[x]+=XX[y];
+        // XX[x]/=2;
+    };
+    std::function<std::size_t(std::size_t)> findu = [&labels,&findu](U u){
+        if(labels[u]==u) return u;
+        else return labels[u] = findu(labels[u]);
+    };
+    //Everyone is in cluster with one ponit.
+    for(std::size_t i=0;i<X.size();++i){
+        labels[i] = i;
+    }
+    //Start Chaining
+    while(now_cluster_num > this->cluster_num){
+        
+        std::size_t bk_pt,bk_pt_2;
+        double dis,mndis;
+        bool onlyone;
+        while(1){
+            if(chain.empty()){
+                bk_pt=0;
+                bk_pt_2=-1;
+                chain.emplace_back(labels[0]);
+                dis = std::numeric_limits<double>::infinity();
+                mndis=std::numeric_limits<double>::infinity();
+            }
+            else if(chain.size()==1){
+                bk_pt=chain[chain.size()-1];
+                bk_pt_2=-1;
+                dis = std::numeric_limits<double>::infinity();
+                mndis=std::numeric_limits<double>::infinity();
[…]

### 2023-05-31 final/preprocess/STD&Interpolation/functions.py

@@ -1,0 +1,34 @@
+import numpy as np
+import random
+import math
+def interpolate_and_add_gaussian_noise(num_i,num_g,data,label,mu=0,sigma=0.1):
+    if(num_g==num_i==0):
+        return (data,label)
+    dic={}
+    for i in label:
+        try:
+            dic[int(i)]+=1
+        except:
+            dic[int(i)]=1
+    idx = len(data)
+    new_data = np.concatenate((data,np.zeros((num_i+num_g-len(data),len(data[0])))))
+    new_label = np.concatenate((label,np.zeros((num_i+num_g-len(label),len(label[0])))))
+    base = 0
+    print(dic)
+    for i in dic:
+        sample_array = [j for j in range(dic[i])]
+        for j in range(num_i//len(dic)-dic[i]):
+            s1,s2 = random.sample(sample_array,2)
+            new_data[idx]=(data[s1+base]+data[s2+base])/2
+            new_label[idx]=np.array([i],dtype=np.int64)
+            idx+=1
+        print("inter")
+        for j in range(num_g//len(dic)):
+            rd_num = random.randint(base,base+dic[i]-1)
+            new_data[idx] = data[rd_num]+np.array([np.random.normal(mu,sigma) for k in range(len(data[0]))])
+            new_label[idx]=np.array([i],dtype=np.int64)
+            idx+=1
+        base += dic[i]
+        print("gau")
+
+    return (new_data,new_label)

### 2023-05-31 final/preprocess/STD&Interpolation/main.py

@@ -1,0 +1,38 @@
+import numpy as np
+import pandas as pd
+import sys
+import math
+import matplotlib.pyplot as plt
+from functions import interpolate_and_add_gaussian_noise
+
+
+m,n = map(int,[sys.argv[1],sys.argv[2]]) #Data Augumentation with linear interpolation and adding noise
+
+data = pd.read_csv(sys.argv[3],header=None).to_numpy()
+data = np.nan_to_num(data,nan=0.0,posinf=999999,neginf=-999999)
+if("train" in sys.argv[3]):
+    data = (data-np.amin(data,0))/(np.amax(data,0)-np.amin(data,0)) #normalization    
+else:
+    train = pd.read_csv(sys.argv[3].replace("test","train"),header=None).to_numpy()
+    data = (data-np.amin(train,0))/(np.amax(train,0)-np.amin(train,0)) #normalization
+data = np.nan_to_num(data,nan=0.0,posinf=999999,neginf=-999999)
+if("train" in sys.argv[3]):
+    data = (data-np.mean(data,axis=0))/np.std(data,axis=0) #standardlization
+else:
+    data = (data-np.mean(train,axis=0))/np.std(train,axis=0) #standardlization
+data = np.nan_to_num(data,nan=0.0,posinf=999999,neginf=-999999)
+label = pd.read_csv(sys.argv[4],header=None).to_numpy()
+
+preprocessed_data = interpolate_and_add_gaussian_noise(m,n,data,label)
+# preprocessed_data = np.nan_to_num(preprocessed_data,nan=0.0,posinf=999999,neginf=-999999)
+data_name = sys.argv[5]
+label_name = sys.argv[6]
+
+np.savetxt(data_name, preprocessed_data[0], delimiter = ',')
+np.savetxt(label_name, preprocessed_data[1], delimiter = ',')
+
+
+
+#python main.py 1000 0 ../../data/gene_expression_cancer_RNA-Seq_data_set/train_data.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/train_label.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_train_data.csv ../../data/gene_expression_cancer_RNA-Seq_data_set/aug_0_train_label.csv
[…]

### 2023-05-31 final/paper/main.tex
update paper

--- 2023-05-31 final/paper/main.tex
@@
       SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
-      Bayes-GA + kmeans           & $X$        & $X$                            & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $X$        & $X$                      & $0.0297$   & $15.8228 \pm 0$      & $X$        & $X$            \\
+      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
       \bottomrule
@@
       SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
-      Bayes-GA + kmeans         & $X$        & $X$               & $X$        & $X$                   & $X$        & $X$                          & $X$        & $X$                      & $0.0338$   & $27.7946 \pm 0$      & $X$        & $X$            \\
+      Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
       \bottomrule
@@
   \item Sun Shih-Yu: SVM, k-means, paper
-  \item Lu Che-Yuan: 
+  \item Lu Che-Yuan: naive Bayes classifier
   \item Huang Chia-Yen: naive Bayes classifier, paper, poster

### 2023-05-31 final/paper/main.tex

@@
 
-\title{The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
+\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
 
@@
 (AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
-Support Vector Data Description (SVDD), naive Bayes classifier; 
 and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
-applications with noise (DBSCAN) and nearest-neighbor chain (NN-chain).
+applications with noise (DBSCAN).
 
@@
 
-\bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
+\bf{naive bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
 theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
@@
 
-  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
+  On the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
   accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
@@
   in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.
+
+  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot be trained with data augmented by 
+  interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
+  clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
+  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.
 
@@
 techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
-KNN, SVM, SVDD, NN, Bayes classifier, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
+KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
 combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
@@
 algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
-the accuracy on these datasets.
+the accuracy on these datasets. Another issue is SVDD, in 32 dimension PCA data, it can not 
+separate the known and unkonwn types well. The reason behind is that in a lower dimension, 
+the distance between known and unknown types are so close that SVDD can not separate them. 
+If reduce the dataset to a relatively larger dimension, the problem may be solved.
 

### 2023-05-31 final/paper/main.tex
update paper

@@
 learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
-(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
-and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
-applications with noise (DBSCAN).
+(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), support vector data 
+description (SVDD), neural network (NN) and naive Bayes classifier; and clustering for dealing with unknown 
+types, e.g., k-means, density-based spatial clustering of applications with noise (DBSCAN).
 
@@
 these two datasets, this work examines the the accuracy of the combinations of some major machine 
-learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.
+learning techniques, including PCA, AE, KNN, SVM, SVDD, NN, naive Bayes classifier, NN-chain, k-means, 
+DBSCAN.
 

### 2023-05-31 final/paper/main.tex
paper experiment done

--- 2023-05-31 final/paper/main.tex
@@
 
-  As for Naive Bayes classifier, first assume there are $N$ known types. Denotes the $N$ Bayes classifiers recognizing each 
-  type of known types as $B_1, B_2, ..., B_N$. For each test data, let $B_1$ determine whether it belongs to type 1, if 
-  it does, mark it as type 1 and try classifying next test data, otherwise, $B_2$ will determine whether it belongs to type 2 
+  When it comes to Naive Bayes classifier, Assume there are N known types. Denotes the N Bayes classifiers recognizing each
+  type of known types as BC_1, BC_2, ..., BC_N. For each test data, let BC_1 determine whether it belongs to     type 1, if
+  it does, mark it as type 1 and try classifying next test data, otherwise, BC_2 will determine whether it belongs to class_2
   or not, and so on. If all Bayes classifiers results false, namely, the data doesn't belong to     any known types, marks it
@@
 
-  On the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
+  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
   accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
@@
 
-  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot be trained with data augmented by 
-  interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
-  clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
-  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.
+  For the NN part, SVDD cannot be trained with data only processed interpolation or PCA and AE with low dimension.
+The hypersphere that the SVDD defines will include or exclude almost all the data in the test dataset, which make the clustering almost impossible.
+  On the other hand,SVDD can be trained with PCA-100-dimension data with accuracy up to 98 percent.
+With the NN with 100 percent accuracy and clustering algorithm NN-chain processing gene expression cancer RNA-Seq dataset,the accuray can achieve 75 percent correctness.
 
@@
       SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
-      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
+      NN + NNChain                & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
       \bottomrule
@@
       SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
-      Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
+      NN + NNChain              & $163.359$  & $40.96   \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
       \bottomrule
@@
 algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
-the accuracy on these datasets. Another issue is SVDD, in 32 dimension PCA data, it can not 
-separate the known and unkonwn types well. The reason behind is that in a lower dimension, 
-the distance between known and unknown types are so close that SVDD can not separate them. 
-If reduce the dataset to a relatively larger dimension, the problem may be solved.
+the accuracy on these datasets.
 
@@
   \item Sun Shih-Yu: SVM, k-means, paper
-  \item Lu Che-Yuan: naive Bayes classifier
-  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
+  \item Lu Che-Yuan: 
+  \item Huang Chia-Yen: Bayes, paper, poster
 \end{itemize}

### 2023-05-31 final/paper/main.tex

--- 2023-05-31 final/paper/main.tex
@@
       Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
+      NN + NNChain                & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
       \bottomrule
@@
       Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
+      NN + NNChain              & $163.359$  & $40.96   \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
       \bottomrule
@@
   \item Lu Che-Yuan: naive Bayes classifier
-  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
+  \item Huang Chia-Yen: naive Bayes classifier, paper, poster, ppt
 \end{itemize}

### 2023-05-31 final/paper/main.tex
update paper

@@
 
-\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
+\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}
 
@@
       \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
-      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
-      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
+      \State{$\text{Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
+      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Knowns})$}
     \end{algorithmic}
@@
 
-  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot be trained with data augmented by 
+  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot fit well with data augmented by 
   interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
@@
       Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
-      NN + NNChain                & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
+      NN + NN-Chain               & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
       \bottomrule
@@
       SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
-      Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
-      NN + NNChain              & $163.359$  & $40.96   \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
+      Bayes-GA + kmeans         & $2.231$    & $43.6746 \pm 0$   & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
+      NN + NN-Chain             & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
       \bottomrule

### 2023-06-01 final/main/main.cpp
experimental merge SVDD+NN+DBSACN/k-means

@@ -85,6 +85,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     std::string_view test_data_path  = args["-test_data_path"];
     std::string_view train_label_path = args["-train_label_path"];
     std::string_view test_label_path  = args["-test_label_path"];
+
     if (args["-verbose"] == "true")
     {
         std::cout << "===================================================" << std::endl;
@@ -126,6 +127,9 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     	std::cout << "clustering algorithm: " << args["-clustering"] << std::endl << std::endl;
     }
     
+    label_t label_;
+    point_t<label_t> outer_classifying_result;
+    while (std::cin >> label_) outer_classifying_result.emplace_back(label_);
 	for (std::size_t _ = 0; _ < repeats; ++_)
 	{
 		//std::cout << _ << "-th fitting..." << std::endl;
@@ -134,10 +138,11 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
         kindscnt.resize(KNOWN_CNT + 1);
         centers.resize(UNKNOWN_CNT + KNOWN_CNT + 1);
         for (auto& x : centers) x.resize(dataloader.test_data.data_dimension());
-
+        
         //std::cerr << "classifying..." << std::endl;
-        auto classifying_result = Fn[args["-classifying"]](args, dataloader, KNOWN_CNT);
-		
+        //auto classifying_result = Fn[args["-classifying"]](args, dataloader, KNOWN_CNT);
+		auto classifying_result = outer_classifying_result;
+
 		dataset_t<data_t, label_t> unknown_data;
 		auto unknowncnt = 0, classify_correct = 0;
 		for (std::size_t i = 0; i < dataloader.test_data.size(); ++i)
@@ -165,7 +170,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
             std::cerr << "truely unknown cnt = " << unknowncnt << std::endl;
             std::cerr << "classify acc = " << (double)classify_correct / (dataloader.test_data.size() - unknowncnt) << std::endl;
         }
-
+        
 		Dataloader_t<data_t, label_t> unknown_dataloader;
 		unknown_dataloader.load_test(unknown_data);
         
@@ -199,7 +204,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
[…]

### 2023-06-01 final/paper/main.tex
update paper
update PCA100

@@
 classifying the known types, and finally apply DBSCAN on the remaining data, the accuracy of predicting 
-can reach about 94\%, which beats the other methods out. In the other way, the result of arrhythmia 
-dataset shows that, with raw data, use KNN and k-means, the highest accuracy of predicting can reach about 
-53\%.
+can reach about 94\%, which beats the most methods out. And with PCA reducing the dimension to 100, SVDD 
+with NN can even have 98\% accuracy. 
+On the other way, the result of arrhythmia dataset shows that, with raw data, use KNN and k-means, the 
+highest accuracy of predicting can reach about 53\%.
 
@@
 
-  On the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
+  On the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN + k-means in raw data gets 53.1646\% 
   accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
-  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
-  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.
+  KNN + k-means in PCA data gets 94.8795\%. And KNN + DBSCAN performs well too. This method shows similar performance 
+  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA-30 data.
 
-  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot fit well with data augmented by 
+  For the SVDD with NN + NN-chain, the performance is not as good as KNN, since SVDD cannot fit well with data augmented by 
   interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
   clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
-  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.
+  the accuracy of SVDD with NN + NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset with PCA-30. 
+  However, when in PCA-100, SVDD with NN + k-means and DBSCAN can have 98.4940\% and 97.8916\% respectively.
 
@@
       SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
-      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
+      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $\text{not converge}$& $0.0294$  & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
+      SVDD w.t.
 NN + NN-Chain     & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
@@
       \begin{tabular}{@{}lcccccccccccc@{}}\toprule
-        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\
-        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
+        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{PCA-100} & \multicolumn{2}{c}{PCA-100 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\
+        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}\cmidrule(lr){14-15}\cmidrule(lr){16-17}
                                 & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                                                                                             & Search (s) & acc                  & Search (s) & acc            \\ \midrule
-      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
-      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
-      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
-      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
-      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
-      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
-      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
-      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
-      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
-      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
-      Bayes-GA + kmeans         & $2.231$    & $43.6746 \pm 0$   & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
-      NN + NN-Chain             & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.96 \pm 0$            & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
+      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0518$   & $91.2651 \pm 0$& $0.0494$   & $69.8795 \pm 0$           & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
+      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $4.3810$   & $9.9398 \pm 0$ & $0.5112$   & $9.9398 \pm 0$            & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
+      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.4586$   & $64.4578 \pm 0$& $0.4612$   & $61.747 \pm 0$            & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $21.3767$  & $9.9398 \pm 0$ & $3.3378$   & $9.6386 \pm 0$            & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.9179$   & $71.9880 \pm 0$& $1.6702$   & $61.4458 \pm 0$           & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0374$   & $91.8675 \pm 0$& $0.0404$   & $75.6024 \pm 0$           & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
+      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $2.3938$   & $9.9398 \pm 0$ & $0.5174$   & $9.9398 \pm 0$            & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
+      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.4698$   & $64.4578 \pm 0$& $5.4048$   & $9.9398 \pm 0$            & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
+      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $3.1693$   & $9.9398 \pm 0$ & $5.1415$   & $9.9398 \pm 0$            & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
+      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $1.1448$   & $71.9880 \pm 0$& $1.3232$   & $61.4458 \pm 0$           & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
+      Bayes-GA + kmeans         & $2.231$    & $43.6746 \pm 0$   & $X$        & $\text{not converge}$ & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $X$        & $X \pm 0$      & $0.0237$   & $X \pm 0$           & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
+      SVDD w.t.
+NN + NN-Chain   & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $X \pm 0$      & $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
+      SVDD w.t.
+NN + DBSCAN     & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $98.4940 \pm 0$& $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
+      SVDD w.t.
+NN + k-means    & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $97.8916 \pm 0$& $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
       \bottomrule
@@
 the accuracy on these datasets. Another issue is SVDD, in 32 dimension PCA data, it can not 
-separate the known and unkonwn types well. The reason behind is that in a lower dimension, 
+separate the known and unkonwn types well, but in 100 dimension PCA data, it can separate konwn 
+and unkonwn with 98\% accuracy. The reason behind is because that in a lower dimension, 
 the distance between known and unknown types are so close that SVDD can not separate them. 
-If reduce the dataset to a relatively larger dimension, the problem may be solved.
+If reduce the dataset to a relatively larger dimension, the problem can be solved.
 

### 2023-06-02 final/classifying/SVDD-wt-NN/SVDDNN.py
update SVDD-wt-NN

@@ -1,0 +1,102 @@
+import torch
+import torch.nn as F
+import torchvision
+from torch.utils.data import TensorDataset,DataLoader
+import numpy as np
+import pandas as pd
+from model import DNN,SVDD
+import time
+import sys
+BATCH_SIZE = 8
+OUTPUT_DIM= 200
+DATA = "PCA100"
+
+def SVDDNN(data_path,label_path,outcome_path):
+    test_data = pd.read_csv(data_path,header=None).to_numpy()
+    test_label = pd.read_csv(label_path,header=None).to_numpy()
+    tensor_test_data = torch.tensor(test_data)
+
+    tensor_test_label = torch.tensor(test_label).long()
+    tensor_test_label[tensor_test_label<4]=1
+    tensor_test_label[tensor_test_label>=4]=0
+    test_dataset = TensorDataset(tensor_test_data,tensor_test_label)
+
+    dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
+    SVDD_model = SVDD(len(test_dataset[0][0]),OUTPUT_DIM).to("cuda")
+    SVDD_model.load_state_dict(torch.load('./model/one-class-model-from-{}.pth'.format(DATA)))
+    c = torch.tensor(pd.read_csv("./parameter/c.txt",header=None).to_numpy()).squeeze().to(torch.float32).to("cuda")
+    arr = []
+
+    st = time.time()
+    with torch.no_grad():
+        for step,(inputs,target) in enumerate(dataloader):
+            inputs, target = inputs.to(torch.float32).to("cuda"), target.to("cuda")
+            outcome = SVDD_model(inputs)
+            # a = torch.nn.functional.softmax(outcome,dim=1)
+            # print(a.max(dim=1),target)
+            dist = torch.sum((outcome-c)**2,dim=1)
+            arr.extend(list(zip(dist.cpu().numpy().tolist(),target.cpu().numpy().tolist())))
+
+    r = pd.read_csv("./parameter/r.txt",header = None).to_numpy()[0]
+    cnt = 0
+    li = []
+    for dist,label in arr:
+        if dist > r:
+            ans = 0
+        else:
+            ans = 1
+        li.append(ans)
+        cnt += ans != label[0]
+        if ans != label[0]:
+            print(dist)
+    print("Finished")
+    print("SVDD Accuracy:{:.6f}%".format((len(arr)-cnt)/len(arr)*100))
+
+    li = np.array(li)
+
[…]

### 2023-06-02 final/main/main.cpp
add SVDD-wt-NN classifying

@@ -3,6 +3,7 @@
 #include <cmath>
 #include <chrono>
 #include <unordered_map>
+#include <fstream>
 #include "KNN.h"
 #include "Brute.h"
 #include "Annoy.h"
@@ -22,6 +23,7 @@ using ccfn = point_t<label_t>(*)(std::unordered_map<std::string, std::string>&, 
 
 point_t<label_t> KNN_predict(auto& args, const auto& dataloader, std::size_t KNOWN_CNT);
 point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KNOWN_CNT);
+point_t<label_t> SVDD_wt_NN_predict(auto& args, const auto& dataloader, std::size_t n);
 point_t<label_t> DBSCAN_fit(auto& args, const auto& dataloader, std::size_t UNKNOWN_CNT);
 point_t<label_t> kmeans_fit(auto& args, const auto& dataloader, std::size_t k);
 
@@ -31,6 +33,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 {
     Fn["KNN"] = KNN_predict;
     Fn["SVM"] = SVMs_predict;
+    Fn["SVDD-wt-NN"] = SVDD_wt_NN_predict;
     Fn["DBSCAN"] = DBSCAN_fit;
     Fn["kmeans"] = kmeans_fit;
 
@@ -209,7 +212,7 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
 	macc_ /= repeats;
 
 	std::chrono::steady_clock::time_point ed = std::chrono::steady_clock::now();
-	std::cout << "acc = " << macc_ << "%(" << stand_ << ")" << std::endl;
+	std::cout << "" << macc_ << "%(" << stand_ << ")" << std::endl;
 	auto duration = std::chrono::duration_cast<std::chrono::microseconds>(ed - st).count() / 1000000.0 / repeats;
 	std::cout << "time: " << duration << std::endl << std::endl;
 
@@ -299,6 +302,18 @@ point_t<label_t> SVMs_predict(auto& args, const auto& dataloader, std::size_t KN
         for (std::size_t j = 0; j < result_.size(); ++j)
             result[j] = (result_[j] == 1LL ? (label_t)i : 0LL);
     }
+    return result;
+}
+
[…]

### 2023-06-02 final/paper/main.tex
update paper

@@
   the accuracy of SVDD with NN + NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset with PCA-30. 
-  However, when in PCA-100, SVDD with NN + k-means and DBSCAN can have 98.4940\% and 97.8916\% respectively.
+  However, as Table~\ref{table:gene_expression_result_PCA_100} shown, when in PCA-100, SVDD with NN + k-means and DBSCAN can 
+  have 98.1928\% and 98.1928\% respectively.
 
@@
       SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
-      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $\text{not converge}$& $0.0294$  & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
-      SVDD w.t.
-NN + NN-Chain     & $0.6338$   & $31.6456 \pm 0$                & $0.633 $   & $29.7468 \pm 0$     & $0.9358$   & $31.6456 \pm 0$      & $0.8370$   & $30.3797 \pm 0$          & $1.0540$   & $29.7468 \pm 0$      & $1.0540$   & $29.7468 \pm 0$\\
+      Bayes-GA + kmeans           & $0.0957$   & $\z{9.9367} \pm 0.0041$        & $0.1416$   & $\z{8.9241} \pm 0.0019$ & $0.0315$   & $\z{8.7975} \pm 0.0019$  & $0.0336$   & $\z{8.5443} \pm 0.0042$  & $0.0325$   & $\z{3.7975} \pm 0$   & $0.0332$   & $\z{4.4304} \pm 0$\\
       \bottomrule
@@
       \begin{tabular}{@{}lcccccccccccc@{}}\toprule
-        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{PCA-100} & \multicolumn{2}{c}{PCA-100 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\
-        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}\cmidrule(lr){14-15}\cmidrule(lr){16-17}
+        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} &  \multicolumn{2}{c}{AE-30}        & \multicolumn{2}{c}{AE-30 Normalized} \\
+        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                 & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
-      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0518$   & $91.2651 \pm 0$& $0.0494$   & $69.8795 \pm 0$           & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
-      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $4.3810$   & $9.9398 \pm 0$ & $0.5112$   & $9.9398 \pm 0$            & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
-      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.4586$   & $64.4578 \pm 0$& $0.4612$   & $61.747 \pm 0$            & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
-      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $21.3767$  & $9.9398 \pm 0$ & $3.3378$   & $9.6386 \pm 0$            & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
-      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.9179$   & $71.9880 \pm 0$& $1.6702$   & $61.4458 \pm 0$           & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
-      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0374$   & $91.8675 \pm 0$& $0.0404$   & $75.6024 \pm 0$           & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
-      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $2.3938$   & $9.9398 \pm 0$ & $0.5174$   & $9.9398 \pm 0$            & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
-      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.4698$   & $64.4578 \pm 0$& $5.4048$   & $9.9398 \pm 0$            & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
-      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $3.1693$   & $9.9398 \pm 0$ & $5.1415$   & $9.9398 \pm 0$            & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
-      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $1.1448$   & $71.9880 \pm 0$& $1.3232$   & $61.4458 \pm 0$           & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
-      Bayes-GA + kmeans         & $2.231$    & $43.6746 \pm 0$   & $X$        & $\text{not converge}$ & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $X$        & $X \pm 0$      & $0.0237$   & $X \pm 0$           & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
-      SVDD w.t.
-NN + NN-Chain   & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $X \pm 0$      & $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
-      SVDD w.t.
-NN + DBSCAN     & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $98.4940 \pm 0$& $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
-      SVDD w.t.
-NN + k-means    & $163.359$  & $40.9600 \pm 0$   & $169.031$  & $41.2651 \pm 0$       & $1.1779$   & $35.5421 \pm 0$              & $1.1170$   & $40.9600 \pm 0$          & $X$        & $97.8916 \pm 0$& $0.0237$   & $X \pm 0$           & $0.9979$   & $16.4634 \pm 0$      & $1.0220$   & $41.2651 \pm 0$\\
+      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
+      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
+      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
+      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
+      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
+      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
+      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
+      Bayes-GA + kmeans         & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.0314$   & $37.0482 \pm 5.5511$         & $0.0406$   & $60.2410 \pm 1.1102$     & $0.0391$   & $33.1325 \pm 0$      & $0.0303$   & $31.3253 \pm 0$\\
       \bottomrule
@@
     \label{table:gene_expression_result}
+      \vspace{-\baselineskip}
+  \end{table*}
+
+  \begin{table*}
+    \centering
+    \newcommand{\z}{\phantom{0}}
+    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
+      \begin{tabular}{@{}lcc@{}}\toprule
+        Method                  & \multicolumn{2}{c}{PCA-100} \\ 
+        \cmidrule(lr){2-3}
+                                & Search (s) & acc            \\ \midrule
+      KNN-Brute-Force + DBSCAN  & $0.0518$   & $91.2651 \pm 0$\\
+      SVM (linear) + DBSCAN     & $4.3810$   & $\z{9.9398}  \pm 0$\\
+      SVM (polynomial) + DBSCAN & $0.4586$   & $64.4578 \pm 0$\\
+      SVM (RBF) + DBSCAN        & $21.3767$  & $\z{9.9398}  \pm 0$\\
+      SVM (sigmoid) + DBSCAN    & $0.9179$   & $71.9880 \pm 0$\\
+      KNN-Brute-Force + kmeans  & $0.0374$   & $91.8675 \pm 0$\\
+      SVM (linear) + kmeans     & $2.3938$   & $\z{9.9398}  \pm 0$\\
+      SVM (polynomial) + kmeans & $0.4698$   & $64.4578 \pm 0$\\
+      SVM (RBF) + kmeans        & $3.1693$   & $\z{9.9398}  \pm 0$\\
+      SVM (sigmoid) + kmeans    & $1.1448$   & $71.9880 \pm 0$\\
+      SVDD w.t. NN + DBSCAN     & $1.218$    & $\bf{98.1928} \pm 0$\\
+      SVDD w.t. NN + k-means    & $1.267$    & $\bf{98.1928} \pm 0$\\
+      \bottomrule
+      \end{tabular}
+    \label{table:gene_expression_result_PCA_100}
       \vspace{-\baselineskip}
@@
 
+\newpage
 \section{Contribution}

### 2023-06-03 final/classifying/SVDD-wt-NN/SVDDNN.py
customized model pth and parameter pth

@@ -11,7 +11,7 @@ BATCH_SIZE = 8
 OUTPUT_DIM= 200
 DATA = "PCA100"
 
-def SVDDNN(data_path,label_path,outcome_path):
+def SVDDNN(data_path,label_path,outcome_path, model_pth, param_pth):
     test_data = pd.read_csv(data_path,header=None).to_numpy()
     test_label = pd.read_csv(label_path,header=None).to_numpy()
     tensor_test_data = torch.tensor(test_data)
@@ -23,8 +23,8 @@ def SVDDNN(data_path,label_path,outcome_path):
 
     dataloader = DataLoader(test_dataset,batch_size=BATCH_SIZE)
     SVDD_model = SVDD(len(test_dataset[0][0]),OUTPUT_DIM).to("cuda")
-    SVDD_model.load_state_dict(torch.load('./model/one-class-model-from-{}.pth'.format(DATA)))
-    c = torch.tensor(pd.read_csv("./parameter/c.txt",header=None).to_numpy()).squeeze().to(torch.float32).to("cuda")
+    SVDD_model.load_state_dict(torch.load(f"{model_pth}/one-class-model-from-{DATA}.pth"))
+    c = torch.tensor(pd.read_csv(f"{param_pth}/c.txt",header=None).to_numpy()).squeeze().to(torch.float32).to("cuda")
     arr = []
 
     st = time.time()
@@ -37,7 +37,7 @@ def SVDDNN(data_path,label_path,outcome_path):
             dist = torch.sum((outcome-c)**2,dim=1)
             arr.extend(list(zip(dist.cpu().numpy().tolist(),target.cpu().numpy().tolist())))
 
-    r = pd.read_csv("./parameter/r.txt",header = None).to_numpy()[0]
+    r = pd.read_csv(f"{param_pth}/r.txt",header = None).to_numpy()[0]
     cnt = 0
     li = []
     for dist,label in arr:
@@ -64,7 +64,7 @@ def SVDDNN(data_path,label_path,outcome_path):
 
     CANCER_OUTPUT_DIM=4
     model = DNN(len(tensor_test_data[0]),CANCER_OUTPUT_DIM).to("cuda")
-    model.load_state_dict(torch.load('./model/classifying-model-from-{}.pth'.format(DATA)))
[…]

### 2023-06-03 final/main/main.cpp
add SVDD-wt-NN_result pth

@@ -70,6 +70,9 @@ int main([[maybe_unused]]int argc, [[maybe_unused]]char* argv[])
     Argparser.add("-SVM_kernel_degree");
     Argparser.add("-SVM_kernel_r");
 
+    // SVDD w.t. NN
+    Argparser.add("-SVDD-wt-NN_result_path");
+
 	// DBSCAN
 	Argparser.add("-DBSCAN_minPts");
 	Argparser.add("-DBSCAN_eps");
